### 2020-12-06 tex/interactcsesample.tex
a tex version can be compiled successfully

% interactcsesample.tex
% v1.05 - August 2017

\documentclass[]{interact}

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage[caption=false]{subfig}% Support for small, `sub' figures and tables
%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required

%\usepackage[doublespacing]{setspace}% To produce a `double spaced' document if required
%\setlength\parindent{24pt}% To increase paragraph indentation when line spacing is doubled
%\setlength\bibindent{2em}% To increase hanging indent in bibliography when line spacing is doubled

\usepackage{natbib}% Citation support using natbib.sty
\bibpunct[, ]{(}{)}{;}{a}{}{,}% Citation support using natbib.sty
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty

\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{notation}{Notation}

\begin{document}

\articletype{ARTICLE}% Specify the article type or omit as appropriate

\title{The responses of \textit{Spinifex littoreus} to sand burial on the coastal area of Pingtan Island, Fujian Province, South China}

\author{
\name{
  Shuang Song\textsuperscript{a}, 
  Jianhui Du \textsuperscript{a,b} \thanks{CONTACT Jianhui Du. Email: dujh1982@hotmail.com}, 
  Qirui Wu \textsuperscript{a},
  Mingyang Ni \textsuperscript{a} and Yingling Zhang \textsuperscript{a}}\affil{\textsuperscript{a}School of Geography and Planning, Sun Yat-Sen University, Guangzhou, 510275, China; \textsuperscript{b} Guangdong Key Laboratory for Urbanization and Geo-simulation, Guangzhou, 510275, China}
}

\maketitle

\begin{abstract}
\label{abstract}
% 砂生植物对沙埋藏的适应能力对海岸沙丘系统的生态恢复至关重要。
The adaptive capacity of psammophytes to sand burial is crucial for the ecological restoration of coastal dune systems. 
% 研究了福建平潭岛海岸滨鹬对不同埋沙深度和埋沙深度的响应。
The responses of Spinifex littoreus to different sand burial depths and levels were examined on the coast of Pingtan island, Fujian Province, South China. 
% 结果表明，与对照组相比，砂埋对其匍匐茎的垂直生长无显著影响。
The results indicated that, compared to the control group, sand burial on the S. littoreus stolons had no significant impact on its vertical growth of conjoint ramets. 
% 随着砂埋的继续，匍匐茎顶端生长更快，完全砂埋比半砂埋影响更明显。
The stolon apex grew even faster as the sand burial continued, with more obvious influence under complete sand burial than half sand burial. 
% 不同埋沙处理均能刺激和产生荔枝匍匐茎上的不定根，其长度随埋沙水平的变化而变化。
Adventitious roots on S. littoreus stolons were stimulated and produced in all sand burial treatments, the length of which varied according to the sand burial levels. 
% 在不定根和叶片上，三个匍匐茎上的干生物量分配均发生了变化，而在茎上则没有变化。
Dry biomass allocation were altered by sand burial in both adventitious roots and leaves, but not in stems. 
More adventitious roots on base of stolon and leaves on apex of stolon were observed. 
% 通过匍匐茎的快速生长，匍匐茎基部产生大量不定根，匍匐茎顶端的叶片萌发率较高，可以适应完全的砂埋。
S. littoreus can adapt to complete sand burial by rapid growth of stolons, abundant production of adventitious roots on the stolon base, and more germination of leaves on the stolon apex.
\end{abstract}

\begin{keywords}
Sections; lists; figures; tables; mathematics; fonts; references; appendices
\end{keywords}

\section{Introduction}

In order to assist authors in the process of preparing a manuscript for a journal, the Taylor \& Francis `\textsf{Interact}' layout style has been implemented as a \LaTeXe\ class file based on the \texttt{article} document class. A \textsc{Bib}\TeX\ bibliography style file and a sample bibliography are also provided in order to assist with the formatting of your references.

Commands that differ from or are provided in addition to standard \LaTeXe\ are described in this document, which is \emph{not} a substitute for a \LaTeXe\ tutorial.

The \texttt{interactcsesample.tex} file can be used as a template for a manuscript by cutting, pasting, inserting and deleting text as appropriate, using the preamble and the \LaTeX\ environments provided (e.g.\ \verb"\begin{abstract}", \verb"\begin{keywords}").

\subsection{The \textsf{Interact} class file}\label{class}

The \texttt{interact} class file preserves the standard \LaTeXe\ interface such that any document that can be produced using \texttt{article.cls} can also be produced with minimal alteration using the \texttt{interact} class file as described in this document.

If your article is accepted for publication it will be typeset as the journal requires in Minion Pro and/or Myriad Pro. Since most authors will not have these fonts installed, the page make-up is liable to alter slightly with the change of font. Also, the \texttt{interact} class file produces only single-column format, which is preferred for peer review and will be converted to two-column format by the typesetter if necessary during preparation of the proofs. Please therefore do not try to match the typeset format exactly, but use the standard \LaTeX\ fonts instead and ignore details such as slightly long lines of text or figures/tables not appearing in exact synchronization with their citations in the text: these details will be dealt with by the typesetter. Similarly, it is unnecessary to spend time addressing warnings in the log file -- if your .tex file compiles to produce a PDF document that correctly shows how you wish your paper to appear, such warnings will not prevent your source files being imported into the typesetter's program.

\subsection{Submission of manuscripts prepared using \emph{\LaTeX}}

Manuscripts for possible publication should be submitted to the Editors for review as directed in the journal's Instructions for Authors, and in accordance with any technical instructions provided in the journal's ScholarOne Manuscripts or Editorial Manager site. Your \LaTeX\ source file(s), the class file and any graphics files will be required in addition to the final PDF version when final, revised versions of accepted manuscripts are submitted.

Please ensure that any author-defined macros used in your article are gathered together in the preamble of your .tex file, i.e.\ before the \verb"\begin{document}" command. Note that if serious problems are encountered in the coding of a document (missing author-defined macros, for example), the typesetter may resort to rekeying it.

\section{Using the \texttt{interact} class file}

For convenience, simply copy the \texttt{interact.cls} file into the same directory as your manuscript files (you do not need to install it in your \TeX\ distribution). In order to use the \texttt{interact} document class, replace the command \verb"\documentclass{article}" at the beginning of your document with the command \verb"\documentclass{interact}".

The following document-class options should \emph{not} be used with the \texttt{interact} class file:
\begin{itemize}
  \item \texttt{10pt}, \texttt{11pt}, \texttt{12pt} -- unavailable;
  \item \texttt{oneside}, \texttt{twoside} -- not necessary, \texttt{oneside} is the default;
  \item \texttt{leqno}, \texttt{titlepage} -- should not be used;
  \item \texttt{twocolumn} -- should not be used (see Subsection~\ref{class});
  \item \texttt{onecolumn} -- not necessary as it is the default style.
\end{itemize}
To prepare a manuscript for a journal that is printed in A4 (two column) format, use the \verb"largeformat" document-class option provided by \texttt{interact.cls}; otherwise the class file produces pages sized for B5 (single column) format by default. The \texttt{geometry} package should not be used to make any further adjustments to the page dimensions.

%If your manuscript has supplementary content you can use the \verb"interact" class file to prepare all or part of it using the \verb"suppldata" document-class option, which will suppress the `article history' date. This option \emph{must not} be used on any primary content. Note that authors are solely responsible for the preparation of all supplemental material.

\section{Additional features of the \texttt{interact} class file}

\subsection{Title, authors' names and affiliations, abstracts and article types}

The title should be generated at the beginning of your article using the \verb"\maketitle" command.
In the final version the author name(s) and affiliation(s) must be followed immediately by \verb"\maketitle" as shown below in order for them to be displayed in your PDF document.
To prepare an anonymous version for double-blind peer review, you can put the \verb"\maketitle" between the \verb"\title" and the \verb"\author" in order to hide the author name(s) and affiliation(s) temporarily.
Next you should include the abstract if your article has one, enclosed within an \texttt{abstract} environment.
The \verb"\articletype" command is also provided as an \emph{optional} element which should \emph{only} be included if your article actually needs it.
For example, the titles for this document begin as follows:
\begin{verbatim}
\articletype{ARTICLE TEMPLATE}

\title{Taylor \& Francis \LaTeX\ template for authors (\textsf{Interact}
layout + Council of Science Editors name-year reference style)}

\author{
\name{A.~N. Author\textsuperscript{a}\thanks{CONTACT A.~N. Author.
Email: latex.helpdesk@tandf.co.uk} and John Smith\textsuperscript{b}}
\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton
Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik,
Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany} }

\maketitle

\begin{abstract}
This template is for authors who are preparing a manuscript for a
Taylor \& Francis journal using the \LaTeX\ document preparation system
and the \texttt{interact} class file, which is available via selected
journals' home pages on the Taylor \& Francis website.
\end{abstract}
\end{verbatim}

An additional abstract in another language (preceded by a translation of the article title) may be included within the \verb"abstract" environment if required.

A graphical abstract may also be included if required. Within the \verb"abstract" environment you can include the code
\begin{verbatim}
\\\resizebox{25pc}{!}{\includegraphics{abstract.eps}}
\end{verbatim}
where the graphical abstract is to appear, where \verb"abstract.eps" is the name of the file containing the graphic (note that \verb"25pc" is the recommended maximum width, expressed in pica, for the graphical abstract in your manuscript).

\subsection{Abbreviations}

A list of abbreviations may be included if required, enclosed within an \texttt{abbreviations} environment, i.e.\ \verb"\begin{abbreviations}"\ldots\verb"\end{abbreviations}", immediately following the \verb"abstract" environment.

\subsection{Keywords}

A list of keywords may be included if required, enclosed within a \texttt{keywords} environment, i.e.\ \verb"\begin{keywords}"\ldots\verb"\end{keywords}". Additional keywords in other languages (preceded by a translation of the word `keywords') may also be included within the \verb"keywords" environment if required.

\subsection{Subject classification codes}

AMS, JEL or PACS classification codes may be included if required. The \texttt{interact} class file provides an \texttt{amscode} environment, i.e.\ \verb"\begin{amscode}"\ldots\verb"\end{amscode}", a \texttt{jelcode} environment, i.e.\ \verb"\begin{jelcode}"\ldots\verb"\end{jelcode}", and a \texttt{pacscode} environment, i.e.\ \verb"\begin{pacscode}"\ldots\verb"\end{pacscode}" to assist with this.

\subsection{Additional footnotes to the title or authors' names}

The \verb"\thanks" command may be used to create additional footnotes to the title or authors' names if required. Footnote symbols for this purpose should be used in the order
$^\ast$~(coded as \verb"$^\ast$"), $\dagger$~(\verb"$\dagger$"), $\ddagger$~(\verb"$\ddagger$"), $\S$~(\verb"$\S$"), $\P$~(\verb"$\P$"), $\|$~(\verb"$\|$"),
$\dagger\dagger$~(\verb"$\dagger\dagger$"), $\ddagger\ddagger$~(\verb"$\ddagger\ddagger$"), $\S\S$~(\verb"$\S\S$"), $\P\P$~(\verb"$\P\P$").

Note that any \verb"footnote"s to the main text will automatically be assigned the superscript symbols 1, 2, 3, etc. by the class file.\footnote{If preferred, the \texttt{endnotes} package may be used to set the notes at the end of your text, before the bibliography. The symbols will be changed to match the style of the journal if necessary by the typesetter.}

\section{Some guidelines for using the standard features of \LaTeX}

\subsection{Sections}

The \textsf{Interact} layout style allows for five levels of section heading, all of which are provided in the \texttt{interact} class file using the standard \LaTeX\ commands \verb"\section", \verb"\subsection", \verb"\subsubsection", \verb"\paragraph" and \verb"\subparagraph". Numbering will be automatically generated for all these headings by default.

\subsection{Lists}

Numbered lists are produced using the \texttt{enumerate} environment, which will number each list item with arabic numerals by default. For example,
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
was produced by
\begin{verbatim}
\begin{enumerate}
  \item first item
  \item second item
  \item third item
\end{enumerate}
\end{verbatim}
Alternative numbering styles can be achieved by inserting an optional argument in square brackets to each \verb"item", e.g.\ \verb"\item[(i)] first item"\, to create a list numbered with roman numerals at level one.

Bulleted lists are produced using the \texttt{itemize} environment. For example,
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
was produced by
\begin{verbatim}
\begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
\end{itemize}
\end{verbatim}

\subsection{Figures}

The \texttt{interact} class file will deal with positioning your figures in the same way as standard \LaTeX. It should not normally be necessary to use the optional \texttt{[htb]} location specifiers of the \texttt{figure} environment in your manuscript; you may, however, find the \verb"[p]" placement option or the \verb"endfloat" package useful if a journal insists on the need to separate figures from the text.

Figure captions appear below the figures themselves, therefore the \verb"\caption" command should appear after the body of the figure. For example, Figure~\ref{sample-figure} with caption and sub-captions is produced using the following commands:
\begin{verbatim}
\begin{figure}
\centering
\subfloat[An example of an individual figure sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{graph1.eps}}}\hspace{5pt}
\subfloat[A slightly shorter sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{graph2.eps}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line of text.} \label{sample-figure}
\end{figure}
\end{verbatim}
\begin{figure}
\centering
\subfloat[An example of an individual figure sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{graph1.eps}}}\hspace{5pt}
\subfloat[A slightly shorter sub-caption.]{%
\resizebox*{5cm}{!}{\includegraphics{graph2.eps}}}
\caption{Example of a two-part figure with individual sub-captions
 showing that captions are flush left and justified if greater
 than one line of text.} \label{sample-figure}
\end{figure}

To ensure that figures are correctly numbered automatically, the \verb"\label" command should be included just after the \verb"\caption" command, or in its argument.

The \verb"\subfloat" command requires \verb"subfig.sty", which is called in the preamble of the \texttt{interactcsesample.tex} file (to allow your choice of an alternative package if preferred) and included in the \textsf{Interact} \LaTeX\ bundle for convenience. Please supply any additional figure macros used with your article in the preamble of your .tex file.

The source files of any figures will be required when the final, revised version of a manuscript is submitted. Authors should ensure that these are suitable (in terms of lettering size, etc.) for the reductions they envisage.

The \texttt{epstopdf} package can be used to incorporate encapsulated PostScript (.eps) illustrations when using PDF\LaTeX, etc. Please provide the original .eps source files rather than the generated PDF images of those illustrations for production purposes.

\subsection{Tables}

The \texttt{interact} class file will deal with positioning your tables in the same way as standard \LaTeX. It should not normally be necessary to use the optional \texttt{[htb]} location specifiers of the \texttt{table} environment in your manuscript; you may, however, find the \verb"[p]" placement option or the \verb"endfloat" package useful if a journal insists on the need to separate tables from the text.

The \texttt{tabular} environment can be used as shown to create tables with single horizontal rules at the head, foot and elsewhere as appropriate. The captions appear above the tables in the \textsf{Interact} style, therefore the \verb"\tbl" command should be used before the body of the table. For example, Table~\ref{sample-table} is produced using the following commands:
\begin{table}
\tbl{Example of a table showing that its caption is as wide as
 the table itself and justified.}
{\begin{tabular}{lcccccc} \toprule
 & \multicolumn{2}{l}{Type} \\ \cmidrule{2-7}
 Class & One & Two & Three & Four & Five & Six \\ \midrule
 Alpha\textsuperscript{a} & A1 & A2 & A3 & A4 & A5 & A6 \\
 Beta & B2 & B2 & B3 & B4 & B5 & B6 \\
 Gamma & C2 & C2 & C3 & C4 & C5 & C6 \\ \bottomrule
\end{tabular}}
\tabnote{\textsuperscript{a}This footnote shows how to include
 footnotes to a table if required.}
\label{sample-table}
\end{table}
\begin{verbatim}
\begin{table}
\tbl{Example of a table showing that its caption is as wide as
 the table itself and justified.}
{\begin{tabular}{lcccccc} \toprule
 & \multicolumn{2}{l}{Type} \\ \cmidrule{2-7}
 Class & One & Two & Three & Four & Five & Six \\ \midrule
 Alpha\textsuperscript{a} & A1 & A2 & A3 & A4 & A5 & A6 \\
 Beta & B2 & B2 & B3 & B4 & B5 & B6 \\
 Gamma & C2 & C2 & C3 & C4 & C5 & C6 \\ \bottomrule
\end{tabular}}
\tabnote{\textsuperscript{a}This footnote shows how to include
 footnotes to a table if required.}
\label{sample-table}
\end{table}
\end{verbatim}

To ensure that tables are correctly numbered automatically, the \verb"\label" command should be included just before \verb"\end{table}".

The \verb"\toprule", \verb"\midrule", \verb"\bottomrule" and \verb"\cmidrule" commands are those used by \verb"booktabs.sty", which is called by the \texttt{interact} class file and included in the \textsf{Interact} \LaTeX\ bundle for convenience. Tables produced using the standard commands of the \texttt{tabular} environment are also compatible with the \texttt{interact} class file.

\subsection{Landscape pages}

If a figure or table is too wide to fit the page it will need to be rotated, along with its caption, through 90$^{\circ}$ anticlockwise. Landscape figures and tables can be produced using the \verb"rotating" package, which is called by the \texttt{interact} class file. The following commands (for example) can be used to produce such pages.
\begin{verbatim}
\setcounter{figure}{1}
\begin{sidewaysfigure}
\centerline{\epsfbox{figname.eps}}
\caption{Example landscape figure caption.}
\label{landfig}
\end{sidewaysfigure}
\end{verbatim}
\begin{verbatim}
\setcounter{table}{1}
\begin{sidewaystable}
 \tbl{Example landscape table caption.}
  {\begin{tabular}{@{}llllcll}
    .
    .
    .
  \end{tabular}}\label{landtab}
\end{sidewaystable}
\end{verbatim}
Before any such float environment, use the \verb"\setcounter" command as above to fix the numbering of the caption (the value of the counter being the number given to the preceding figure or table). Subsequent captions will then be automatically renumbered accordingly. The \verb"\epsfbox" command requires \verb"epsfig.sty", which is called by the \texttt{interact} class file and is also included in the \textsf{Interact} \LaTeX\ bundle for convenience.

Please note that if the \verb"endfloat" package is used, one or both of the commands
\begin{verbatim}
\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
\DeclareDelayedFloatFlavor{sidewaystable}{table}
\end{verbatim}
will need to be included in the preamble of your .tex file, after the \verb"endfloat" package is loaded, in order to process any landscape figures and/or tables correctly.

\subsection{Theorem-like structures}

A predefined \verb"proof" environment is provided by the \texttt{amsthm} package (which is called by the \texttt{interact} class file), as follows:
\begin{proof}
More recent algorithms for solving the semidefinite programming relaxation are particularly efficient, because they explore the structure of the MAX-CUT problem.
\end{proof}
\noindent This was produced by simply typing:
\begin{verbatim}
\begin{proof}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proof}
\end{verbatim}
Other theorem-like environments (theorem, definition, remark, etc.) need to be defined as required, e.g.\ using \verb"\newtheorem{theorem}{Theorem}" in the preamble of your .tex file (see the preamble of \verb"interactcsesample.tex" for more examples). You can define the numbering scheme for these structures however suits your article best. Please note that the format of the text in these environments may be changed if necessary to match the style of individual journals by the typesetter during preparation of the proofs.

\subsection{Mathematics}

\subsubsection{Displayed mathematics}

The \texttt{interact} class file will set displayed mathematical formulas centred on the page without equation numbers if you use the \texttt{displaymath} environment or the equivalent \verb"\[...\]" construction. For example, the equation
\[
 \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
\]
was typeset using the commands
\begin{verbatim}
\[
 \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
\]
\end{verbatim}

For those of your equations that you wish to be automatically numbered sequentially throughout the text for future reference, use the \texttt{equation} environment, e.g.
\begin{equation}
 \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
\end{equation}
was typeset using the commands
\begin{verbatim}
\begin{equation}
 \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
\end{equation}
\end{verbatim}

Part numbers for sets of equations may be generated using the \texttt{subequations} environment, e.g.
\begin{subequations} \label{subeqnexample}
\begin{equation}
     \varepsilon \rho w_{tt}(s,t) = N[w_{s}(s,t),w_{st}(s,t)]_{s},
     \label{subeqnparta}
\end{equation}
\begin{equation}
     w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
     \label{subeqnpartb}
\end{equation}
\end{subequations}
which was typeset using the commands
\begin{verbatim}
\begin{subequations} \label{subeqnexample}
\begin{equation}
     \varepsilon \rho w_{tt}(s,t) = N[w_{s}(s,t),w_{st}(s,t)]_{s},
     \label{subeqnparta}
\end{equation}
\begin{equation}
     w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,   \label{subeqnpartb}
\end{equation}
\end{subequations}
\end{verbatim}
This is made possible by the \texttt{amsmath} package, which is called by the class file. If you put a \verb"\label" just after the \verb"\begin{subequations}" command, references can be made to the collection of equations, i.e.\ `(\ref{subeqnexample})' in the example above. Or, as the example also shows, you can label and refer to each equation individually -- i.e.\ `(\ref{subeqnparta})' and `(\ref{subeqnpartb})'.

Displayed mathematics should be given end-of-line punctuation appropriate to the running text sentence of which it forms a part, if required.

\subsubsection{Math fonts}

\paragraph{Superscripts and subscripts}
Superscripts and subscripts will automatically come out in the correct size in a math environment (i.e.\ enclosed within \verb"\(...\)" or \verb"$...$" commands in running text, or within \verb"\[...\]" or the \texttt{equation} environment for displayed equations). Sub/superscripts that are physical variables should be italic, whereas those that are labels should be roman (e.g.\ $C_p$, $T_\mathrm{eff}$). If the subscripts or superscripts need to be other than italic, they must be coded individually.

\paragraph{Upright Greek characters and the upright partial derivative sign}
Upright lowercase Greek characters can be obtained by inserting the letter `u' in the control code for the character, e.g.\ \verb"\umu" and \verb"\upi" produce $\umu$ (used, for example, in the symbol for the unit microns -- $\umu\mathrm{m}$) and $\upi$ (the ratio of the circumference of a circle to its diameter). Similarly, the control code for the upright partial derivative $\upartial$ is \verb"\upartial". Bold lowercase as well as uppercase Greek characters can be obtained by \verb"{\bm \gamma}", for example, which gives ${\bm \gamma}$, and \verb"{\bm \Gamma}", which gives ${\bm \Gamma}$.

\section*{Acknowledgement(s)}

An unnumbered section, e.g.\ \verb"\section*{Acknowledgements}", may be used for thanks, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.

\section*{Disclosure statement}

An unnumbered section, e.g.\ \verb"\section*{Disclosure statement}", may be used to declare any potential conflict of interest and included \emph{in the non-anonymous version} before any Notes or References, after any Acknowledgements and before any Funding information.

\section*{Funding}

An unnumbered section, e.g.\ \verb"\section*{Funding}", may be used for grant details, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.

\section*{Notes on contributor(s)}

An unnumbered section, e.g.\ \verb"\section*{Notes on contributors}", may be included \emph{in the non-anonymous version} if required. A photograph may be added if requested.

\section*{Nomenclature/Notation}

An unnumbered section, e.g.\ \verb"\section*{Nomenclature}" (or \verb"\section*{Notation}"), may be included if required, before any Notes or References.

\section*{Notes}

An unnumbered `Notes' section may be included before the References (if using the \verb"endnotes" package, use the command \verb"\theendnotes" where the notes are to appear, instead of creating a \verb"\section*").

\section{References}

\subsection{References cited in the text}

References should be cited in Council of Science Editors (CSE) name-year style, e.g.\ `\citep{Rit74,Fel81,Fau02}', or `\ldots see \citet[p.~15]{Smi91}'. When several in-text references occur at the same point, distinguish works by the same author published in different years by placing the years after the author name in chronological sequence, e.g.\ `\citep{Smi70,Smi75}'. For two or more works published by the same author in the same year, add an alphabetic designator to the year in both the in-text reference and the end reference, e.g.\ `(\citealp{And60CJPS}, \citeyear{And60CJB})'. When the authors of two works published in the same year have identical surnames, include their initials in the in-text reference and separate the two in-text references by a semicolon and a space, e.g.\ `\citep{DawJ86,DawM86}'. If a work has two authors, give both names in the in-text reference, e.g.\ `\citep{Wei74}'. If a reference has three or more authors, give only the first author's name followed by `et~al.' and the year of publication, e.g.\ `\citep{Och03}'. If the first author's names and the years of publication are identical for several references, include enough co-author names to eliminate ambiguity, e.g.\ `(Martinez, Fuentes, et~al. 1990; Martinez, Fuentes, Ortiz, et~al. 1990)'. For further details on this reference style, see the Instructions for Authors on the Taylor \& Francis website.

Each bibliographic entry has a key, which is assigned by the author and is used to refer to that entry in the text. In this document, the key \verb"Ant97" in the citation form \verb"\citep{Ant97}" produces `\citep{Ant97}', and the keys \verb"{Sha78,AG98,BGC04}" in the citation form \verb"\citep{Sha78,AG98,BGC04}" produce `\citep{Sha78,AG98,BGC04}'. The appropriate citation style for different situations can be obtained, for example, by \verb"\citet{IOM75}" for `\citet{IOM75}', \verb"\citealt{SRW05}" for `\citealt{SRW05}', or \verb"\citealp{Lee03}" for `\citealp{Lee03}'. Citation of the year alone may be produced by \verb"\citeyear{Ste64}", i.e.\ `\citeyear{Ste64}', or \verb"\citeyearpar{Ovi95}", i.e.\ `\citeyearpar{Ovi95}', or of the author(s) alone by \verb"\citeauthor{Wei03}", i.e.\ `\citeauthor{Wei03}'. Optional notes may be included at the beginning and/or end of a citation by the use of square brackets, e.g.\ \verb"\citep[see][p.~73-–77]{PI51}" produces `\citep[see][p.~73--77]{PI51}'; \verb"\citep[e.g.][]{Sch02}" produces `\citep[e.g.][]{Sch02}'. A `plain' \verb"\cite" command will produce the same results as a \verb"\citet", i.e.\ \verb"\cite{Ant03}" will produce `\cite{Ant03}'.

\subsection{The list of references}

References should be listed at the end of the main text in alphabetical order by author, then chronologically.
If there is no identifiable author, use e.g. `\citep{Hbk00}'.
The year of publication is required for all reference types; for newspaper articles and patents, provide the full date of publication including the month and day of the month.
If a date of publication is impossible to find, use `\citeyear{LedND}' in its place. The following list shows some sample references prepared in the Taylor \& Francis CSE name-year style.

\begin{thebibliography}{}

\bibitem[Ambudkar and Gottesman(1998)]{AG98}
Ambudkar~SV, Gottesman~MM, editors. 1998. ABC transporters: biomedical,
  cellular, and molecular aspects. San Diego (CA): Academic Press. (Methods
  in enzymology; vol. 292).

\bibitem[Andrews(1960a)]{And60CJPS}
Andrews~JE. 1960a. Cold hardiness of sprouting wheat as affected by duration of
  hardening and hardening temperature. Can J Plant Sci. 40(1):93--102.

\bibitem[Andrews(1960b)]{And60CJB}
Andrews~JE. 1960b. Cold hardening and cold hardiness of young winter rye
  seedlings as affected by stage of development and temperature. Can J Bot.
  38(3):353--363.

\bibitem[Antani et~al.(2003)]{Ant03}
Antani~S, Long~LR, Thoma~GR, Lee~DJ. 2003. Anatomical shape representation in
  spine x-ray images. Paper presented at: VIIP 2003. Proceedings of the
  3rd IASTED International Conference on Visualization, Imaging and
  Image Processing; Sep 8--10; Benalmadena, Spain.

\bibitem[Antonioli(1997)]{Ant97}
Antonioli~GE, editor. 1997. Pacemaker leads 1997. Proceedings of the 3rd
  International Symposium on Pacemaker Leads; Sep 11--13; Ferrara, Italy.
  Bologna: Monducci Editore.

\bibitem[Berrino et~al.(2004)]{BGC04}
Berrino~F, Gatta~G, Crosignani~P. 2004. [Case-control evaluation of screening
  efficacy]. Epidemiol Prev. 28:354--359. Italian.

\bibitem[Dawson~J(1986)]{DawJ86}
Dawson~J. 1986. Animal experiments: conference report. BMJ.
  292(6536):1654--1655.

\bibitem[Dawson~M(1986)]{DawM86}
Dawson~M. 1986. Some examples of necessary continuation and
  possible discontinuation of animal experiments. Acta Physiol Scand Suppl.
  554:194--197.

\bibitem[Fauci(2002)]{Fau02}
Fauci~AS. 2002. Smallpox vaccination policy -- the need for dialogue. N Engl J
  Med. 346(17):1319--1320.

\bibitem[Feller(1981)]{Fel81}
Feller~BA. 1981. Health characteristics of persons with chronic activity
  limitation, United States, 1979. Hyattsville (MD): National Center for
  Health Statistics (US). Report No.: VHS-SER-10/137. Available from: NTIS,
  Springfield, VA; PB88-228622.

\bibitem[Handbook\ldots(2000)]{Hbk00}
Handbook of geriatric drug therapy. 2000. Springhouse (PA): Springhouse.

\bibitem[IOM(1975)]{IOM75}
[IOM] Institute of Medicine (US). 1975. Legalized abortion and the public health:
  report of a study by a committee of the Institute of Medicine. Washington
  (DC): National Academy of Sciences.

\bibitem[Lederer({[date unknown]})]{LedND}
Lederer~J. {[date unknown]}. Alimentation et cancer [Diet and cancer].
  Brussels: Nauwelaerts.

\bibitem[Lee et~al.(2003)]{Lee03}
Lee~DJ, Bates~D, Dromey~C, Xu~X, Antani~S. 2003. An imaging system correlating
  lip shapes with tongue contact patterns for speech pathology research. In:
  Krol~M, Mitra~S, Lee~DJ, editors. CMBS 2003. Proceedings of the 16th IEEE
  Symposium on Computer-Based Medical Systems; 2003 Jun 26--27; New York. Los
  Alamitos (CA): IEEE Computer Society. p.~307--313.

\bibitem[Ochi et~al.(2003)]{Och03}
Ochi~K, Sugiura~N, Komatsuzaki~Y, Nishino~H, Ohashi~T. 2003. Patency of
  inferior meatal antrostomy. Auris Nasus Larynx. 30 Suppl:S57--S60.

\bibitem[Oviedo(1995)]{Ovi95}
Oviedo~S. 1995. Adolescent pregnancy: voices heard in the everyday lives of
  pregnant teenagers [master's thesis]. Denton (TX): University of North Texas.

\bibitem[Piaget and Inhelder(1951)]{PI51}
Piaget~J, Inhelder~B. 1951. La gen{\`e}se de l'id{\'e}e de hasard chez l'enfant
  [The origin of the idea of chance in the child]. Paris: Presses
  Universitaires de France.

\bibitem[Ritzmann(1974)]{Rit74}
Ritzmann~RE. 1974. The snapping mechanism of \textit{Alpheid} shrimp
  [dissertation]. Charlottesville (VA): University of Virginia.

\bibitem[Savage et~al.(2005)]{SRW05}
Savage~E, Ramsay~M, White~J, Beard~S, Lawson~H, Hunjan~R, Brown~D. 2005. Mumps
  outbreaks across England and Wales in 2004: observational study. BMJ.
  [cited~2005 May 31]; 330(7500):1119--1120. Available from:
  http://bmj.bmjjournals.com/cgi/reprint/330/7500/1119

\bibitem[Schott and Priest(2002)]{Sch02}
Schott~J, Priest~J. 2002. Leading antenatal classes: A practical guide. 2nd ed.
  Boston (MA): Books for Midwives.

\bibitem[Shakelford(1978)]{Sha78}
Shakelford~RT. 1978. Surgery of the alimentary tract. Philadelphia (PA): W.B.
  Saunders; Chapter 2, Esophagoscopy, p.~29--40.

\bibitem[Smith(1970)]{Smi70}
Smith~CE. 1970. Studies on arbovirus epidemiology associated with established
  and developing rice culture. Introduction. Trans R Soc Trop Med Hyg.
  64(4):481--482.

\bibitem[Smith(1975)]{Smi75}
Smith~CE. 1975. The significance of mosquito longevity and blood-feeding
  behaviour in the dynamics of arbovirus infections. Med Biol. 53(5):288--294.

\bibitem[Smith(1991)]{Smi91}
Smith~KL. 1991. New dangers in our field [editorial]. Am J Nucl Eng.
  13(1):15--16.

\bibitem[Stearns(1864)]{Ste64}
Stearns~AA. 1864. Armory {S}quare {H}ospital nursing diary. 70 leaves. Located
  at: History of Medicine Division, National Library of Medicine, Bethesda, MD;
  MS B 372.

\bibitem[Weinstein and Swartz(1974)]{Wei74}
Weinstein~L, Swartz~MN. 1974. Pathologic properties of invading organisms. In:
  Sodeman~WA, editor. Pathologic physiology: Mechanisms of disease. 5th ed.
  Philadelphia (PA): Saunders; p. 135--140.

\bibitem[Weiss(2003 Apr~11)]{Wei03}
Weiss~R. 2003 Apr 11. Study shows problems in cloning people: researchers find
  replicating primates will be harder than other mammals. Washington Post (Home
  Ed.). Sect.~A:12 (col.~1).

\end{thebibliography}
\bigskip
\noindent This was produced by typing:
\begin{verbatim}
\begin{thebibliography}{}

\bibitem[Ambudkar and Gottesman(1998)]{AG98}
Ambudkar~SV, Gottesman~MM, editors. 1998. ABC transporters: biomedical,
 cellular, and molecular aspects. San Diego (CA): Academic Press.
 (Methods in enzymology; vol. 292).

\bibitem[Andrews(1960a)]{And60CJPS}
Andrews~JE. 1960a. Cold hardiness of sprouting wheat as affected by
 duration of hardening and hardening temperature. Can J Plant Sci.
 40(1):93--102.

\bibitem[Andrews(1960b)]{And60CJB}
Andrews~JE. 1960b. Cold hardening and cold hardiness of young winter
 rye seedlings as affected by stage of development and temperature.
 Can J Bot. 38(3):353--363.

\bibitem[Antani et~al.(2003)]{Ant03}
Antani~S, Long~LR, Thoma~GR, Lee~DJ. 2003. Anatomical shape
 representation in spine x-ray images. Paper presented at: VIIP 2003.
 Proceedings of the 3rd IASTED International Conference on
 Visualization, Imaging and Image Processing; Sep 8--10; Benalmadena,
 Spain.

\bibitem[Antonioli(1997)]{Ant97}
Antonioli~GE, editor. 1997. Pacemaker leads 1997. Proceedings of the
 3rd International Symposium on Pacemaker Leads; Sep 11--13; Ferrara,
 Italy. Bologna: Monducci Editore.

\bibitem[Berrino et~al.(2004)]{BGC04}
Berrino~F, Gatta~G, Crosignani~P. 2004. [Case-control evaluation of
 screening efficacy]. Epidemiol Prev. 28:354--359. Italian.

\bibitem[Dawson~J(1986)]{DawJ86}
Dawson~J. 1986. Animal experiments: Conference report. BMJ.
 292(6536):1654--1655.

\bibitem[Dawson~M(1986)]{DawM86}
Dawson~M. 1986. Some examples of necessary continuation and possible
 discontinuation of animal experiments. Acta Physiol Scand Suppl.
 554:194--197.

\bibitem[Fauci(2002)]{Fau02}
Fauci~AS. 2002. Smallpox vaccination policy -- the need for dialogue.
 N Engl J Med. 346(17):1319--1320.

\bibitem[Feller(1981)]{Fel81}
Feller~BA. 1981. Health characteristics of persons with chronic
 activity limitation, United States, 1979. Hyattsville (MD): National
 Center for Health Statistics (US). Report No.: VHS-SER-10/137.
 Available from: NTIS, Springfield, VA; PB88-228622.

\bibitem[Handbook\ldots(2000)]{Hbk00}
Handbook of geriatric drug therapy. 2000. Springhouse (PA):
 Springhouse.

\bibitem[IOM(1975)]{IOM75}
[IOM] Institute of Medicine (US). 1975. Legalized abortion and the
 public health: report of a study by a committee of the Institute of
 Medicine. Washington (DC): National Academy of Sciences.

\bibitem[Lederer({[date unknown]})]{LedND}
Lederer~J. {[date unknown]}. Alimentation et cancer [Diet and cancer].
 Brussels: Nauwelaerts.

\bibitem[Lee et~al.(2003)]{Lee03}
Lee~DJ, Bates~D, Dromey~C, Xu~X, Antani~S. 2003. An imaging system
 correlating lip shapes with tongue contact patterns for speech
 pathology research. In: Krol~M, Mitra~S, Lee~DJ, editors. CMBS 2003.
 Proceedings of the 16th IEEE Symposium on Computer-Based Medical
 Systems; 2003 Jun 26--27; New York. Los Alamitos (CA): IEEE Computer
 Society. p.~307--313.

\bibitem[Ochi et~al.(2003)]{Och03}
Ochi~K, Sugiura~N, Komatsuzaki~Y, Nishino~H, Ohashi~T. 2003. Patency of
  inferior meatal antrostomy. Auris Nasus Larynx. 30 Suppl:S57--S60.

\bibitem[Oviedo(1995)]{Ovi95}
Oviedo~S. 1995. Adolescent pregnancy: voices heard in the everyday
 lives of pregnant teenagers [master's thesis]. Denton (TX): University
 of North Texas.

\bibitem[Piaget and Inhelder(1951)]{PI51}
Piaget~J, Inhelder~B. 1951. La gen{\`e}se de l'id{\'e}e de hasard chez
 l'enfant [The origin of the idea of chance in the child]. Paris:
 Presses Universitaires de France.

\bibitem[Ritzmann(1974)]{Rit74}
Ritzmann~RE. 1974. The snapping mechanism of \textit{Alpheid} shrimp
 [dissertation]. Charlottesville (VA): University of Virginia.

\bibitem[Savage et~al.(2005)]{SRW05}
Savage~E, Ramsay~M, White~J, Beard~S, Lawson~H, Hunjan~R, Brown~D. 2005.
 Mumps outbreaks across England and Wales in 2004: observational study.
 BMJ. [cited~2005 May 31]; 330(7500):1119--1120. Available from:
 http://bmj.bmjjournals.com/cgi/reprint/330/7500/1119

\bibitem[Schott and Priest(2002)]{Sch02}
Schott~J, Priest~J. 2002. Leading antenatal classes: A practical guide.
 2nd ed. Boston (MA): Books for Midwives.

\bibitem[Shakelford(1978)]{Sha78}
Shakelford~RT. 1978. Surgery of the alimentary tract. Philadelphia
 (PA): W.B. Saunders; Chapter 2, Esophagoscopy, p.~29--40.

\bibitem[Smith(1970)]{Smi70}
Smith~CE. 1970. Studies on arbovirus epidemiology associated with
 established and developing rice culture. Introduction. Trans R Soc
 Trop Med Hyg. 64(4):481--482.

\bibitem[Smith(1975)]{Smi75}
Smith~CE. 1975. The significance of mosquito longevity and
 blood-feeding behaviour in the dynamics of arbovirus infections.
 Med Biol. 53(5):288--294.

\bibitem[Smith(1991)]{Smi91}
Smith~KL. 1991. New dangers in our field [editorial]. Am J Nucl Eng.
 13(1):15--16.

\bibitem[Stearns(1864)]{Ste64}
Stearns~AA. 1864. Armory {S}quare {H}ospital nursing diary. 70 leaves. 
 Located at: History of Medicine Division, National Library of 
 Medicine, Bethesda, MD; MS B 372.

\bibitem[Weinstein and Swartz(1974)]{Wei74}
Weinstein~L, Swartz~MN. 1974. Pathologic properties of invading 
 organisms. In: Sodeman~WA, editor. Pathologic physiology: Mechanisms 
 of disease. 5th ed. Philadelphia (PA): Saunders; p. 135--140.

\bibitem[Weiss(2003 Apr~11)]{Wei03}
Weiss~R. 2003 Apr 11. Study shows problems in cloning people:
 researchers find replicating primates will be harder than other
 mammals. Washington Post (Home Ed.). Sect.~A:12 (col.~1).

\end{thebibliography}
\end{verbatim}
\bigskip
\noindent Each entry takes the form:
\begin{verbatim}
\bibitem[authors' names(date of publication)]{key}
 Bibliography entry
\end{verbatim}
where `\texttt{authors' names}' is the list of names to appear where the \verb"bibitem" is cited in the text, and `\texttt{key}' is the tag that is to be used as an argument for the \verb"\cite{}" commands in the text of the article. `\texttt{Bibliography entry}' is the material that is to appear in the list of references, suitably formatted. The commands
\begin{verbatim}
\usepackage{natbib}
\bibpunct[, ]{(}{)}{;}{a}{}{,}
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}
\end{verbatim}
need to be included in the preamble of your .tex file in order to generate the citations and bibliography as described above.

Instead of typing the bibliography by hand, you may prefer to create the list of references using a \textsc{Bib}\TeX\ database. The \texttt{tfcse.bst} file needs to be in your working folder or an appropriate directory, and the lines
\begin{verbatim}
\bibliographystyle{tfcse}
\bibliography{interactcsesample}
\end{verbatim}
included where the list of references is to appear, where \texttt{tfcse.bst} is the name of the \textsc{Bib}\TeX\ bibliography style file for Taylor \& Francis' CSE name-year reference style and \texttt{interactcsesample.bib} is the bibliographic database included with the \textsf{Interact}-CSE \LaTeX\ bundle (to be replaced with the name of your own .bib file). \LaTeX/\textsc{Bib}\TeX\ will extract from your .bib file only those references that are cited in your .tex file and list them in the References section.

Please include a copy of your .bib file and/or the final generated .bbl file among your source files if your .tex file does not contain a reference list in a \texttt{thebibliography} environment.

\section{Appendices}

Any appendices should be placed after the list of references, beginning with the command \verb"\appendix" followed by the command \verb"\section" for each appendix title, e.g.
\begin{verbatim}
\appendix
\section{This is the title of the first appendix}
\section{This is the title of the second appendix}
\end{verbatim}
produces:\medskip

\noindent\textbf{Appendix A. This is the title of the first appendix}\medskip

\noindent\textbf{Appendix B. This is the title of the second appendix}\medskip

\noindent Subsections, equations, figures, tables, etc.\ within appendices will then be automatically numbered as appropriate. Some theorem-like environments may need to have their counters reset manually (e.g.\ if they are not numbered within sections in the main text). You can achieve this by using \verb"\numberwithin{remark}{section}" (for example) just after the \verb"\appendix" command.

Note that if the \verb"endfloat" package is used on a document containing any appendices, the \verb"\processdelayedfloats" command must be included immediately before the \verb"\appendix" command in order to ensure that the floats belonging to the main body of the text are numbered as such.

%\processdelayedfloats %%% See above for an explanation of why this command might be needed here.

\appendix

\section{Troubleshooting}

Authors may occasionally encounter problems with the preparation of a manuscript using \LaTeX. The appropriate action to take will depend on the nature of the problem:
\begin{enumerate}
\item[(i)] If the problem is with \LaTeX\ itself, rather than with the actual macros, please consult an appropriate \LaTeXe\ manual for initial advice. If the solution cannot be found, or if you suspect that the problem does lie with the macros, then please contact Taylor \& Francis for assistance (\texttt{latex.helpdesk@tandf.co.uk}), clearly stating the title of the journal to which you are submitting.
\item[(ii)] Problems with page make-up (e.g.\ occasional overlong lines of text; figures or tables appearing out of order): please do not try to fix these using `hard' page make-up commands -- the typesetter will deal with such problems. (You may, if you wish, draw attention to particular problems when submitting the final version of your manuscript.)
\item[(iii)] If a required font is not available on your system, allow \TeX\ to substitute the font and specify which font is required in a covering letter accompanying your files.
\end{enumerate}

\section{Obtaining the template and class file}

\subsection{Via the Taylor \& Francis website}

This article template and the \texttt{interact} class file may be obtained via the `Instructions for Authors' pages of selected Taylor \& Francis journals.

Please note that the class file calls up the open-source \LaTeX\ packages booktabs.sty, epsfig.sty and rotating.sty, which will, for convenience, unpack with the downloaded template and class file. The template calls for natbib.sty and subfig.sty, which are also supplied for convenience.

\subsection{Via e-mail}

This article template, the \texttt{interact} class file and the associated open-source \LaTeX\ packages are also available via e-mail. Requests should be addressed to \texttt{latex.helpdesk@tandf.co.uk}, clearly stating for which journal you require the template and class file.

\end{document}

### 2020-12-06 tex/interactcsesample.tex
rectify the Introduction section

@@
 \begin{keywords}
-Sections; lists; figures; tables; mathematics; fonts; references; appendices
+Psammophytes; sand burial; \textit{Spinifex littoreus}; responses, plant osmotic stress
 \end{keywords}
@@
 
-In order to assist authors in the process of preparing a manuscript for a journal, the Taylor \& Francis `\textsf{Interact}' layout style has been implemented as a \LaTeXe\ class file based on the \texttt{article} document class.
-A \textsc{Bib}\TeX\ bibliography style file and a sample bibliography are also provided in order to assist with the formatting of your references.
+\label{Introduction-1}
+% 主要介绍沙生植物对海岸生态系统对重要意义
+Sand dunes occupy a finite area in coastal regions, but they are characterized by providing multiple ecological services, and play an important role in the sustainable development in those regions with rising sea levels, surface subsidence and coastal hazards (Martínez et al.
+2004, De Battisti \& Griffin 2020).
+Recently, due to the influence of both climate change and anthropogenic activities, many coastal sand dunes have been modified or destroyed, and this can, or has potentially led to the retreat of coastlines, disappearance of habitats, loss of biodiversity, and severe degradation of ecosystem functions in coastal sand dunes (Feagin et al.
+2005, Schlacher et al.
+2011, Qu et al.
+2017).
+With the rapid development of economy in China, most of the coastal sand dunes were also eradicated due to real estate and infrastructure development and tourism activities.
+Almost no well-preserved coastal sand dunes are left, which apart from the loss of ecological functions and habitats, may ultimately result in coastal erosion and the loss of life, property and economy (Yang et al.
+2017).
+Hard engineering structures have been proved to be costly and detrimental for the protection of coastal regions, so it is very important to select natural and environmentally friendly methods for both the protection and restoration of the remaining coastal dune systems (Hanley et al.
+2014).
 
-Commands that differ from or are provided in addition to standard \LaTeXe\ are described in this document, which is \emph{not} a substitute for a \LaTeXe\ tutorial.
+\label{Introduction-2}
+% 主要介绍沙埋与沙生植物对关系
+Psammophytes can build and stabilize coastal dunes, which will favor the restoration of their ecological functions due to their specific adaptive strategies (Yuan et al.
+1993, Nolet et al.
+2018, De Battisti \& Griffin 2020).
+However, only a few species can survive in these ecosystems due to the harsh environmental stress, such as drought, salt spray, strong winds, and especially the frequent and intensive sand burial (Maun \& Lapierre 1986, Hesp 1991, Maun 1994, Maun 1996, Zhao et al.
+2014, Du \& Hesp 2020).
+Sand burial is commonly considered as the selective force for coastal plant regeneration and survival (Moreno-Casasola 1986, Maun 1996, Hwang et al.
+2016, Wang et al.
+2019), which can decrease and even eliminate the psammophytes if the sand burial levels are over their tolerance capacity, ultimately giving rise to the alteration of species composition in coastal dune systems (Maun \& Perumal 1999, Miller 2015).
 
-The \texttt{interactcsesample.tex} file can be used as a template for a manuscript by cutting, pasting, inserting and deleting text as appropriate, using the preamble and the \LaTeX\ environments provided (e.g.\ \verb"\begin{abstract}", \verb"\begin{keywords}").
+\label{Introduction-3}
+% 这一段主要讲海岸沙生植物耐沙埋能力的用处
+The tolerance capacity to different sand burial levels is varied among species, which finally affect the initial and subsequent coastal dune development and morphology (Hesp 1989).
+Generally, the growth of most psammophytes can be expected to be stimulated with low to moderate sand burial (Zhou et al.
+2015a, Harris et al.
+2017, Brown \& Zinnert 2018, Wang et al.
+2019), while intensive sand burial will decrease its survival and per plant biomass (Maun 1996, Franks \& Peterson 2003).
+Wang et al.
+(2012) demonstrated that both stem height in the vertical direction and leaf weight of Messerschmidia sibirica were increased with light sand burial, while all decreased with moderate treatments contrasted with the control.
+In addition, Zhou et al.
+(2015b) showed that the growth of Artemisia desterorum was enhanced with moderate sand burial, but inhibited with intense sand burial.
+Elongation of stolons, upward growth of ramets, and development of new adventitious roots are the main adaptive strategies for plants to sand burial, potentially leading to an alteration in the biomass allocation of psammophytes in coastal sand dunes (Dech \& Maun 2006, Frosini et al.
+2012, Mendoza-González et al.
+2014, Luo et al.
+2018).
 
-\subsection{The \textsf{Interact} class file}\label{class}
+\label{Introduction-4}
+% 这一段主要介绍老鼠乐与研究去意义
+Spinifex littoreus, a herbaceous plant, is the dominant species in coastal foredunes in South China.
+It often grows vigorously above the backshore, and in the more dynamic foredune, while it declines in the more stabilized backdunes in similarity to its Australian and NZ cousins S.
+hirsutus and S.
+sericeus (Hesp 1989, 2002).
+Its peak growth occurs in summer, with two growth forms, including elongation of horizontal stolons and upward growth of vertical ramets, which sprout out from the same vegetative reproduction, and usually can be recognized as the same ramets (Jackson et al.
+1986).
+The leaf apex of S.
+littoreus is very sharp and hard, which makes it difficult to be intruded, and is usually recognized as one of the excellent species for sand dune fixation in this region (Yang et al.
+2017).
+Frequent typhoons often occur in the growing season of this species in South China, which causes severe sand burial on S.
+littoreus, particularly its stolons on nebkhas forming the foredune zone (Yang et al.
+2017) (Figure 1).
+However, the tolerance capacity of this species to sand burial is still unclear at present, and how this species revitalized in the frequent sand burial is less studied.
+Furthermore, local government has planted an invasive species Casuarinas equisetifolia for the stabilization of nebkhas originally formed by S.littoreus, which causes severe damage to this species, and will inevitably increase the fragility of coastal dune ecosystems in this region (Figure 2).
+Therefore, understanding the adaptive strategies of S.
+littoreus to sand burial levels, and its role in the stabilization of coastal dunes are very crucial for the effective coastal management and conservation in South China.
 
-The \texttt{interact} class file preserves the standard \LaTeXe\ interface such that any document that can be produced using \texttt{article.cls} can also be produced with minimal alteration using the \texttt{interact} class file as described in this document.
+\begin{figure}
+  \centering
+  \subfloat[\textit{S. littoreus} under natural sand burial.]{%
+  \resizebox*{6cm}{!}{\includegraphics{../figs/sand_buried_plants.jpg}}}\hspace{5pt}
+  \subfloat[\textit{C. equisetifolia} danmaged by sand burial.]{%
+  \resizebox*{6cm}{!}{\includegraphics{../figs/damaged_trees.jpg}}}
+  \caption{(a) Intensive sand burial on the Spinifex littoreus nebkhas on Pingtan island after typhoon Soudelor (1513) landed in Putian City, Fujian Province, China in August, 2015.
+(b)The nebkhas formed by Spinifex littoreus was stabilized by the planting of an invasive species Casuarinas equisetifolia seedlings on Pingtan Island, Fujian Province, China.}
+  \label{sample-pic}
+\end{figure}
 
-If your article is accepted for publication it will be typeset as the journal requires in Minion Pro and/or Myriad Pro.
-Since most authors will not have these fonts installed, the page make-up is liable to alter slightly with the change of font.
-Also, the \texttt{interact} class file produces only single-column format, which is preferred for peer review and will be converted to two-column format by the typesetter if necessary during preparation of the proofs.
-Please therefore do not try to match the typeset format exactly, but use the standard \LaTeX\ fonts instead and ignore details such as slightly long lines of text or figures/tables not appearing in exact synchronization with their citations in the text: these details will be dealt with by the typesetter.
-Similarly, it is unnecessary to spend time addressing warnings in the log file -- if your .tex file compiles to produce a PDF document that correctly shows how you wish your paper to appear, such warnings will not prevent your source files being imported into the typesetter's program.
+\label{Introduction-5}
+% 我们的研究假设和研究思路
+% 我们认为不同的沙埋情形将改变植株的生长方式，是该植物能够适应台风带来的强烈沙埋的关键性因素。
+In this study, we assume that the different sand burial changes the growth process of S.
+littoreus, which is the key factor for the plants to adapt to the intense sand burial.
+Then, the vertical height of ramets, horizontal length of stolons, and biomass allocation of adventitious roots, stems and leaves on stolons of S.
+littoreus under different sand burial levels were simulated and measured in a field experiment, in a growing season on Pingtan Island, Fujian Province, South China.
 
-\subsection{Submission of manuscripts prepared using \emph{\LaTeX}}
-
-Manuscripts for possible publication should be submitted to the Editors for review as directed in the journal's Instructions for Authors, and in accordance with any technical instructions provided in the journal's ScholarOne Manuscripts or Editorial Manager site.
-Your \LaTeX\ source file(s), the class file and any graphics files will be required in addition to the final PDF version when final, revised versions of accepted manuscripts are submitted.
-
-Please ensure that any author-defined macros used in your article are gathered together in the preamble of your .tex file, i.e.\ before the \verb"\begin{document}" command.
-Note that if serious problems are encountered in the coding of a document (missing author-defined macros, for example), the typesetter may resort to rekeying it.
-
-\section{Using the \texttt{interact} class file}
-
-For convenience, simply copy the \texttt{interact.cls} file into the same directory as your manuscript files (you do not need to install it in your \TeX\ distribution).
-In order to use the \texttt{interact} document class, replace the command \verb"\documentclass{article}" at the beginning of your document with the command \verb"\documentclass{interact}".
-
-The following document-class options should \emph{not} be used with the \texttt{interact} class file:
-\begin{itemize}
-  \item \texttt{10pt}, \texttt{11pt}, \texttt{12pt} -- unavailable;
-  \item \texttt{oneside}, \texttt{twoside} -- not necessary, \texttt{oneside} is the default;
-  \item \texttt{leqno}, \texttt{titlepage} -- should not be used;
-  \item \texttt{twocolumn} -- should not be used (see Subsection~\ref{class});
-  \item \texttt{onecolumn} -- not necessary as it is the default style.
-\end{itemize}
-To prepare a manuscript for a journal that is printed in A4 (two column) format, use the \verb"largeformat" document-class option provided by \texttt{interact.cls}; otherwise the class file produces pages sized for B5 (single column) format by default.
+\section{Material and Methods}
+\subsection{Study area}
+% 如果手稿要给期刊A4打印了，用 document-class 提供的 largeformat 参数（由 interact.cls）提供
+% To prepare a manuscript for a journal that is printed in A4 (two column) format, use the \verb"largeformat" document-class option provided by \texttt{interact.cls}; otherwise the class file produces pages sized for B5 (single column) format by default.
 The \texttt{geometry} package should not be used to make any further adjustments to the page dimensions.
 
-%If your manuscript has supplementary content you can use the \verb"interact" class file to prepare all or part of it using the \verb"suppldata" document-class option, which will suppress the `article history' date.
-This option \emph{must not} be used on any primary content.
-Note that authors are solely responsible for the preparation of all supplemental material.
+\subsection{Methods}
 
-\section{Additional features of the \texttt{interact} class file}
+\section{Results}
 
-\subsection{Title, authors' names and affiliations, abstracts and article types}
+\subsection{Influence of sand burial on the height of vertical ramets}
 
-The title should be generated at the beginning of your article using the \verb"\maketitle" command.
-In the final version the author name(s) and affiliation(s) must be followed immediately by \verb"\maketitle" as shown below in order for them to be displayed in your PDF document.
-To prepare an anonymous version for double-blind peer review, you can put the \verb"\maketitle" between the \verb"\title" and the \verb"\author" in order to hide the author name(s) and affiliation(s) temporarily.
-Next you should include the abstract if your article has one, enclosed within an \texttt{abstract} environment.
-The \verb"\articletype" command is also provided as an \emph{optional} element which should \emph{only} be included if your article actually needs it.
-For example, the titles for this document begin as follows:
-\begin{verbatim}
-\articletype{ARTICLE TEMPLATE}
+\subsection{Influence of sand burial on the length of horizontal stolons}
 
-\title{Taylor \& Francis \LaTeX\ template for authors (\textsf{Interact}
-layout + Council of Science Editors name-year reference style)}
-
-\author{
-\name{A.~N. Author\textsuperscript{a}\thanks{CONTACT A.~N. Author.
-Email: latex.helpdesk@tandf.co.uk} and John Smith\textsuperscript{b}}
-\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton
-Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik,
-Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany} }
-
-\maketitle
-
-\begin{abstract}
-This template is for authors who are preparing a manuscript for a
-Taylor \& Francis journal using the \LaTeX\ document preparation system
-and the \texttt{interact} class file, which is available via selected
-journals' home pages on the Taylor \& Francis website.
-\end{abstract}
-\end{verbatim}
-
-An additional abstract in another language (preceded by a translation of the article title) may be included within the \verb"abstract" environment if required.
-
-A graphical abstract may also be included if required. Within the \verb"abstract" environment you can include the code
-\begin{verbatim}
-\\\resizebox{25pc}{!}{\includegraphics{abstract.eps}}
-\end{verbatim}
-where the graphical abstract is to appear, where \verb"abstract.eps" is the name of the file containing the graphic (note that \verb"25pc" is the recommended maximum width, expressed in pica, for the graphical abstract in your manuscript).
-
-\subsection{Abbreviations}
-
-A list of abbreviations may be included if required, enclosed within an \texttt{abbreviations} environment, i.e.\ \verb"\begin{abbreviations}"\ldots\verb"\end{abbreviations}", immediately following the \verb"abstract" environment.
-
-\subsection{Keywords}
-
-A list of keywords may be included if required, enclosed within a \texttt{keywords} environment, i.e.\ \verb"\begin{keywords}"\ldots\verb"\end{keywords}".
-Additional keywords in other languages (preceded by a translation of the word `keywords') may also be included within the \verb"keywords" environment if required.
-
-\subsection{Subject classification codes}
-
-AMS, JEL or PACS classification codes may be included if required.
-The \texttt{interact} class file provides an \texttt{amscode} environment, i.e.\ \verb"\begin{amscode}"\ldots\verb"\end{amscode}", a \texttt{jelcode} environment, i.e.\ \verb"\begin{jelcode}"\ldots\verb"\end{jelcode}", and a \texttt{pacscode} environment, i.e.\ \verb"\begin{pacscode}"\ldots\verb"\end{pacscode}" to assist with this.
-
-\subsection{Additional footnotes to the title or authors' names}
-
-The \verb"\thanks" command may be used to create additional footnotes to the title or authors' names if required. Footnote symbols for this purpose should be used in the order
-$^\ast$~(coded as \verb"$^\ast$"), $\dagger$~(\verb"$\dagger$"), $\ddagger$~(\verb"$\ddagger$"), $\S$~(\verb"$\S$"), $\P$~(\verb"$\P$"), $\|$~(\verb"$\|$"),
-$\dagger\dagger$~(\verb"$\dagger\dagger$"), $\ddagger\ddagger$~(\verb"$\ddagger\ddagger$"), $\S\S$~(\verb"$\S\S$"), $\P\P$~(\verb"$\P\P$").
-
-Note that any \verb"footnote"s to the main text will automatically be assigned the superscript symbols 1, 2, 3, etc.
-by the class file.\footnote{If preferred, the \texttt{endnotes} package may be used to set the notes at the end of your text, before the bibliography.
-The symbols will be changed to match the style of the journal if necessary by the typesetter.}
+\subsection{Influence of sand burial on the biomass allocation}
 
 \section{Some guidelines for using the standard features of \LaTeX}
-
-\subsection{Sections}
-
-The \textsf{Interact} layout style allows for five levels of section heading, all of which are provided in the \texttt{interact} class file using the standard \LaTeX\ commands \verb"\section", \verb"\subsection", \verb"\subsubsection", \verb"\paragraph" and \verb"\subparagraph".
-Numbering will be automatically generated for all these headings by default.
-
-\subsection{Lists}
-
-Numbered lists are produced using the \texttt{enumerate} environment, which will number each list item with arabic numerals by default. For example,
-\begin{enumerate}
-  \item first item
-  \item second item
-  \item third item
-\end{enumerate}
-was produced by
-\begin{verbatim}
-\begin{enumerate}
-  \item first item
-  \item second item
-  \item third item
-\end{enumerate}
-\end{verbatim}
-Alternative numbering styles can be achieved by inserting an optional argument in square brackets to each \verb"item", e.g.\ \verb"\item[(i)] first item"\, to create a list numbered with roman numerals at level one.
-
-Bulleted lists are produced using the \texttt{itemize} environment. For example,
-\begin{itemize}
-  \item First bulleted item
-  \item Second bulleted item
-  \item Third bulleted item
-\end{itemize}
-was produced by
-\begin{verbatim}
-\begin{itemize}
-  \item First bulleted item
-  \item Second bulleted item
-  \item Third bulleted item
-\end{itemize}
-\end{verbatim}
-
-\subsection{Figures}
-
-The \texttt{interact} class file will deal with positioning your figures in the same way as standard \LaTeX.
-It should not normally be necessary to use the optional \texttt{[htb]} location specifiers of the \texttt{figure} environment in your manuscript; you may, however, find the \verb"[p]" placement option or the \verb"endfloat" package useful if a journal insists on the need to separate figures from the text.
-
-Figure captions appear below the figures themselves, therefore the \verb"\caption" command should appear after the body of the figure.
-For example, Figure~\ref{sample-figure} with caption and sub-captions is produced using the following commands:
-\begin{verbatim}
-\begin{figure}
-\centering
-\subfloat[An example of an individual figure sub-caption.]{%
-\resizebox*{5cm}{!}{\includegraphics{graph1.eps}}}\hspace{5pt}
-\subfloat[A slightly shorter sub-caption.]{%
-\resizebox*{5cm}{!}{\includegraphics{graph2.eps}}}
-\caption{Example of a two-part figure with individual sub-captions
- showing that captions are flush left and justified if greater
- than one line of text.} \label{sample-figure}
-\end{figure}
-\end{verbatim}
-\begin{figure}
-\centering
-\subfloat[An example of an individual figure sub-caption.]{%
-\resizebox*{5cm}{!}{\includegraphics{graph1.eps}}}\hspace{5pt}
-\subfloat[A slightly shorter sub-caption.]{%
-\resizebox*{5cm}{!}{\includegraphics{graph2.eps}}}
-\caption{Example of a two-part figure with individual sub-captions
- showing that captions are flush left and justified if greater
- than one line of text.} \label{sample-figure}
-\end{figure}
-
-To ensure that figures are correctly numbered automatically, the \verb"\label" command should be included just after the \verb"\caption" command, or in its argument.
-
-The \verb"\subfloat" command requires \verb"subfig.sty", which is called in the preamble of the \texttt{interactcsesample.tex} file (to allow your choice of an alternative package if preferred) and included in the \textsf{Interact} \LaTeX\ bundle for convenience.
-Please supply any additional figure macros used with your article in the preamble of your .tex file.
-
-The source files of any figures will be required when the final, revised version of a manuscript is submitted.
-Authors should ensure that these are suitable (in terms of lettering size, etc.) for the reductions they envisage.
-
-The \texttt{epstopdf} package can be used to incorporate encapsulated PostScript (.eps) illustrations when using PDF\LaTeX, etc.
-Please provide the original .eps source files rather than the generated PDF images of those illustrations for production purposes.
 
@@
 
-\subsection{Landscape pages}
-
-If a figure or table is too wide to fit the page it will need to be rotated, along with its caption, through 90$^{\circ}$ anticlockwise.
-Landscape figures and tables can be produced using the \verb"rotating" package, which is called by the \texttt{interact} class file.
-The following commands (for example) can be used to produce such pages.
-\begin{verbatim}
-\setcounter{figure}{1}
-\begin{sidewaysfigure}
-\centerline{\epsfbox{figname.eps}}
-\caption{Example landscape figure caption.}
-\label{landfig}
-\end{sidewaysfigure}
-\end{verbatim}
-\begin{verbatim}
-\setcounter{table}{1}
-\begin{sidewaystable}
- \tbl{Example landscape table caption.}
-  {\begin{tabular}{@{}llllcll}
-    .
-    .
-    .
-  \end{tabular}}\label{landtab}
-\end{sidewaystable}
-\end{verbatim}
-Before any such float environment, use the \verb"\setcounter" command as above to fix the numbering of the caption (the value of the counter being the number given to the preceding figure or table).
-Subsequent captions will then be automatically renumbered accordingly.
-The \verb"\epsfbox" command requires \verb"epsfig.sty", which is called by the \texttt{interact} class file and is also included in the \textsf{Interact} \LaTeX\ bundle for convenience.
-
-Please note that if the \verb"endfloat" package is used, one or both of the commands
-\begin{verbatim}
-\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
-\DeclareDelayedFloatFlavor{sidewaystable}{table}
-\end{verbatim}
-will need to be included in the preamble of your .tex file, after the \verb"endfloat" package is loaded, in order to process any landscape figures and/or tables correctly.
-
-\subsection{Theorem-like structures}
-
-A predefined \verb"proof" environment is provided by the \texttt{amsthm} package (which is called by the \texttt{interact} class file), as follows:
-\begin{proof}
-More recent algorithms for solving the semidefinite programming relaxation are particularly efficient, because they explore the structure of the MAX-CUT problem.
-\end{proof}
-\noindent This was produced by simply typing:
-\begin{verbatim}
-\begin{proof}
-More recent algorithms for solving the semidefinite programming
-relaxation are particularly efficient, because they explore the
-structure of the MAX-CUT problem.
-\end{proof}
-\end{verbatim}
-Other theorem-like environments (theorem, definition, remark, etc.) need to be defined as required, e.g.\ using \verb"\newtheorem{theorem}{Theorem}" in the preamble of your .tex file (see the preamble of \verb"interactcsesample.tex" for more examples).
-You can define the numbering scheme for these structures however suits your article best.
-Please note that the format of the text in these environments may be changed if necessary to match the style of individual journals by the typesetter during preparation of the proofs.
-
-\subsection{Mathematics}
-
-\subsubsection{Displayed mathematics}
-
-The \texttt{interact} class file will set displayed mathematical formulas centred on the page without equation numbers if you use the \texttt{displaymath} environment or the equivalent \verb"\[...\]" construction.
-For example, the equation
-\[
- \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
-\]
-was typeset using the commands
-\begin{verbatim}
-\[
- \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
-\]
-\end{verbatim}
-
-For those of your equations that you wish to be automatically numbered sequentially throughout the text for future reference, use the \texttt{equation} environment, e.g.
-\begin{equation}
- \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
-\end{equation}
-was typeset using the commands
-\begin{verbatim}
-\begin{equation}
- \hat{\theta}_{w_i} = \hat{\theta}(s(t,\mathcal{U}_{w_i}))
-\end{equation}
-\end{verbatim}
-
-Part numbers for sets of equations may be generated using the \texttt{subequations} environment, e.g.
-\begin{subequations} \label{subeqnexample}
-\begin{equation}
-     \varepsilon \rho w_{tt}(s,t) = N[w_{s}(s,t),w_{st}(s,t)]_{s},
-     \label{subeqnparta}
-\end{equation}
-\begin{equation}
-     w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
-     \label{subeqnpartb}
-\end{equation}
-\end{subequations}
-which was typeset using the commands
-\begin{verbatim}
-\begin{subequations} \label{subeqnexample}
-\begin{equation}
-     \varepsilon \rho w_{tt}(s,t) = N[w_{s}(s,t),w_{st}(s,t)]_{s},
-     \label{subeqnparta}
-\end{equation}
-\begin{equation}
-     w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,   \label{subeqnpartb}
-\end{equation}
-\end{subequations}
-\end{verbatim}
-This is made possible by the \texttt{amsmath} package, which is called by the class file.
-If you put a \verb"\label" just after the \verb"\begin{subequations}" command, references can be made to the collection of equations, i.e.\ `(\ref{subeqnexample})' in the example above.
-Or, as the example also shows, you can label and refer to each equation individually -- i.e.\ `(\ref{subeqnparta})' and `(\ref{subeqnpartb})'.
-
-Displayed mathematics should be given end-of-line punctuation appropriate to the running text sentence of which it forms a part, if required.
-
-\subsubsection{Math fonts}
-
-\paragraph{Superscripts and subscripts}
-Superscripts and subscripts will automatically come out in the correct size in a math environment (i.e.\ enclosed within \verb"\(...\)" or \verb"$...$" commands in running text, or within \verb"\[...\]" or the \texttt{equation} environment for displayed equations).
-Sub/superscripts that are physical variables should be italic, whereas those that are labels should be roman (e.g.\ $C_p$, $T_\mathrm{eff}$).
-If the subscripts or superscripts need to be other than italic, they must be coded individually.
-
-\paragraph{Upright Greek characters and the upright partial derivative sign}
-Upright lowercase Greek characters can be obtained by inserting the letter `u' in the control code for the character, e.g.\ \verb"\umu" and \verb"\upi" produce $\umu$ (used, for example, in the symbol for the unit microns -- $\umu\mathrm{m}$) and $\upi$ (the ratio of the circumference of a circle to its diameter).
-Similarly, the control code for the upright partial derivative $\upartial$ is \verb"\upartial".
-Bold lowercase as well as uppercase Greek characters can be obtained by \verb"{\bm \gamma}", for example, which gives ${\bm \gamma}$, and \verb"{\bm \Gamma}", which gives ${\bm \Gamma}$.
-
 \section*{Acknowledgement(s)}
@@
 
-\subsection{References cited in the text}
+test\citep{quEffectsSandBurial2017}
 
-References should be cited in Council of Science Editors (CSE) name-year style, e.g.\ `\citep{Rit74,Fel81,Fau02}', or `\ldots see \citet[p.~15]{Smi91}'.
-When several in-text references occur at the same point, distinguish works by the same author published in different years by placing the years after the author name in chronological sequence, e.g.\ `\citep{Smi70,Smi75}'.
-For two or more works published by the same author in the same year, add an alphabetic designator to the year in both the in-text reference and the end reference, e.g.\ `(\citealp{And60CJPS}, \citeyear{And60CJB})'.
-When the authors of two works published in the same year have identical surnames, include their initials in the in-text reference and separate the two in-text references by a semicolon and a space, e.g.\ `\citep{DawJ86,DawM86}'.
-If a work has two authors, give both names in the in-text reference, e.g.\ `\citep{Wei74}'.
-If a reference has three or more authors, give only the first author's name followed by `et~al.' and the year of publication, e.g.\ `\citep{Och03}'.
-If the first author's names and the years of publication are identical for several references, include enough co-author names to eliminate ambiguity, e.g.\ `(Martinez, Fuentes, et~al.
-1990; Martinez, Fuentes, Ortiz, et~al.
-1990)'.
-For further details on this reference style, see the Instructions for Authors on the Taylor \& Francis website.
-
-Each bibliographic entry has a key, which is assigned by the author and is used to refer to that entry in the text.
-In this document, the key \verb"Ant97" in the citation form \verb"\citep{Ant97}" produces `\citep{Ant97}', and the keys \verb"{Sha78,AG98,BGC04}" in the citation form \verb"\citep{Sha78,AG98,BGC04}" produce `\citep{Sha78,AG98,BGC04}'.
-The appropriate citation style for different situations can be obtained, for example, by \verb"\citet{IOM75}" for `\citet{IOM75}', \verb"\citealt{SRW05}" for `\citealt{SRW05}', or \verb"\citealp{Lee03}" for `\citealp{Lee03}'.
-Citation of the year alone may be produced by \verb"\citeyear{Ste64}", i.e.\ `\citeyear{Ste64}', or \verb"\citeyearpar{Ovi95}", i.e.\ `\citeyearpar{Ovi95}', or of the author(s) alone by \verb"\citeauthor{Wei03}", i.e.\ `\citeauthor{Wei03}'.
-Optional notes may be included at the beginning and/or end of a citation by the use of square brackets, e.g.\ \verb"\citep[see][p.~73-–77]{PI51}" produces `\citep[see][p.~73--77]{PI51}'; \verb"\citep[e.g.][]{Sch02}" produces `\citep[e.g.][]{Sch02}'.
-A `plain' \verb"\cite" command will produce the same results as a \verb"\citet", i.e.\ \verb"\cite{Ant03}" will produce `\cite{Ant03}'.
-
-\subsection{The list of references}
-
-References should be listed at the end of the main text in alphabetical order by author, then chronologically.
-If there is no identifiable author, use e.g. `\citep{Hbk00}'.
-The year of publication is required for all reference types; for newspaper articles and patents, provide the full date of publication including the month and day of the month.
-If a date of publication is impossible to find, use `\citeyear{LedND}' in its place. The following list shows some sample references prepared in the Taylor \& Francis CSE name-year style.
-
-\begin{thebibliography}{}
-
-\bibitem[Ambudkar and Gottesman(1998)]{AG98}
-Ambudkar~SV, Gottesman~MM, editors. 1998. ABC transporters: biomedical,
-  cellular, and molecular aspects. San Diego (CA): Academic Press. (Methods
-  in enzymology; vol. 292).
-
-\bibitem[Andrews(1960a)]{And60CJPS}
-Andrews~JE. 1960a. Cold hardiness of sprouting wheat as affected by duration of
-  hardening and hardening temperature. Can J Plant Sci. 40(1):93--102.
-
-\bibitem[Andrews(1960b)]{And60CJB}
-Andrews~JE. 1960b. Cold hardening and cold hardiness of young winter rye
-  seedlings as affected by stage of development and temperature. Can J Bot.
-  38(3):353--363.
-
-\bibitem[Antani et~al.(2003)]{Ant03}
-Antani~S, Long~LR, Thoma~GR, Lee~DJ. 2003. Anatomical shape representation in
-  spine x-ray images. Paper presented at: VIIP 2003. Proceedings of the
-  3rd IASTED International Conference on Visualization, Imaging and
-  Image Processing; Sep 8--10; Benalmadena, Spain.
-
-\bibitem[Antonioli(1997)]{Ant97}
-Antonioli~GE, editor. 1997. Pacemaker leads 1997. Proceedings of the 3rd
-  International Symposium on Pacemaker Leads; Sep 11--13; Ferrara, Italy.
-  Bologna: Monducci Editore.
-
-\bibitem[Berrino et~al.(2004)]{BGC04}
-Berrino~F, Gatta~G, Crosignani~P. 2004. [Case-control evaluation of screening
-  efficacy]. Epidemiol Prev. 28:354--359. Italian.
-
-\bibitem[Dawson~J(1986)]{DawJ86}
-Dawson~J. 1986. Animal experiments: conference report. BMJ.
-  292(6536):1654--1655.
-
-\bibitem[Dawson~M(1986)]{DawM86}
-Dawson~M. 1986. Some examples of necessary continuation and
-  possible discontinuation of animal experiments. Acta Physiol Scand Suppl.
-  554:194--197.
-
-\bibitem[Fauci(2002)]{Fau02}
-Fauci~AS. 2002. Smallpox vaccination policy -- the need for dialogue. N Engl J
-  Med. 346(17):1319--1320.
-
-\bibitem[Feller(1981)]{Fel81}
-Feller~BA. 1981. Health characteristics of persons with chronic activity
-  limitation, United States, 1979. Hyattsville (MD): National Center for
-  Health Statistics (US). Report No.: VHS-SER-10/137. Available from: NTIS,
-  Springfield, VA; PB88-228622.
-
-\bibitem[Handbook\ldots(2000)]{Hbk00}
-Handbook of geriatric drug therapy. 2000. Springhouse (PA): Springhouse.
-
-\bibitem[IOM(1975)]{IOM75}
-[IOM] Institute of Medicine (US). 1975. Legalized abortion and the public health:
-  report of a study by a committee of the Institute of Medicine. Washington
-  (DC): National Academy of Sciences.
-
-\bibitem[Lederer({[date unknown]})]{LedND}
-Lederer~J. {[date unknown]}. Alimentation et cancer [Diet and cancer].
-  Brussels: Nauwelaerts.
-
-\bibitem[Lee et~al.(2003)]{Lee03}
-Lee~DJ, Bates~D, Dromey~C, Xu~X, Antani~S. 2003. An imaging system correlating
-  lip shapes with tongue contact patterns for speech pathology research. In:
-  Krol~M, Mitra~S, Lee~DJ, editors. CMBS 2003. Proceedings of the 16th IEEE
-  Symposium on Computer-Based Medical Systems; 2003 Jun 26--27; New York. Los
-  Alamitos (CA): IEEE Computer Society. p.~307--313.
-
-\bibitem[Ochi et~al.(2003)]{Och03}
-Ochi~K, Sugiura~N, Komatsuzaki~Y, Nishino~H, Ohashi~T. 2003. Patency of
-  inferior meatal antrostomy. Auris Nasus Larynx. 30 Suppl:S57--S60.
-
-\bibitem[Oviedo(1995)]{Ovi95}
-Oviedo~S. 1995. Adolescent pregnancy: voices heard in the everyday lives of
-  pregnant teenagers [master's thesis]. Denton (TX): University of North Texas.
-
-\bibitem[Piaget and Inhelder(1951)]{PI51}
-Piaget~J, Inhelder~B. 1951. La gen{\`e}se de l'id{\'e}e de hasard chez l'enfant
-  [The origin of the idea of chance in the child]. Paris: Presses
-  Universitaires de France.
-
-\bibitem[Ritzmann(1974)]{Rit74}
-Ritzmann~RE. 1974. The snapping mechanism of \textit{Alpheid} shrimp
-  [dissertation]. Charlottesville (VA): University of Virginia.
-
-\bibitem[Savage et~al.(2005)]{SRW05}
-Savage~E, Ramsay~M, White~J, Beard~S, Lawson~H, Hunjan~R, Brown~D. 2005. Mumps
-  outbreaks across England and Wales in 2004: observational study. BMJ.
-  [cited~2005 May 31]; 330(7500):1119--1120. Available from:
-  http://bmj.bmjjournals.com/cgi/reprint/330/7500/1119
-
-\bibitem[Schott and Priest(2002)]{Sch02}
-Schott~J, Priest~J. 2002. Leading antenatal classes: A practical guide. 2nd ed.
-  Boston (MA): Books for Midwives.
-
-\bibitem[Shakelford(1978)]{Sha78}
-Shakelford~RT. 1978. Surgery of the alimentary tract. Philadelphia (PA): W.B.
-  Saunders; Chapter 2, Esophagoscopy, p.~29--40.
-
-\bibitem[Smith(1970)]{Smi70}
-Smith~CE. 1970. Studies on arbovirus epidemiology associated with established
-  and developing rice culture. Introduction. Trans R Soc Trop Med Hyg.
-  64(4):481--482.
-
-\bibitem[Smith(1975)]{Smi75}
-Smith~CE. 1975. The significance of mosquito longevity and blood-feeding
-  behaviour in the dynamics of arbovirus infections. Med Biol. 53(5):288--294.
-
-\bibitem[Smith(1991)]{Smi91}
-Smith~KL. 1991. New dangers in our field [editorial]. Am J Nucl Eng.
-  13(1):15--16.
-
-\bibitem[Stearns(1864)]{Ste64}
-Stearns~AA. 1864. Armory {S}quare {H}ospital nursing diary. 70 leaves. Located
-  at: History of Medicine Division, National Library of Medicine, Bethesda, MD;
-  MS B 372.
-
-\bibitem[Weinstein and Swartz(1974)]{Wei74}
-Weinstein~L, Swartz~MN. 1974. Pathologic properties of invading organisms. In:
-  Sodeman~WA, editor. Pathologic physiology: Mechanisms of disease. 5th ed.
-  Philadelphia (PA): Saunders; p. 135--140.
-
-\bibitem[Weiss(2003 Apr~11)]{Wei03}
-Weiss~R. 2003 Apr 11. Study shows problems in cloning people: researchers find
-  replicating primates will be harder than other mammals. Washington Post (Home
-  Ed.). Sect.~A:12 (col.~1).
-
-\end{thebibliography}
-\bigskip
-\noindent This was produced by typing:
-\begin{verbatim}
-\begin{thebibliography}{}
-
-\bibitem[Ambudkar and Gottesman(1998)]{AG98}
-Ambudkar~SV, Gottesman~MM, editors. 1998. ABC transporters: biomedical,
- cellular, and molecular aspects. San Diego (CA): Academic Press.
- (Methods in enzymology; vol. 292).
-
-\bibitem[Andrews(1960a)]{And60CJPS}
-Andrews~JE. 1960a. Cold hardiness of sprouting wheat as affected by
- duration of hardening and hardening temperature. Can J Plant Sci.
- 40(1):93--102.
-
-\bibitem[Andrews(1960b)]{And60CJB}
-Andrews~JE. 1960b. Cold hardening and cold hardiness of young winter
- rye seedlings as affected by stage of development and temperature.
- Can J Bot. 38(3):353--363.
-
-\bibitem[Antani et~al.(2003)]{Ant03}
-Antani~S, Long~LR, Thoma~GR, Lee~DJ. 2003. Anatomical shape
- representation in spine x-ray images. Paper presented at: VIIP 2003.
- Proceedings of the 3rd IASTED International Conference on
- Visualization, Imaging and Image Processing; Sep 8--10; Benalmadena,
- Spain.
-
-\bibitem[Antonioli(1997)]{Ant97}
-Antonioli~GE, editor. 1997. Pacemaker leads 1997. Proceedings of the
- 3rd International Symposium on Pacemaker Leads; Sep 11--13; Ferrara,
- Italy. Bologna: Monducci Editore.
-
-\bibitem[Berrino et~al.(2004)]{BGC04}
-Berrino~F, Gatta~G, Crosignani~P. 2004. [Case-control evaluation of
- screening efficacy]. Epidemiol Prev. 28:354--359. Italian.
-
-\bibitem[Dawson~J(1986)]{DawJ86}
-Dawson~J. 1986. Animal experiments: Conference report. BMJ.
- 292(6536):1654--1655.
-
-\bibitem[Dawson~M(1986)]{DawM86}
-Dawson~M. 1986. Some examples of necessary continuation and possible
- discontinuation of animal experiments. Acta Physiol Scand Suppl.
- 554:194--197.
-
-\bibitem[Fauci(2002)]{Fau02}
-Fauci~AS. 2002. Smallpox vaccination policy -- the need for dialogue.
- N Engl J Med. 346(17):1319--1320.
-
-\bibitem[Feller(1981)]{Fel81}
-Feller~BA. 1981. Health characteristics of persons with chronic
- activity limitation, United States, 1979. Hyattsville (MD): National
- Center for Health Statistics (US). Report No.: VHS-SER-10/137.
- Available from: NTIS, Springfield, VA; PB88-228622.
-
-\bibitem[Handbook\ldots(2000)]{Hbk00}
-Handbook of geriatric drug therapy. 2000. Springhouse (PA):
- Springhouse.
-
-\bibitem[IOM(1975)]{IOM75}
-[IOM] Institute of Medicine (US). 1975. Legalized abortion and the
- public health: report of a study by a committee of the Institute of
- Medicine. Washington (DC): National Academy of Sciences.
-
-\bibitem[Lederer({[date unknown]})]{LedND}
-Lederer~J. {[date unknown]}. Alimentation et cancer [Diet and cancer].
- Brussels: Nauwelaerts.
-
-\bibitem[Lee et~al.(2003)]{Lee03}
-Lee~DJ, Bates~D, Dromey~C, Xu~X, Antani~S. 2003. An imaging system
- correlating lip shapes with tongue contact patterns for speech
- pathology research. In: Krol~M, Mitra~S, Lee~DJ, editors. CMBS 2003.
- Proceedings of the 16th IEEE Symposium on Computer-Based Medical
- Systems; 2003 Jun 26--27; New York. Los Alamitos (CA): IEEE Computer
- Society. p.~307--313.
-
-\bibitem[Ochi et~al.(2003)]{Och03}
-Ochi~K, Sugiura~N, Komatsuzaki~Y, Nishino~H, Ohashi~T. 2003. Patency of
-  inferior meatal antrostomy. Auris Nasus Larynx. 30 Suppl:S57--S60.
-
-\bibitem[Oviedo(1995)]{Ovi95}
-Oviedo~S. 1995. Adolescent pregnancy: voices heard in the everyday
- lives of pregnant teenagers [master's thesis]. Denton (TX): University
- of North Texas.
-
-\bibitem[Piaget and Inhelder(1951)]{PI51}
-Piaget~J, Inhelder~B. 1951. La gen{\`e}se de l'id{\'e}e de hasard chez
- l'enfant [The origin of the idea of chance in the child]. Paris:
- Presses Universitaires de France.
-
-\bibitem[Ritzmann(1974)]{Rit74}
-Ritzmann~RE. 1974. The snapping mechanism of \textit{Alpheid} shrimp
- [dissertation]. Charlottesville (VA): University of Virginia.
-
-\bibitem[Savage et~al.(2005)]{SRW05}
-Savage~E, Ramsay~M, White~J, Beard~S, Lawson~H, Hunjan~R, Brown~D. 2005.
- Mumps outbreaks across England and Wales in 2004: observational study.
- BMJ. [cited~2005 May 31]; 330(7500):1119--1120. Available from:
- http://bmj.bmjjournals.com/cgi/reprint/330/7500/1119
-
-\bibitem[Schott and Priest(2002)]{Sch02}
-Schott~J, Priest~J. 2002. Leading antenatal classes: A practical guide.
- 2nd ed. Boston (MA): Books for Midwives.
-
-\bibitem[Shakelford(1978)]{Sha78}
-Shakelford~RT. 1978. Surgery of the alimentary tract. Philadelphia
- (PA): W.B. Saunders; Chapter 2, Esophagoscopy, p.~29--40.
-
-\bibitem[Smith(1970)]{Smi70}
-Smith~CE. 1970. Studies on arbovirus epidemiology associated with
- established and developing rice culture. Introduction. Trans R Soc
- Trop Med Hyg. 64(4):481--482.
-
-\bibitem[Smith(1975)]{Smi75}
-Smith~CE. 1975. The significance of mosquito longevity and
- blood-feeding behaviour in the dynamics of arbovirus infections.
- Med Biol. 53(5):288--294.
-
-\bibitem[Smith(1991)]{Smi91}
-Smith~KL. 1991. New dangers in our field [editorial]. Am J Nucl Eng.
- 13(1):15--16.
-
-\bibitem[Stearns(1864)]{Ste64}
-Stearns~AA. 1864. Armory {S}quare {H}ospital nursing diary. 70 leaves. 
- Located at: History of Medicine Division, National Library of 
- Medicine, Bethesda, MD; MS B 372.
-
-\bibitem[Weinstein and Swartz(1974)]{Wei74}
-Weinstein~L, Swartz~MN. 1974. Pathologic properties of invading 
- organisms. In: Sodeman~WA, editor. Pathologic physiology: Mechanisms 
- of disease. 5th ed. Philadelphia (PA): Saunders; p. 135--140.
-
-\bibitem[Weiss(2003 Apr~11)]{Wei03}
-Weiss~R. 2003 Apr 11. Study shows problems in cloning people:
- researchers find replicating primates will be harder than other
- mammals. Washington Post (Home Ed.). Sect.~A:12 (col.~1).
-
-\end{thebibliography}
-\end{verbatim}
-\bigskip
-\noindent Each entry takes the form:
-\begin{verbatim}
-\bibitem[authors' names(date of publication)]{key}
- Bibliography entry
-\end{verbatim}
-where `\texttt{authors' names}' is the list of names to appear where the \verb"bibitem" is cited in the text, and `\texttt{key}' is the tag that is to be used as an argument for the \verb"\cite{}" commands in the text of the article.
-`\texttt{Bibliography entry}' is the material that is to appear in the list of references, suitably formatted.
-The commands
-\begin{verbatim}
-\usepackage{natbib}
-\bibpunct[, ]{(}{)}{;}{a}{}{,}
-\renewcommand\bibfont{\fontsize{10}{12}\selectfont}
-\end{verbatim}
-need to be included in the preamble of your .tex file in order to generate the citations and bibliography as described above.
-
-Instead of typing the bibliography by hand, you may prefer to create the list of references using a \textsc{Bib}\TeX\ database.
-The \texttt{tfcse.bst} file needs to be in your working folder or an appropriate directory, and the lines
-\begin{verbatim}
-\bibliographystyle{tfcse}
+\bibliographystyle{tfcse.bst}
 \bibliography{interactcsesample}
-\end{verbatim}
-included where the list of references is to appear, where \texttt{tfcse.bst} is the name of the \textsc{Bib}\TeX\ bibliography style file for Taylor \& Francis' CSE name-year reference style and \texttt{interactcsesample.bib} is the bibliographic database included with the \textsf{Interact}-CSE \LaTeX\ bundle (to be replaced with the name of your own .bib file).
-\LaTeX/\textsc{Bib}\TeX\ will extract from your .bib file only those references that are cited in your .tex file and list them in the References section.
-
-Please include a copy of your .bib file and/or the final generated .bbl file among your source files if your .tex file does not contain a reference list in a \texttt{thebibliography} environment.
-
-\section{Appendices}
-
-Any appendices should be placed after the list of references, beginning with the command \verb"\appendix" followed by the command \verb"\section" for each appendix title, e.g.
-\begin{verbatim}
-\appendix
-\section{This is the title of the first appendix}
-\section{This is the title of the second appendix}
-\end{verbatim}
-produces:\medskip
-
-\noindent\textbf{Appendix A. This is the title of the first appendix}\medskip
-
-\noindent\textbf{Appendix B. This is the title of the second appendix}\medskip
-
-\noindent Subsections, equations, figures, tables, etc.\ within appendices will then be automatically numbered as appropriate.
-Some theorem-like environments may need to have their counters reset manually (e.g.\ if they are not numbered within sections in the main text).
-You can achieve this by using \verb"\numberwithin{remark}{section}" (for example) just after the \verb"\appendix" command.
-
-Note that if the \verb"endfloat" package is used on a document containing any appendices, the \verb"\processdelayedfloats" command must be included immediately before the \verb"\appendix" command in order to ensure that the floats belonging to the main body of the text are numbered as such.
-
-%\processdelayedfloats %%% See above for an explanation of why this command might be needed here.
-
-\appendix
-
-\section{Troubleshooting}
-
-Authors may occasionally encounter problems with the preparation of a manuscript using \LaTeX. The appropriate action to take will depend on the nature of the problem:
-\begin{enumerate}
-\item[(i)] If the problem is with \LaTeX\ itself, rather than with the actual macros, please consult an appropriate \LaTeXe\ manual for initial advice.
-If the solution cannot be found, or if you suspect that the problem does lie with the macros, then please contact Taylor \& Francis for assistance (\texttt{latex.helpdesk@tandf.co.uk}), clearly stating the title of the journal to which you are submitting.
-\item[(ii)] Problems with page make-up (e.g.\ occasional overlong lines of text; figures or tables appearing out of order): please do not try to fix these using `hard' page make-up commands -- the typesetter will deal with such problems.
-(You may, if you wish, draw attention to particular problems when submitting the final version of your manuscript.)
-\item[(iii)] If a required font is not available on your system, allow \TeX\ to substitute the font and specify which font is required in a covering letter accompanying your files.
-\end{enumerate}
-
-\section{Obtaining the template and class file}
-
-\subsection{Via the Taylor \& Francis website}
-
-This article template and the \texttt{interact} class file may be obtained via the `Instructions for Authors' pages of selected Taylor \& Francis journals.
-
-Please note that the class file calls up the open-source \LaTeX\ packages booktabs.sty, epsfig.sty and rotating.sty, which will, for convenience, unpack with the downloaded template and class file.
-The template calls for natbib.sty and subfig.sty, which are also supplied for convenience.
-
-\subsection{Via e-mail}
-
-This article template, the \texttt{interact} class file and the associated open-source \LaTeX\ packages are also available via e-mail.
-Requests should be addressed to \texttt{latex.helpdesk@tandf.co.uk}, clearly stating for which journal you require the template and class file.
 

### 2020-12-06 tex/interactcsesample.tex
add jpg figs

@@
 \subsection{Study area}
-% 如果手稿要给期刊A4打印了，用 document-class 提供的 largeformat 参数（由 interact.cls）提供
-% To prepare a manuscript for a journal that is printed in A4 (two column) format, use the \verb"largeformat" document-class option provided by \texttt{interact.cls}; otherwise the class file produces pages sized for B5 (single column) format by default.
-The \texttt{geometry} package should not be used to make any further adjustments to the page dimensions.
+
+Pingtan island is located on the eastern coast of Fujian province, South China, with a sub-humid and oceanic monsoon climate.
+The study area is situated in the southeast of Pingtan island $(25^{\circ}26'36''-25^{\circ}26'48''N, 119^{\circ}46'09''-119^{\circ}46'21''E)$, and is usually regarded as hosting the most well-preserved coastal sand dunes in China (Figure 3) (Yang et al.
+2017).
+Annual average temperature is 19.5℃, and precipitation is 1151 mm.
+The Monsoon is the dominant wind in this area, SE in the summer and NE in the winter, with an annual average wind speed of $6.9 m/s$.
+A total of 106 typhoons made landfall on Pingtan island from 1981 to 2019, average 2.65 times per year, and mainly they occur in July to September.
+The maximum wind speed can be up to $32.7 m/s$, ultimately leading to the severe sand burial on the psammophytes in this period.
+Soil is mainly composed of medium to fine sand, with well-sorted grains.
+Sediments are transported by the wind and intercepted by the ramets and stolons of S.
+littoreus, and a discrete dune mound or hummock was usually formed by aeolian sand deposition within an isolated plant or group of plants (Hesp \& Smyth 2019), ultimately developing into a 300 m wide nebkha dominated foredune zone (Figure~\ref{sample-pic}).
+S.
+littoreus is the dominant species in the study area and the auxiliary plants including Oenothera drummondii, Cynodondactylon, Pluchea pteropoda, and Sesuvium portulacastrum.
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.8]{../figs/study_area.jpg}
+  \caption{Schematic diagram of the field experiment} 
+  \label{map}
+\end{figure}
 
 \subsection{Methods}
+Field experiments were carried out in July, 2016, in Tannan bay, Pingtan Island (Figure~\ref{fig:map}).
+One study belt without the interruption of animals, pollutants, and apparent human activities was selected in the center of the coastal sand dunes.
+Considering most of the S.
+littoreus were distributed on the windward slopes, 35 healthy plants with uniform size and comparable age were selected on the windward slopes were chosen for study.
+All the observed plants can be well distinguished from surrounding plants, and the height of vertical ramets and the length of stolons were all similar with each other before the burial treatments.
+Stolons of plants on the windward slopes were selected, and labeled with a red cord at points 1/3 and 2/3 of the length from the stem base to the apex of the stolons.
+Weeds around the selected plants were manually cleared, and wooden frames 20 cm in height (similar to the height of stolons) were set around the selected plants.
+Later, all the observed plants were fixed with a label, and its serial number was recorded on the label and wooden baffles respectively in order to facilitate periodic measurements later.
+The few adventitious roots present on the stolons of the observed plants were completely eliminated, the height of vertical ramets and length of stolons were measured separately before the experiments began.
+Later, all the plants were buried with sand from the nearby dunes according to a variety of different treatments (Figure 4).
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.8]{../figs/treatment.jpg}
+  \caption{Schematic diagram of the sand burial treatments of the samples} 
+  \label{treatment}
+\end{figure}
 

### 2020-12-13 tex/interactcsesample.tex
tex outline

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.8]{../figs/study_area.jpg}
+  \caption{Schematic diagram of the field experiment} 
+  \label{fig:map}
+\end{figure}
+
 Pingtan island is located on the eastern coast of Fujian province, South China, with a sub-humid and oceanic monsoon climate.
-The study area is situated in the southeast of Pingtan island $(25^{\circ}26'36''-25^{\circ}26'48''N, 119^{\circ}46'09''-119^{\circ}46'21''E)$, and is usually regarded as hosting the most well-preserved coastal sand dunes in China (Figure 3) (Yang et al.
+The study area is situated in the southeast of Pingtan island $(25^{\circ}26'36''-25^{\circ}26'48''N, 119^{\circ}46'09''-119^{\circ}46'21''E)$, and is usually regarded as hosting the most well-preserved coastal sand dunes in China (Figure~\ref{fig:map}) (Yang et al.
 2017).
@@
 littoreus is the dominant species in the study area and the auxiliary plants including Oenothera drummondii, Cynodondactylon, Pluchea pteropoda, and Sesuvium portulacastrum.
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.8]{../figs/study_area.jpg}
-  \caption{Schematic diagram of the field experiment} 
-  \label{map}
-\end{figure}
 
@@
   \centering
-  \includegraphics[scale=0.8]{../figs/treatment.jpg}
+  \includegraphics[scale=0.5]{../figs/diagram.jpg}
   \caption{Schematic diagram of the sand burial treatments of the samples} 
-  \label{treatment}
+  \label{fig:diagram}
 \end{figure}
+
+\begin{table}
+  \tbl{Sand burial treatments of the plants.}
+  {\begin{tabular}{lrrr} 
+  \toprule
+   Treatment & Burial depth & Burial level \\ 
+  \midrule
+   CG & No sand burial & No sand burial \\
+   HL & Half & Light \\
+   HM & Half & Moderate \\
+   HI & Half & Intense \\
+   CL & Complete & Light \\
+   CM & Complete & Moderate \\
+   CI & Complete & Intense \\
+  \bottomrule
+  \end{tabular}}
+  \label{tab:treatment}
+\end{table}
+
+While control groups (CG) had not been buried by sand artificially, and other groups were buried in different ways.
+Since the height of vertical ramets of S.
+littoreus is relatively high, it is naturally impossible for them to be completely buried in the sand.
+The treated S.littoreus, thus, only the stolons of which were buried at different depths and levels (see Figure~\ref{fig:diagram} and Table~\ref{tab:treatment}).
+Moreover, some adventitious roots on the stolons of selected plants were observed only a few days after sand burial, so the growth parameters of plants were dynamically investigated in 5, 9, 13, 17, 20 days after the sand burial to investigate the response of S.littoreus to severe sand burial over a short time scale.
+
+During the measurements, the sand burying the plants was carefully removed to one side in a wooden baffle, and the height of the vertical ramets, the length of the stolons and adventitious roots were all measured with a tape.
+In the end, all the plants were buried again with the previous sand.
+When the experiments were finished, both above and below ground biomass of plants were collected and separated according to the label previously fixed on the stolons.
+Then all the samples were taken to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of 65℃ for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: 0.0001g).
+
+All the data were calculated with average according to all the replications with standard error as measurement of variability.
+The results were analysed with Python3 and package Pingouin.
+For each observed variable, we used repeated measure ANOVA analysis to test if the experimental treatments were verified due to time, and checked the significance $(P<0.05)$.
 
@@
 
-\subsection{Influence of sand burial on the height of vertical ramets}
-
-\subsection{Influence of sand burial on the length of horizontal stolons}
+\subsection{Influence of sand burial on growth processes of \textit{S. littoreus}}
 
@@
 
-\section{Some guidelines for using the standard features of \LaTeX}
+\section{Discussion}
 
-\subsection{Tables}
+\subsection{Mechanism of \textit{S. littoreus'} responses to severe sand burial}
 
-The \texttt{interact} class file will deal with positioning your tables in the same way as standard \LaTeX.
-It should not normally be necessary to use the optional \texttt{[htb]} location specifiers of the \texttt{table} environment in your manuscript; you may, however, find the \verb"[p]" placement option or the \verb"endfloat" package useful if a journal insists on the need to separate tables from the text.
-
-The \texttt{tabular} environment can be used as shown to create tables with single horizontal rules at the head, foot and elsewhere as appropriate.
-The captions appear above the tables in the \textsf{Interact} style, therefore the \verb"\tbl" command should be used before the body of the table.
-For example, Table~\ref{sample-table} is produced using the following commands:
-\begin{table}
-\tbl{Example of a table showing that its caption is as wide as
- the table itself and justified.}
-{\begin{tabular}{lcccccc} \toprule
- & \multicolumn{2}{l}{Type} \\ \cmidrule{2-7}
- Class & One & Two & Three & Four & Five & Six \\ \midrule
- Alpha\textsuperscript{a} & A1 & A2 & A3 & A4 & A5 & A6 \\
- Beta & B2 & B2 & B3 & B4 & B5 & B6 \\
- Gamma & C2 & C2 & C3 & C4 & C5 & C6 \\ \bottomrule
-\end{tabular}}
-\tabnote{\textsuperscript{a}This footnote shows how to include
- footnotes to a table if required.}
-\label{sample-table}
-\end{table}
-\begin{verbatim}
-\begin{table}
-\tbl{Example of a table showing that its caption is as wide as
- the table itself and justified.}
-{\begin{tabular}{lcccccc} \toprule
- & \multicolumn{2}{l}{Type} \\ \cmidrule{2-7}
- Class & One & Two & Three & Four & Five & Six \\ \midrule
- Alpha\textsuperscript{a} & A1 & A2 & A3 & A4 & A5 & A6 \\
- Beta & B2 & B2 & B3 & B4 & B5 & B6 \\
- Gamma & C2 & C2 & C3 & C4 & C5 & C6 \\ \bottomrule
-\end{tabular}}
-\tabnote{\textsuperscript{a}This footnote shows how to include
- footnotes to a table if required.}
-\label{sample-table}
-\end{table}
-\end{verbatim}
-
-To ensure that tables are correctly numbered automatically, the \verb"\label" command should be included just before \verb"\end{table}".
-
-The \verb"\toprule", \verb"\midrule", \verb"\bottomrule" and \verb"\cmidrule" commands are those used by \verb"booktabs.sty", which is called by the \texttt{interact} class file and included in the \textsf{Interact} \LaTeX\ bundle for convenience.
-Tables produced using the standard commands of the \texttt{tabular} environment are also compatible with the \texttt{interact} class file.
+\subsection{Significance of \textit{S. littoreus'} adaptation to sand burial}
 

### 2020-12-13 tex/interactcsesample.tex
re-write results section

@@
 
+\begin{figure}[!h]
+  \centering
+  \includegraphics[scale=0.8]{../figs/grid_differences.jpg}
+  \caption{
+    % 不同沙埋处理下，植株的株高生长（A）与匍匐茎生长（B）同空白对照组之间的差异变化。
+    Difference in ramets height growth (\textbf{A}) and horizontal stolons (\textbf{B}) between control group (CG) and different sand burial treatments.
+The blue dots refer negative (less than CG) while the red dots refer positive (larger than CG) differences.
+The fulfilled dots are significant different in statistic ($P<0.05$) and size of the dots denotes the size of difference.
+  } 
+  \label{fig:lattice}
+\end{figure}
+
+\begin{figure}[!h]
+  \centering
+  \includegraphics[scale=0.8]{../figs/growth_process.jpg}
+  \caption{
+    Growth process of horizontal stolons with half intense (HI) group and complete intense (CI) group plants.
+    \textbf{A} growth of horizontal stolons' length of HI group, compared with the control group (CG).
+    \textbf{B} growth of horizontal stolons' length of CI group, compared with the control group (CG).
+    \textbf{C} growth of different sections of horizontal stolons' length of HI group.
+    \textbf{D} growth of different sections of horizontal stolons' length of CI group.
+  }
+  \label{fig:growth}
+\end{figure}
+
+% 不同的沙埋处理下的老鼠楽株高的生长过程与空白对照之间没有显著差异（图1A），但沙埋对老鼠楽匍匐茎的伸长生长产生了显著影响（图1B）。
+With different treatments, there was no significant difference between the growth of ramets height, but with significant effects on the growth of horizontal stolons when intense half sand burial (HI) and complete intense sand burial (CI) (Figure~\ref{fig:lattice}).
+While the significant effect of CI occurred after 9 days after sand burial treatment, the significant effect of a HI group occurred at 13 days and 20 days after sand burial. 
+% CI组不仅时间效应出现的更早，而且对水平stolons生长的促进作用也大于HI组，在20天砂埋试验结束时，其stolons长度显著增加24.56\%和40.79\%。
+Not only did the time effect appear earlier with the CI group, but also had a greater promoting effect on the growth of horizontal stolons than the HI group, with significant increases in stolons' length of 40.79\% and 24.56\% respectively at the end of 20-day sand burial experiment (Figure~\ref{fig:growth} A and B).
+% 其伸长生长过程都在不断增加顶端1/3长度所占的比例，而基部长度占比和中段的长度占比均匀下降（图2C-D）。
+During the elongation growth process, the proportion of the length of the top 1/3 (apex) increased continuously, while the proportion of the length of the base and the length of the middle sections decreased uniformly (Figure~\ref{fig:growth} C and D).
+
 \subsection{Influence of sand burial on the biomass allocation}
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.6]{../figs/roots.jpg}
+  \caption{
+    \textbf{A.} Total length of adventitious roots under different sand burial treatments.
+    \textbf{B.} Number of adventitious roots under different sand burial treatments.
+    \textbf{C.} Mean dry weights in different sections of horizontal stolons.
+  }
+  \label{fig:roots}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.8]{../figs/ratio.jpg}
+  \caption{
+    Ratio between stem weights and leaf weights after the experiments under different treatments.
+The white lines denote mean ratio of the control group (CG) while the grey spans denote the standard error of.
+Weights ratio from different sections were compared one by one (\textbf{A:} base sections, \textbf{B:} middle sections, \textbf{C:} apex sections, \textbf{D:} all sections).
+  }
+  \label{fig:ratio}
+\end{figure}
+
+% 大多数的人工沙埋不同程度上促进了不定根的生成，无论是不定根数量还是总长度（Fig3）。
+Most of sand-burial treatments promote the generation of adventitious roots to varying degrees, both in terms of the number of roots and the total length of the roots (Figure~\ref{fig:roots} A and B).
+% 而且不定根主要分布在基部，顶端无不定根生成。
+What's more, the adventitious roots are mainly distributed at the base and the adventitious roots are not generated at the apex (Figure~\ref{fig:roots} C).
+% 经过20天的沙埋实验，老鼠楽植株茎和叶片的干重比例在不同程度上发生了改变。
+After 20 days of sand-burying experiments, the ratio of dry weight between stems and leaves of \textit{S.
+littoreus} plant changed to varying degrees (most of which decreased in ratio of stem weight and leaf weight) under different treatments (Figure~\ref{fig:ratio}).
+% 相对于空白对照组来说，沙埋使得植株将干重更多分配在茎上而非叶片上，在植株的顶端尤其明显。
+Compared with the control group (CG), sand burial caused the plant to distribute dry weight more on the stem than on the leaves, especially at the top of the plant (Figure~\ref{fig:ratio} C).
 

### 2020-12-13 tex/interactcsesample.tex
finish manuscript initially

@@
 
-\title{The responses of \textit{Spinifex littoreus} to sand burial on the coastal area of Pingtan Island, Fujian Province, South China}
+\title{The responses of \textit{\textit{Spinifex littoreus}} to sand burial on the coastal area of Pingtan Island, Fujian Province, South China}
 
@@
 % 研究了福建平潭岛海岸滨鹬对不同埋沙深度和埋沙深度的响应。
-The responses of Spinifex littoreus to different sand burial depths and levels were examined on the coast of Pingtan island, Fujian Province, South China. 
+The responses of \textit{Spinifex littoreus} to different sand burial depths and levels were examined on the coast of Pingtan island, Fujian Province, South China. 
 % 结果表明，与对照组相比，砂埋对其匍匐茎的垂直生长无显著影响。
-The results indicated that, compared to the control group, sand burial on the S. littoreus stolons had no significant impact on its vertical growth of conjoint ramets. 
-% 随着砂埋的继续，匍匐茎顶端生长更快，完全砂埋比半砂埋影响更明显。
-The stolon apex grew even faster as the sand burial continued, with more obvious influence under complete sand burial than half sand burial. 
-% 不同埋沙处理均能刺激和产生荔枝匍匐茎上的不定根，其长度随埋沙水平的变化而变化。
-Adventitious roots on S. littoreus stolons were stimulated and produced in all sand burial treatments, the length of which varied according to the sand burial levels. 
+The results indicated that, compared to the control group, sand burial on the \textit{S. littoreus} stolons had no significant impact on its vertical growth of conjoint ramets. 
+% 然而，随着砂埋的继续，匍匐茎顶端生长更快，完全砂埋比半砂埋影响更明显。
+However, growth of horizontal stolons on \textit{S.
+littoreus} were stimulated and significantly increased in half intense (HI) and complete intense (CI) sand burial by 24.56\% and 40.79\%, respectively.
 % 在不定根和叶片上，三个匍匐茎上的干生物量分配均发生了变化，而在茎上则没有变化。
-Dry biomass allocation were altered by sand burial in both adventitious roots and leaves, but not in stems. 
-More adventitious roots on base of stolon and leaves on apex of stolon were observed. 
+Throughout experiment, nearly all of adventitious roots were observed on base section of stolons, comparing with even no roots with the control groups. 
+After the 20-day artificial sand burial, dry biomass allocation were altered and ratio of dry weights between stem and leaf decreased, especially for apex sections. 
 % 通过匍匐茎的快速生长，匍匐茎基部产生大量不定根，匍匐茎顶端的叶片萌发率较高，可以适应完全的砂埋。
-S. littoreus can adapt to complete sand burial by rapid growth of stolons, abundant production of adventitious roots on the stolon base, and more germination of leaves on the stolon apex.
+Overall, \textit{S.
+littoreus} can adapt to complete and intense sand burial by rapid growth of stolons, abundant production of adventitious roots on the stolon base, and more germination of leaves on the stolon apex.
 \end{abstract}
@@
 \begin{keywords}
-Psammophytes; sand burial; \textit{Spinifex littoreus}; responses, plant osmotic stress
+Psammophytes; sand burial; \textit{\textit{Spinifex littoreus}}; responses, plant osmotic stresses
 \end{keywords}
@@
 % 主要介绍沙生植物对海岸生态系统对重要意义
-Sand dunes occupy a finite area in coastal regions, but they are characterized by providing multiple ecological services, and play an important role in the sustainable development in those regions with rising sea levels, surface subsidence and coastal hazards (Martínez et al.
-2004, De Battisti \& Griffin 2020).
-Recently, due to the influence of both climate change and anthropogenic activities, many coastal sand dunes have been modified or destroyed, and this can, or has potentially led to the retreat of coastlines, disappearance of habitats, loss of biodiversity, and severe degradation of ecosystem functions in coastal sand dunes (Feagin et al.
-2005, Schlacher et al.
-2011, Qu et al.
-2017).
+Sand dunes occupy a finite area in coastal regions, but they are characterized by providing multiple ecological services, and play an important role in the sustainable development in those regions with rising sea levels, surface subsidence and coastal hazards
+\citep{martinezFragilityConservationWorld2004,debattistiBelowgroundBiomassPlants2020}. 
+Recently, due to the influence of both climate change and anthropogenic activities, many coastal sand dunes have been modified or destroyed, and this can, or has potentially led to the retreat of coastlines, disappearance of habitats, loss of biodiversity, and severe degradation of ecosystem functions in coastal sand dunes
+\citep{feaginCoastalErosionGlobal2005,schlacherVegetationGhostCrabs2011,quEffectsSandBurial2017}. 
 With the rapid development of economy in China, most of the coastal sand dunes were also eradicated due to real estate and infrastructure development and tourism activities.
-Almost no well-preserved coastal sand dunes are left, which apart from the loss of ecological functions and habitats, may ultimately result in coastal erosion and the loss of life, property and economy (Yang et al.
-2017).
-Hard engineering structures have been proved to be costly and detrimental for the protection of coastal regions, so it is very important to select natural and environmentally friendly methods for both the protection and restoration of the remaining coastal dune systems (Hanley et al.
-2014).
+Almost no well-preserved coastal sand dunes are left, which apart from the loss of ecological functions and habitats, may ultimately result in coastal erosion and the loss of life, property and economy
+\citep{xian-jiDiurnalVariationCharacteristics2017}. 
+Hard engineering structures have been proved to be costly and detrimental for the protection of coastal regions, so it is very important to select natural and environmental-friendly methods for both the protection and restoration of the remaining coastal dune systems
+\citep{hanleyShiftingSandsCoastal2014}.
 
@@
 % 主要介绍沙埋与沙生植物对关系
-Psammophytes can build and stabilize coastal dunes, which will favor the restoration of their ecological functions due to their specific adaptive strategies (Yuan et al.
-1993, Nolet et al.
-2018, De Battisti \& Griffin 2020).
-However, only a few species can survive in these ecosystems due to the harsh environmental stress, such as drought, salt spray, strong winds, and especially the frequent and intensive sand burial (Maun \& Lapierre 1986, Hesp 1991, Maun 1994, Maun 1996, Zhao et al.
-2014, Du \& Hesp 2020).
-Sand burial is commonly considered as the selective force for coastal plant regeneration and survival (Moreno-Casasola 1986, Maun 1996, Hwang et al.
-2016, Wang et al.
-2019), which can decrease and even eliminate the psammophytes if the sand burial levels are over their tolerance capacity, ultimately giving rise to the alteration of species composition in coastal dune systems (Maun \& Perumal 1999, Miller 2015).
+Psammophytes can build and stabilize coastal dunes, which will favor the restoration of their ecological functions due to specific adaptive strategies 
+\citep{yuanEffectsSandAccretion1993,brownMechanismsSurvivingBurial2018,debattistiBelowgroundBiomassPlants2020}. 
+However, only a few species can survive in these ecosystems due to the harsh environmental stresses, such as drought, salt spray, strong winds, and especially the frequent and intensive sand burial 
+\citep{maunEffectsBurialSand1986,hespEcologicalProcessesPlant1991,maunAdaptationsEnhancingSurvival1994,y.-y.zhaoAdvanceDistributionAdaptability2014,duSaltSprayDistribution2020}. 
+Sand burial is commonly considered as the selective force for coastal plant regeneration and survival \citep{moreno-casasolaSandMovementFactor1986, maunAdaptationsEnhancingSurvival1994}, which can decrease and even eliminate the psammophytes if the sand burial levels are over their tolerance capacity, ultimately giving rise to the alteration of species composition in coastal dune systems \citep{maunZonationVegetationLacustrine1999,millerEffectsDisturbanceVegetation2015}.
 
@@
 % 这一段主要讲海岸沙生植物耐沙埋能力的用处
-The tolerance capacity to different sand burial levels is varied among species, which finally affect the initial and subsequent coastal dune development and morphology (Hesp 1989).
-Generally, the growth of most psammophytes can be expected to be stimulated with low to moderate sand burial (Zhou et al.
-2015a, Harris et al.
-2017, Brown \& Zinnert 2018, Wang et al.
-2019), while intensive sand burial will decrease its survival and per plant biomass (Maun 1996, Franks \& Peterson 2003).
+The tolerance capacity to different sand burial levels is varied among species, which finally affect the initial and subsequent coastal dune development and morphology 
+\citep{hespReviewBiologicalGeomorphological1989}. 
+Generally, the growth of most psammophytes can be expected to be stimulated with low to moderate sand burial \citep{ruilinAnalysisGrowthStrategy2015,harrisDifferentialResponseBarrier2017,brownMechanismsSurvivingBurial2018,wangEffectsSandBurial2019}, while intensive sand burial will decrease its survival and per plant biomass \citep{maunEffectsBurialSand1996,franksBurialDisturbanceLeads2003}.
 Wang et al.
-(2012) demonstrated that both stem height in the vertical direction and leaf weight of Messerschmidia sibirica were increased with light sand burial, while all decreased with moderate treatments contrasted with the control.
+\citet{wangAdvancesStudiesMorphological2005} demonstrated that both stem height in the vertical direction and leaf weight of \textit{Messerschmidia sibirica} were increased with light sand burial, while all decreased with moderate treatments contrasted with the control.
 In addition, Zhou et al.
-(2015b) showed that the growth of Artemisia desterorum was enhanced with moderate sand burial, but inhibited with intense sand burial.
-Elongation of stolons, upward growth of ramets, and development of new adventitious roots are the main adaptive strategies for plants to sand burial, potentially leading to an alteration in the biomass allocation of psammophytes in coastal sand dunes (Dech \& Maun 2006, Frosini et al.
-2012, Mendoza-González et al.
-2014, Luo et al.
-2018).
+\citet{ruilinPhysiologicalAdaptationMechanisms2015} showed that the growth of Artemisia desterorum was enhanced with moderate sand burial, but inhibited with intense sand burial.
+Elongation of stolons, upward growth of ramets, and development of new adventitious roots are the main adaptive strategies for plants to sand burial, potentially leading to an alteration in the biomass allocation of psammophytes in coastal sand dunes \citep{dechAdventitiousRootProduction2006,frosiniGlobalChangeResponse2012,mendoza-gonzalezBiologicalFloraCoastal2014,brownMechanismsSurvivingBurial2018}.
 
@@
 % 这一段主要介绍老鼠乐与研究去意义
-Spinifex littoreus, a herbaceous plant, is the dominant species in coastal foredunes in South China.
-It often grows vigorously above the backshore, and in the more dynamic foredune, while it declines in the more stabilized backdunes in similarity to its Australian and NZ cousins S.
-hirsutus and S.
-sericeus (Hesp 1989, 2002).
-Its peak growth occurs in summer, with two growth forms, including elongation of horizontal stolons and upward growth of vertical ramets, which sprout out from the same vegetative reproduction, and usually can be recognized as the same ramets (Jackson et al.
-1986).
-The leaf apex of S.
-littoreus is very sharp and hard, which makes it difficult to be intruded, and is usually recognized as one of the excellent species for sand dune fixation in this region (Yang et al.
-2017).
-Frequent typhoons often occur in the growing season of this species in South China, which causes severe sand burial on S.
-littoreus, particularly its stolons on nebkhas forming the foredune zone (Yang et al.
-2017) (Figure 1).
+\textit{Spinifex littoreus}, a herbaceous plant, is the dominant species in coastal foredunes in South China.
+It often grows vigorously above the backshore, and in the more dynamic foredune, while it declines in the more stabilized backdunes in similarity to its Australian and NZ cousins \textit{S.
+hirsutus} and \textit{S.
+sericeus} \citep{hespReviewBiologicalGeomorphological1989}.
+Its peak growth occurs in summer, with two growth forms, including elongation of horizontal stolons and upward growth of vertical ramets, which sprout out from the same vegetative reproduction, and usually can be recognized as the same ramets \citep{jacksonPopulationBiologyEvolution1985}.
+The leaf apex of \textit{S.
+littoreus} is very sharp and hard, which makes it difficult to be intruded, and is usually recognized as one of the excellent species for sand dune fixation in this region \citep{xian-jiDiurnalVariationCharacteristics2017}.
+Frequent typhoons often occur in the growing season of this species in South China, which causes severe sand burial on \textit{S.
+littoreus}, particularly its stolons on nebkhas forming the foredune zone \citep{xian-jiDiurnalVariationCharacteristics2017}(Figure~\ref{sample-pic} A).
 However, the tolerance capacity of this species to sand burial is still unclear at present, and how this species revitalized in the frequent sand burial is less studied.
-Furthermore, local government has planted an invasive species Casuarinas equisetifolia for the stabilization of nebkhas originally formed by S.littoreus, which causes severe damage to this species, and will inevitably increase the fragility of coastal dune ecosystems in this region (Figure 2).
-Therefore, understanding the adaptive strategies of S.
-littoreus to sand burial levels, and its role in the stabilization of coastal dunes are very crucial for the effective coastal management and conservation in South China.
+Furthermore, local government has planted an invasive species Casuarinas equisetifolia for the stabilization of nebkhas originally formed by \textit{S.
+littoreus}, which causes severe damage to this species, and will inevitably increase the fragility of coastal dune ecosystems in this region (Figure~\ref{sample-pic} B).
+Therefore, understanding the adaptive strategies of \textit{S.
+littoreus} to sand burial levels, and its role in the stabilization of coastal dunes are very crucial for the effective coastal management and conservation in South China.
 
@@
   \resizebox*{6cm}{!}{\includegraphics{../figs/damaged_trees.jpg}}}
-  \caption{(a) Intensive sand burial on the Spinifex littoreus nebkhas on Pingtan island after typhoon Soudelor (1513) landed in Putian City, Fujian Province, China in August, 2015.
-(b)The nebkhas formed by Spinifex littoreus was stabilized by the planting of an invasive species Casuarinas equisetifolia seedlings on Pingtan Island, Fujian Province, China.}
+  \caption{(a) Intensive sand burial on the \textit{Spinifex littoreus} nebkhas on Pingtan island after typhoon Soudelor (1513) landed in Putian City, Fujian Province, China in August, 2015.
+(b)The nebkhas formed by \textit{Spinifex littoreus} was stabilized by the planting of an invasive species Casuarinas equisetifolia seedlings on Pingtan Island, Fujian Province, China.}
   \label{sample-pic}
@@
 % 我们认为不同的沙埋情形将改变植株的生长方式，是该植物能够适应台风带来的强烈沙埋的关键性因素。
-In this study, we assume that the different sand burial changes the growth process of S.
-littoreus, which is the key factor for the plants to adapt to the intense sand burial.
-Then, the vertical height of ramets, horizontal length of stolons, and biomass allocation of adventitious roots, stems and leaves on stolons of S.
-littoreus under different sand burial levels were simulated and measured in a field experiment, in a growing season on Pingtan Island, Fujian Province, South China.
+In this study, we assume that the different sand burial changes the growth process of \textit{S.
+littoreus}, which is the key factor for the plants to adapt to the intense sand burial.
+Then, the vertical height of ramets, horizontal length of stolons, and biomass allocation of adventitious roots, stems and leaves on stolons of \textit{S.
+littoreus} under different sand burial levels were simulated and measured in a field experiment, in a growing season on Pingtan Island, Fujian Province, South China.
 
@@
 Pingtan island is located on the eastern coast of Fujian province, South China, with a sub-humid and oceanic monsoon climate.
-The study area is situated in the southeast of Pingtan island $(25^{\circ}26'36''-25^{\circ}26'48''N, 119^{\circ}46'09''-119^{\circ}46'21''E)$, and is usually regarded as hosting the most well-preserved coastal sand dunes in China (Figure~\ref{fig:map}) (Yang et al.
-2017).
+The study area is situated in the southeast of Pingtan island $(25^{\circ}26'36''-25^{\circ}26'48''N, 119^{\circ}46'09''-119^{\circ}46'21''E)$, and is usually regarded as hosting the most well-preserved coastal sand dunes in China (Figure~\ref{fig:map})
+\citep{xian-jiDiurnalVariationCharacteristics2017}. 
 Annual average temperature is 19.5℃, and precipitation is 1151 mm.
@@
 Soil is mainly composed of medium to fine sand, with well-sorted grains.
-Sediments are transported by the wind and intercepted by the ramets and stolons of S.
-littoreus, and a discrete dune mound or hummock was usually formed by aeolian sand deposition within an isolated plant or group of plants (Hesp \& Smyth 2019), ultimately developing into a 300 m wide nebkha dominated foredune zone (Figure~\ref{sample-pic}).
-S.
-littoreus is the dominant species in the study area and the auxiliary plants including Oenothera drummondii, Cynodondactylon, Pluchea pteropoda, and Sesuvium portulacastrum.
+Sediments are transported by the wind and intercepted by the ramets and stolons of \textit{S.
+littoreus}, and a discrete dune mound or hummock was usually formed by aeolian sand deposition within an isolated plant or group of plants \citep{hespCFDFlowDynamics2019}, ultimately developing into a 300 m wide nebkha dominated foredune zone (Figure~\ref{sample-pic}).
+\textit{S.
+littoreus} is the dominant species in the study area and the auxiliary plants including \textit{Oenothera drummondii}, \textit{Cynodondactylon}, \textit{Pluchea pteropoda}, and \textit{Sesuvium portulacastrum}.
 
@@
 One study belt without the interruption of animals, pollutants, and apparent human activities was selected in the center of the coastal sand dunes.
-Considering most of the S.
-littoreus were distributed on the windward slopes, 35 healthy plants with uniform size and comparable age were selected on the windward slopes were chosen for study.
+Considering most of the \textit{S.
+littoreus} were distributed on the windward slopes, 35 healthy plants with uniform size and comparable age were selected on the windward slopes were chosen for study.
 All the observed plants can be well distinguished from surrounding plants, and the height of vertical ramets and the length of stolons were all similar with each other before the burial treatments.
@@
 The few adventitious roots present on the stolons of the observed plants were completely eliminated, the height of vertical ramets and length of stolons were measured separately before the experiments began.
-Later, all the plants were buried with sand from the nearby dunes according to a variety of different treatments (Figure 4).
+Later, all the plants were buried with sand from the nearby dunes according to a variety of different treatments (Figure~\ref{fig:diagram}).
 
@@
 While control groups (CG) had not been buried by sand artificially, and other groups were buried in different ways.
-Since the height of vertical ramets of S.
-littoreus is relatively high, it is naturally impossible for them to be completely buried in the sand.
-The treated S.littoreus, thus, only the stolons of which were buried at different depths and levels (see Figure~\ref{fig:diagram} and Table~\ref{tab:treatment}).
-Moreover, some adventitious roots on the stolons of selected plants were observed only a few days after sand burial, so the growth parameters of plants were dynamically investigated in 5, 9, 13, 17, 20 days after the sand burial to investigate the response of S.littoreus to severe sand burial over a short time scale.
+Since the height of vertical ramets of \textit{S.
+littoreus} is relatively high, it is naturally impossible for them to be completely buried in the sand.
+The treated \textit{S.
+littoreus}, thus, only the stolons of which were buried at different depths and levels (see Figure~\ref{fig:diagram} and Table~\ref{tab:treatment}).
+Moreover, some adventitious roots on the stolons of selected plants were observed only a few days after sand burial, so the growth parameters of plants were dynamically investigated in 5, 9, 13, 17, 20 days after the sand burial to investigate the response of \textit{S.
+littoreus} to severe sand burial over a short time scale.
 
 During the measurements, the sand burying the plants was carefully removed to one side in a wooden baffle, and the height of the vertical ramets, the length of the stolons and adventitious roots were all measured with a tape.
-In the end, all the plants were buried again with the previous sand.
+After measurements (in minutes generally), all the plants were buried again with the previous sand.
 When the experiments were finished, both above and below ground biomass of plants were collected and separated according to the label previously fixed on the stolons.
-Then all the samples were taken to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of 65℃ for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: 0.0001g).
+Then all the samples were taken to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of 65℃ for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: $0.0001g$).
 
@@
 
-\subsection{Mechanism of \textit{S. littoreus'} responses to severe sand burial}
+\subsection{Mechanism of \textit{\textit{S. littoreus}'} responses to severe sand burial}
 
-\subsection{Significance of \textit{S. littoreus'} adaptation to sand burial}
+% 我们的研究表明，老鼠楽对沙埋有多种不同的响应方式
+Our results suggest that \textit{S. littoreus} responds to sand burial in a variety of ways: uninfluenced ramets height, increased horizontal stolons length, and changed biomass allocation.
+% 这些响应方式的产生可能基于生理生态机制，我们通过和其它海岸沙生植物之间进行对比来进行探讨。
+These responses based on physiological and ecological mechanisms, which we can give a glance to by comparing with other coastal sandy plants.
+
+Sand burial has been assumed to reduce the photosynthetic area of species, which finally inhibit the plant performance in coastal sand dunes \citep{hespEcologicalProcessesPlant1991,brownMechanismsSurvivingBurial2018}.
+Species that withstand sand burial can recover very rapidly by elongating internodes in vertical shoots to overcome this physical barrier \citep{frosiniGlobalChangeResponse2012,keijsersModelingBiogeomorphicEvolution2016,quEffectsSandBurial2017,enriquezAssessingBeachDune2019}.
+However, this is inconsistent with our study, as we clearly show that sand burial on stolons of \textit{S.
+littoreus} in all treatments did not significantly affect the vertical growth of its conjoint ramets on the nebkhas.
+This is probably due to the growth characteristics of \textit{S.
+littoreus} which displays both vertical and horizontal development, the height of its ramets ranges from 40 to 60 cm, and it is virtually impossible to bury the entire vertical ramets by the sand sediments relative to its conjoint stolons during a single typhoon event \citep{xian-jiDiurnalVariationCharacteristics2017}.
+For the plants on the windward slopes, some unburied leaves will continue to provide photosynthetic substance to sustain the growth of sand dune plants even when significant burial has taken place (Figure~\ref{sample-pic}).
+As a result, growths of the ramets height were hardly effected by natural sand burial levels (which we simulated artificially).
+
+Sand burial is considered as the key factor controlling the spatial distribution of specific species, and species tolerant to sand burial usually react positively to sand burial, while they respond negatively or are uninfluenced if the sand burial rate is under some threshold \citep{hespReviewBiologicalGeomorphological1989, maunAdaptationsEnhancingSurvival1994,brownMechanismsSurvivingBurial2018}.
+Our results indicated that all sand burial treatments had a significant promotion on the growth of stolons on the windward slopes, and complete sand burial had a more obvious influence than sand deposition under half sand burial.
+Also consistent with our field investigation, we found that the tall remets of \textit{S.
+littoreus} could intercept sand sediments, and its conjoint stolons were buried at different levels on nebkhas, with more sand burial on the developmental succession period than it on the stabilized succession period.
+The stolon length of \textit{S.
+littoreus} on the former was much longer than it on the latter, which can be attributed to the more dynamic sand movement on the nebkhas in the developmental or building period (Figure~\ref{fig:growth}).
+Qu et al \citet{quEffectsSandBurial2017} also indicated that both seedling height and the survival rate of Artemisia halodendron was enhanced by intensive sand burial, but not stimulated by moderate burial, and shallow burial even had a negative impact on its survival and growth.
+Species usually stimulate their growing point according to the signal of the gravity stresses \citep{ruilinAnalysisGrowthStrategy2015}, and increase their node number and internode length to escape this physical barrier \citep{maunEffectsBurialSand1996}.
+The stresses signal of gravity in complete sand burial was usually stronger than in half sand burial \citep{wangAdvancesStudiesMorphological2005}.
+The current study indicated that complete sand burial on stolons of \textit{S.littoreus} on windward slopes could more rapidly promote plant growth than half sand burial, particularly the growth of the stolon apex, while the base and middle section of stolons were unaffected.
+Since plants often obtain their energy by respiration, once the acceleration of leaf growth still cannot meet the requirement of photosynthesis and break through the sand burial, the quantity of matter will be consumed.
+If the species fails to synthetize the required resources, the growth of leaves in the apex will accelerate rapidly in order to produce more photosynthetic substance to adapt to the sand burial.
+Our results further supported this hypothesis, we found that the growth of the stolon apex of \textit{S.littoreus} was even faster as the sand burial prolonged, and complete sand burial had more obvious effects than half sand burial.
+This has also verified by other studies, and, for example, in \textit{Hydrocotyle vulgaris} and \textit{Lamiastrum galeobdolon}, both clonal plants, the leaf area increased with a decrease of light intensity under sand burial \citep{dongMorphologicalResponsesLocal1995}.
+
+Production of adventitious roots and germination of leaves on stolons can induce the variation of its substance redistribution (Shi et al.
+2004), and change the biomass and growth rhythms of plants \citep{martinezResponsesDuneMosses1999,dechAdventitiousRootProduction2006}.
+Our results indicate that more adventitious roots were allocated to the stolon base, while a larger percent of leaves were observed on the stolon apex compared with other segments of stolons after sand burial.
+Generally, more sand burial depth can be found on the base of stolons due to sand sediments accumulated around the conjoint ramets, deeper sand burial can improve the access of roots to water, and favor the reservation of soil water \citep{yuanEffectsSandAccretion1993}.
+Moreover, \textit{S.littoreus} has a fibrous root system, and adventitious roots are initially produced in the node in the form of primordium.
+However, only the primordium in the unstretched base node of the stolons can develop well and finally break through the cuticular layer to produce the adventitious roots \citep{hochholdingerWeedsCropsGenetic2004}.
+As clonal plants, light will influence the phenotypic plasticity, and foraging behavior will change obviously in order to obtain enough resources \citep{fuResponsesGrasslandHerbaceous2013}. 
+The apex is usually the least buried segment of stolons, as the photosynthetic organ, more leaves emerging on the stolon apex will reduce the risk of further sand burial, increase the light capture for photosynthesis and carbon gain \citep{yuanEffectsSandAccretion1993,shiEffectsSandBurial2004,brownMechanismsSurvivingBurial2018}, and ensure enough supply of carbohydrates for \textit{S.littoreus} to escape the sand burial.
+This was confirmed by Maun \citet{maunAdaptationsEnhancingSurvival1994}, who showed that leaf growth, total leaf area, number of tillers and total dry biomass were usually stimulated by partial sand burial for most of the species seedlings he studied.
+Gilbert et al.
+\citet{gilbertGrowthResponsesCoastal2008} also demonstrated that sand burial could increase the leaf area in mobile-dune species, which fully or partially replaced the lost photosynthetic leaf area, so the shoot must elongate its stem to keep newly produced leaves above the sand surface subsequent to the sand burial.
+The stem tissue density of species is negatively related to the maximal stem elongation rate, which will reduce the cost of stem tissue production.
+Production of taller but thinner shoots was observed in the young clones of Sporobolus virginicus after increased burial severity \citep{frosiniGlobalChangeResponse2012}.
+This was also supported by our study which indicated that whatever the sand burial treatments, the dry biomass ratio of stem to total stolons showed a decreasing trend from the base to the apex of stolons.
+
+\subsection{Significance of \textit{\textit{S. littoreus}'} adaptation to sand burial}
+
+% 凭借上述机制，我们的结果表明老鼠楽能够有效在近地表被严重的沙埋情况下加速生长并存活下来。在热带和亚热带地区的海岸，频繁的台风常常为迎风坡带来数十厘米厚的沙埋，尽管这样的沙埋足以阻止大多数植物在此生长，但老鼠楽凭借其独特的适应能力在此占据来绝对优势。
+With the above mentioned mechanisms, our results indicate that \textit{S.
+littoreus} can accelerate and survive in the presence of severe sand burial near the surface.
+Along the coasts of the tropical and subtropical regions, frequent typhoons often bring with them tens of centimetres of sand to the windward slope each time.
+Although such sand is sufficient to prevent the development of most plants, \textit{S.
+littoreus} are invincible here due to their unique adaptive capacity.
+However, if the sand burial rate is over some threshold, the growth of sand dune species will be inhibited \citep{maunEffectsBurialSand1996, shiEffectsSandBurial2004}.
+Our observation showed that few \textit{S.
+littoreus} on the leeward slopes where the sand burial are so severe that few plants can survive (Figure~\ref{fig:leeward_swale} A).
+This was especially true for the former, which could be attributed to the excessive sand deposition continuously depleting the stored reserves of stolons, and the increased difficulty of plants to escape from sand burial \citep{frosiniGlobalChangeResponse2012}, finally inhibiting the growth of \textit{S.
+littoreus} on these slopes (Figure~\ref{sample-pic}).
+\textit{Ammophila arenaria} was monitored with an Unmanned Aerial Vehicle by Nolet et al.
+\citet{noletUAVimagingModelGrowth2018}, and their data also indicated that the optimal burial rate for this species was $0.31 m$ of sand per growing season, and the maximum tolerance for \textit{Ammophila} ranges from $0.78m$ to $0.96 m$ for cover and NDVI, respectively.
+What's more, in the swales with less sand and better habitats, \textit{S.
+littoreus} were scattered, but this was already an area where a variety of plants were symbiotic and competitive (Figure~\ref{fig:leeward_swale} B).
+
+\begin{figure}
+  \centering
+  \subfloat[Leeward.]{%
+  \resizebox*{6cm}{!}{\includegraphics{../figs/leeward.jpg}}}\hspace{5pt}
+  \subfloat[Swale.]{%
+  \resizebox*{6cm}{!}{\includegraphics{../figs/swale.jpg}}}
+  \caption{(a) Leeward is the most severe sand-burial position where few plants can survive there, including \textit{S.
+littoreus}.
+(b) Swales are much better habitats for plants because of little sand burial.
+However, \textit{S.
+littoreus} can not be dominant in this area because of heavy competition.}
+  \label{fig:leeward_swale}
+\end{figure}
+
+According to our study, we found that an optimal sand burial rate will not affect the survival of \textit{S.
+littoreus}, but enhance its growth on coastal sand dunes.
+This is consistent with its role as the dominant species in coastal foredunes, production of copious adventitious roots, extension of its stolons and alteration of biomass allocation pattern will all stimulate its shoot growth over the accumulating sand \citep{dechAdventitiousRootProduction2006}.
+We consider that the protective and defensive value offered by coastal sand dunes along the coastline of South China may be underestimated or neglected by the local government, and the coastal managers should allow the regular input of wind-blown sand towards this unique species for the protection and building of coastal sand dunes \citep{noletUAVimagingModelGrowth2018}, which can greatly mitigate the loss from coastal hazards in this region.
+So the nebkhas formed by \textit{S.
+littoreus} should be kept dynamic rather than stabilized by some invasive species such as \textit{C.
+equisetifolia} in Southeast China as such practices will lead to the loss of this native, highly adaptive species and accelerate the degradation of coastal dune systems in this region.
+
+\section{Conclusion}
+The following conclusions may be made:
+(1) All sand burial treatments had no significant impact on the growth of the height of ramets of \textit{S.
+littoreus}.
+However, the extension of its stolon was enhanced under intense sand burial (HI and CI) treatments by 24.56\% and 40.79\%, respectively.
+(2) Sand burial increased the production of adventitious roots mainly in the base section of stolons, and germination of leaves on the apex of stolons, as adaptation strategies to long-last sand burials.
+(3) Based on highly adaptation to intense sand burial (even buried brought by typhoons), \textit{S.
+littoreus} can be one of the most protective and defensive species in the coastal ecological systems.
 
@@
 
-An unnumbered section, e.g.\ \verb"\section*{Acknowledgements}", may be used for thanks, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.
+% An unnumbered section, e.g.\ \verb"\section*{Acknowledgements}", may be used for thanks, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.
+Thanks to Patrick Hesp for his assistance with editing our paper.
 
@@
 
-An unnumbered section, e.g.\ \verb"\section*{Disclosure statement}", may be used to declare any potential conflict of interest and included \emph{in the non-anonymous version} before any Notes or References, after any Acknowledgements and before any Funding information.
+% An unnumbered section, e.g.\ \verb"\section*{Disclosure statement}", may be used to declare any potential conflict of interest and included \emph{in the non-anonymous version} before any Notes or References, after any Acknowledgements and before any Funding information.
+The authors declare no competing interests.
 
@@
 
-An unnumbered section, e.g.\ \verb"\section*{Funding}", may be used for grant details, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.
+% An unnumbered section, e.g.\ \verb"\section*{Funding}", may be used for grant details, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.
+This research was supported by National Science Foundation (Grant No. 41101011; 41801101).
 
-\section*{Notes on contributor(s)}
+% \section*{Notes on contributor(s)}
 
-An unnumbered section, e.g.\ \verb"\section*{Notes on contributors}", may be included \emph{in the non-anonymous version} if required. A photograph may be added if requested.
+% An unnumbered section, e.g.\ \verb"\section*{Notes on contributors}", may be included \emph{in the non-anonymous version} if required. A photograph may be added if requested.
 
-\section*{Nomenclature/Notation}
+% \section*{Nomenclature/Notation}
 
-An unnumbered section, e.g.\ \verb"\section*{Nomenclature}" (or \verb"\section*{Notation}"), may be included if required, before any Notes or References.
+% An unnumbered section, e.g.\ \verb"\section*{Nomenclature}" (or \verb"\section*{Notation}"), may be included if required, before any Notes or References.
 
-\section*{Notes}
+% \section*{Notes}
 
-An unnumbered `Notes' section may be included before the References (if using the \verb"endnotes" package, use the command \verb"\theendnotes" where the notes are to appear, instead of creating a \verb"\section*").
+% An unnumbered `Notes' section may be included before the References (if using the \verb"endnotes" package, use the command \verb"\theendnotes" where the notes are to appear, instead of creating a \verb"\section*").
 
@@
 
-test\citep{quEffectsSandBurial2017}
-
-\bibliographystyle{tfcse.bst}
-\bibliography{interactcsesample}
+\bibliographystyle{tfcse}
+\bibliography{Pingtan_ecology}
 

### 2020-12-13 tex/interactcsesample.tex
update details

@@
 After measurements (in minutes generally), all the plants were buried again with the previous sand.
-When the experiments were finished, both above and below ground biomass of plants were collected and separated according to the label previously fixed on the stolons.
+When the experiments were finished, both above and below ground biomass of plants were collected and separated according to the label on the stolons.
 Then all the samples were taken to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of 65℃ for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: $0.0001g$).
@@
 The following conclusions may be made:
+
 (1) All sand burial treatments had no significant impact on the growth of the height of ramets of \textit{S.
@@
 However, the extension of its stolon was enhanced under intense sand burial (HI and CI) treatments by 24.56\% and 40.79\%, respectively.
+
 (2) Sand burial increased the production of adventitious roots mainly in the base section of stolons, and germination of leaves on the apex of stolons, as adaptation strategies to long-last sand burials.
+
 (3) Based on highly adaptation to intense sand burial (even buried brought by typhoons), \textit{S.

### 2020-12-25 tex/interactcsesample.tex
changed according to du's comments

@@
 % 结果表明，与对照组相比，砂埋对其匍匐茎的垂直生长无显著影响。
-The results indicated that, compared to the control group, sand burial on the \textit{S. littoreus} stolons had no significant impact on its vertical growth of conjoint ramets. 
+The results indicated that, compared with the control group, sand burial on the \textit{S. littoreus} stolons had no significant impact on the vertical growth of its conjoint ramets. 
 % 然而，随着砂埋的继续，匍匐茎顶端生长更快，完全砂埋比半砂埋影响更明显。
-However, growth of horizontal stolons on \textit{S.
+However, the horizontal growth of stolons on \textit{S.
 littoreus} were stimulated and significantly increased in half intense (HI) and complete intense (CI) sand burial by 24.56\% and 40.79\%, respectively.
 % 在不定根和叶片上，三个匍匐茎上的干生物量分配均发生了变化，而在茎上则没有变化。
-Throughout experiment, nearly all of adventitious roots were observed on base section of stolons, comparing with even no roots with the control groups. 
-After the 20-day artificial sand burial, dry biomass allocation were altered and ratio of dry weights between stem and leaf decreased, especially for apex sections. 
+Throughout the experiment, about 96\% of adventitious roots were observed on the base section of stolons, comparing with even no roots with the control groups. 
+After a 20-day artificial sand burial, the dry weight ratio between stem and leaf of \textit{S. littoreus} was decreased in all three sections of stolons, especially for the top sections. 
 % 通过匍匐茎的快速生长，匍匐茎基部产生大量不定根，匍匐茎顶端的叶片萌发率较高，可以适应完全的砂埋。
 Overall, \textit{S.
-littoreus} can adapt to complete and intense sand burial by rapid growth of stolons, abundant production of adventitious roots on the stolon base, and more germination of leaves on the stolon apex.
+littoreus} can adapt to the complete and intense sand burial by rapid growth of stolons, abundant production of adventitious roots on the stolon base, and more germination of leaves on the stolon top.
 \end{abstract}
@@
 \begin{keywords}
-Psammophytes; sand burial; \textit{\textit{Spinifex littoreus}}; responses, plant osmotic stresses
+Psammophytes; sand burial; \textit{\textit{Spinifex littoreus}}; responses; adventitious roots; Pingtan Island
 \end{keywords}
@@
 Almost no well-preserved coastal sand dunes are left, which apart from the loss of ecological functions and habitats, may ultimately result in coastal erosion and the loss of life, property and economy
-\citep{xian-jiDiurnalVariationCharacteristics2017}. 
-Hard engineering structures have been proved to be costly and detrimental for the protection of coastal regions, so it is very important to select natural and environmental-friendly methods for both the protection and restoration of the remaining coastal dune systems
+\citep{yangDiurnalvariationcharacteristics2017}. 
+Hard engineering structures have been proved to be costly and detrimental for the protection of coastal regions, so it is very important to select natural and environment-friendly methods for both the protection and restoration of the remaining coastal dune systems
 \citep{hanleyShiftingSandsCoastal2014}.
@@
 However, only a few species can survive in these ecosystems due to the harsh environmental stresses, such as drought, salt spray, strong winds, and especially the frequent and intensive sand burial 
-\citep{maunEffectsBurialSand1986,hespEcologicalProcessesPlant1991,maunAdaptationsEnhancingSurvival1994,y.-y.zhaoAdvanceDistributionAdaptability2014,duSaltSprayDistribution2020}. 
+\citep{maunEffectsBurialSand1986,hespEcologicalProcessesPlant1991,maunAdaptationsEnhancingSurvival1994,zhaoAdvanceDistributionAdaptability2014,duSaltSprayDistribution2020}. 
 Sand burial is commonly considered as the selective force for coastal plant regeneration and survival \citep{moreno-casasolaSandMovementFactor1986, maunAdaptationsEnhancingSurvival1994}, which can decrease and even eliminate the psammophytes if the sand burial levels are over their tolerance capacity, ultimately giving rise to the alteration of species composition in coastal dune systems \citep{maunZonationVegetationLacustrine1999,millerEffectsDisturbanceVegetation2015}.
@@
 \citep{hespReviewBiologicalGeomorphological1989}. 
-Generally, the growth of most psammophytes can be expected to be stimulated with low to moderate sand burial \citep{ruilinAnalysisGrowthStrategy2015,harrisDifferentialResponseBarrier2017,brownMechanismsSurvivingBurial2018,wangEffectsSandBurial2019}, while intensive sand burial will decrease its survival and per plant biomass \citep{maunEffectsBurialSand1996,franksBurialDisturbanceLeads2003}.
+Generally, the growth of most psammophytes can be expected to be stimulated with low to moderate sand burial \citep{zhouAnalysisgrowthstrategy2015,harrisDifferentialResponseBarrier2017,brownMechanismsSurvivingBurial2018,wangEffectsSandBurial2019}, while intensive sand burial will decrease its survival and per plant biomass \citep{maunEffectsBurialSand1996,franksBurialDisturbanceLeads2003}.
 Wang et al.
-\citet{wangAdvancesStudiesMorphological2005} demonstrated that both stem height in the vertical direction and leaf weight of \textit{Messerschmidia sibirica} were increased with light sand burial, while all decreased with moderate treatments contrasted with the control.
+\citet{wangAdvancesStudiesMorphological2005} demonstrated that both stem height in the vertical direction and leaf weight of \textit{Messerschmidia sibirica} were increased with light sand burial, while they all decreased with moderate treatments contrasted with the control.
 In addition, Zhou et al.
-\citet{ruilinPhysiologicalAdaptationMechanisms2015} showed that the growth of Artemisia desterorum was enhanced with moderate sand burial, but inhibited with intense sand burial.
+\citet{zhouphysiologicaladaptationmechanisms2015} showed that the growth of \textit{Artemisia desterorum} was enhanced with moderate sand burial, but inhibited with intense sand burial.
 Elongation of stolons, upward growth of ramets, and development of new adventitious roots are the main adaptive strategies for plants to sand burial, potentially leading to an alteration in the biomass allocation of psammophytes in coastal sand dunes \citep{dechAdventitiousRootProduction2006,frosiniGlobalChangeResponse2012,mendoza-gonzalezBiologicalFloraCoastal2014,brownMechanismsSurvivingBurial2018}.
@@
 \textit{Spinifex littoreus}, a herbaceous plant, is the dominant species in coastal foredunes in South China.
-It often grows vigorously above the backshore, and in the more dynamic foredune, while it declines in the more stabilized backdunes in similarity to its Australian and NZ cousins \textit{S.
+It often grows vigorously in the more dynamic foredune, while it declines in the more stabilized backdunes in similarity to its Australian and NZ cousins \textit{S.
 hirsutus} and \textit{S.
@@
 The leaf apex of \textit{S.
-littoreus} is very sharp and hard, which makes it difficult to be intruded, and is usually recognized as one of the excellent species for sand dune fixation in this region \citep{xian-jiDiurnalVariationCharacteristics2017}.
+littoreus} is very sharp and hard, which makes it difficult to be intruded, and is usually recognized as one of the excellent species for sand dune fixation in this region \citep{yangDiurnalvariationcharacteristics2017}.
 Frequent typhoons often occur in the growing season of this species in South China, which causes severe sand burial on \textit{S.
-littoreus}, particularly its stolons on nebkhas forming the foredune zone \citep{xian-jiDiurnalVariationCharacteristics2017}(Figure~\ref{sample-pic} A).
+littoreus}, particularly its stolons on nebkhas (a sand dune that forms around vegetation) forming the foredune zone \citep{yangDiurnalvariationcharacteristics2017}(Figure~\ref{fig:sample-pic} A).
 However, the tolerance capacity of this species to sand burial is still unclear at present, and how this species revitalized in the frequent sand burial is less studied.
-Furthermore, local government has planted an invasive species Casuarinas equisetifolia for the stabilization of nebkhas originally formed by \textit{S.
-littoreus}, which causes severe damage to this species, and will inevitably increase the fragility of coastal dune ecosystems in this region (Figure~\ref{sample-pic} B).
+Furthermore, local government has planted an invasive species \textit{Casuarinas equisetifolia} for the stabilization of nebkhas originally formed by \textit{S.
+littoreus}, which causes severe damage to this native species, and will inevitably increase the fragility of coastal dune ecosystems in this region (Figure~\ref{fig:sample-pic} B).
 Therefore, understanding the adaptive strategies of \textit{S.
@@
   \subfloat[\textit{S. littoreus} under natural sand burial.]{%
-  \resizebox*{6cm}{!}{\includegraphics{../figs/sand_buried_plants.jpg}}}\hspace{5pt}
-  \subfloat[\textit{C. equisetifolia} danmaged by sand burial.]{%
+  \resizebox*{6cm}{!}{\includegraphics{../figs/sand_buried_plants.png}}}\hspace{5pt}
+  \subfloat[\textit{C. equisetifolia} damaged by sand burial.]{%
   \resizebox*{6cm}{!}{\includegraphics{../figs/damaged_trees.jpg}}}
@@
 (b)The nebkhas formed by \textit{Spinifex littoreus} was stabilized by the planting of an invasive species Casuarinas equisetifolia seedlings on Pingtan Island, Fujian Province, China.}
-  \label{sample-pic}
+  \label{fig:sample-pic}
 \end{figure}
@@
 % 我们认为不同的沙埋情形将改变植株的生长方式，是该植物能够适应台风带来的强烈沙埋的关键性因素。
-In this study, we assume that the different sand burial changes the growth process of \textit{S.
-littoreus}, which is the key factor for the plants to adapt to the intense sand burial.
+In this study, we assume that the growths of \textit{S.
+littoreus} can be facilitated with the increase of sand burial, which is probably the key factor for this native plant to adapt to the intense sand burial.
 Then, the vertical height of ramets, horizontal length of stolons, and biomass allocation of adventitious roots, stems and leaves on stolons of \textit{S.
@@
 Pingtan island is located on the eastern coast of Fujian province, South China, with a sub-humid and oceanic monsoon climate.
-The study area is situated in the southeast of Pingtan island $(25^{\circ}26'36''-25^{\circ}26'48''N, 119^{\circ}46'09''-119^{\circ}46'21''E)$, and is usually regarded as hosting the most well-preserved coastal sand dunes in China (Figure~\ref{fig:map})
-\citep{xian-jiDiurnalVariationCharacteristics2017}. 
-Annual average temperature is 19.5℃, and precipitation is 1151 mm.
-The Monsoon is the dominant wind in this area, SE in the summer and NE in the winter, with an annual average wind speed of $6.9 m/s$.
-A total of 106 typhoons made landfall on Pingtan island from 1981 to 2019, average 2.65 times per year, and mainly they occur in July to September.
+The study area is situated in the southeast of Pingtan island $(25^{\circ}26'36''-25^{\circ}26'48''N, 119^{\circ}46'09''-119^{\circ}46'21''E)$, and is usually regarded as the most well-preserved coastal sand dunes in China (Figure~\ref{fig:map})
+\citep{yangDiurnalvariationcharacteristics2017}. 
+Annual average temperature is $19.5^{\circ}C$, and precipitation is $1151 mm$.
+The monsoon is the dominant wind in this area, SE in the summer and NE in the winter, with an annual average wind speed of $6.9 m/s$.
+A total of 106 typhoons made landfall on Pingtan island from 1981 to 2019, average 2.65 times per year, and mainly they occurred in July to September.
 The maximum wind speed can be up to $32.7 m/s$, ultimately leading to the severe sand burial on the psammophytes in this period.
@@
 Sediments are transported by the wind and intercepted by the ramets and stolons of \textit{S.
-littoreus}, and a discrete dune mound or hummock was usually formed by aeolian sand deposition within an isolated plant or group of plants \citep{hespCFDFlowDynamics2019}, ultimately developing into a 300 m wide nebkha dominated foredune zone (Figure~\ref{sample-pic}).
+littoreus}, and a discrete dune mound or hummock is usually formed by aeolian sand deposition within an isolated plant or group of plants \citep{hespCFDFlowDynamics2019}, ultimately developing into a 300 m wide nebkha dominated foredune zone (Figure~\ref{fig:sample-pic}).
 \textit{S.
-littoreus} is the dominant species in the study area and the auxiliary plants including \textit{Oenothera drummondii}, \textit{Cynodondactylon}, \textit{Pluchea pteropoda}, and \textit{Sesuvium portulacastrum}.
+littoreus} is the dominant species in the study area and the auxiliary plants including \textit{Oenothera drummondii}, \textit{Cynodon dactylon}, \textit{Pluchea pteropoda}, and \textit{Sesuvium portulacastrum}.
 
@@
 Considering most of the \textit{S.
-littoreus} were distributed on the windward slopes, 35 healthy plants with uniform size and comparable age were selected on the windward slopes were chosen for study.
-All the observed plants can be well distinguished from surrounding plants, and the height of vertical ramets and the length of stolons were all similar with each other before the burial treatments.
-Stolons of plants on the windward slopes were selected, and labeled with a red cord at points 1/3 and 2/3 of the length from the stem base to the apex of the stolons.
+littoreus} were distributed on the windward slope of nebkhas in mobile dunes belt, 35 healthy plants with uniform size and comparable age were selected for study on this slope (Figure\ref{fig:leeward_swale}).
+All the observed plants can be well distinguished from surrounding plants, the height of vertical ramets and the length of stolons were all similar with each other before the burial treatments.
+Stolons of \textit{S.
+littoreus} on the windward slopes were selected, and labeled with a red cord at points 1/3 and 2/3 of the length from the stem base to the top of the stolons.
 Weeds around the selected plants were manually cleared, and wooden frames 20 cm in height (similar to the height of stolons) were set around the selected plants.
-Later, all the observed plants were fixed with a label, and its serial number was recorded on the label and wooden baffles respectively in order to facilitate periodic measurements later.
+Later, all the observed plants were fixed with a label, and its serial number was recorded on the label and wooden baffles respectively in order to facilitate the periodic measurements later.
 The few adventitious roots present on the stolons of the observed plants were completely eliminated, the height of vertical ramets and length of stolons were measured separately before the experiments began.
-Later, all the plants were buried with sand from the nearby dunes according to a variety of different treatments (Figure~\ref{fig:diagram}).
+Later, all the plants were buried with sand from the nearby dunes (Figure~\ref{fig:diagram}, Table~\ref{tab:treatment}).
+While control groups (CG) had not been buried by sand artificially, and other groups were buried in different ways.
 
@@
 
-While control groups (CG) had not been buried by sand artificially, and other groups were buried in different ways.
 Since the height of vertical ramets of \textit{S.
@@
 littoreus}, thus, only the stolons of which were buried at different depths and levels (see Figure~\ref{fig:diagram} and Table~\ref{tab:treatment}).
-Moreover, some adventitious roots on the stolons of selected plants were observed only a few days after sand burial, so the growth parameters of plants were dynamically investigated in 5, 9, 13, 17, 20 days after the sand burial to investigate the response of \textit{S.
+Moreover, some adventitious roots on the stolons of selected plants were observed only a few days after treatments, so the growth parameters of plants were dynamically investigated in 5, 9, 13, 17, 20 days after the sand burial to investigate the response of \textit{S.
 littoreus} to severe sand burial over a short time scale.
@@
 During the measurements, the sand burying the plants was carefully removed to one side in a wooden baffle, and the height of the vertical ramets, the length of the stolons and adventitious roots were all measured with a tape.
-After measurements (in minutes generally), all the plants were buried again with the previous sand.
+Considering the uncovering and re-covering of sand will probably affect the gravity signal of plants to sand burial, we finished our measurements in minutes to minimize the potential disturbance, and re-covered the plants to the previous sand burial level with same sand.
 When the experiments were finished, both above and below ground biomass of plants were collected and separated according to the label on the stolons.
-Then all the samples were taken to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of 65℃ for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: $0.0001g$).
+Then all the samples were taken back to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of 65℃ for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: $0.0001g$).
 
@@
 
-\subsection{Influence of sand burial on growth processes of \textit{S. littoreus}}
+\subsection{Influence of sand burial on the growths of \textit{S. littoreus}}
+
+After a 20-day sand burial experiment, we found that the ramet height of \textit{S.
+littoreus} did not show any significant difference compared with the control group (CG).
+However, there were significant effects on the growth of horizontal stolons in both half-intense sand burial (HI) and complete-intense sand burial (CI) treatments, particularly the latter (Figure~\ref{fig:lattice}).
+Specifically, the significant effect of sand burial on the stolon growth was firstly observed at 9 days for the CI treatments, while it delayed at 13 days for the HI treatments ($P<0.05$).
+Moreover, the growth of horizontal stolons was more enhanced by sand burial in CI groups than HI groups, with the stolon length increased by $40.79\%$ in CI treatments, while $24.56\%$ in HI treatments after the end of 20-day sand burial experiment (Figure~\ref{fig:growth} A and B).
+Based on that, the proportion of stolon length in top section was increased continuously from $22.09\%$, $25.53\%$ to $46.48\%$, $50.20\%$, for HI and CI treatments, respectively.
 
@@
   \centering
-  \includegraphics[scale=0.8]{../figs/grid_differences.jpg}
+  \includegraphics[scale=0.7]{../figs/grid_differences.jpg}
   \caption{
@@
   \centering
-  \includegraphics[scale=0.8]{../figs/growth_process.jpg}
+  \includegraphics[scale=0.7]{../figs/growth_process.jpg}
   \caption{
@@
 
-% 不同的沙埋处理下的老鼠楽株高的生长过程与空白对照之间没有显著差异（图1A），但沙埋对老鼠楽匍匐茎的伸长生长产生了显著影响（图1B）。
-With different treatments, there was no significant difference between the growth of ramets height, but with significant effects on the growth of horizontal stolons when intense half sand burial (HI) and complete intense sand burial (CI) (Figure~\ref{fig:lattice}).
-While the significant effect of CI occurred after 9 days after sand burial treatment, the significant effect of a HI group occurred at 13 days and 20 days after sand burial. 
-% CI组不仅时间效应出现的更早，而且对水平stolons生长的促进作用也大于HI组，在20天砂埋试验结束时，其stolons长度显著增加24.56\%和40.79\%。
-Not only did the time effect appear earlier with the CI group, but also had a greater promoting effect on the growth of horizontal stolons than the HI group, with significant increases in stolons' length of 40.79\% and 24.56\% respectively at the end of 20-day sand burial experiment (Figure~\ref{fig:growth} A and B).
-% 其伸长生长过程都在不断增加顶端1/3长度所占的比例，而基部长度占比和中段的长度占比均匀下降（图2C-D）。
-During the elongation growth process, the proportion of the length of the top 1/3 (apex) increased continuously, while the proportion of the length of the base and the length of the middle sections decreased uniformly (Figure~\ref{fig:growth} C and D).
-
-\subsection{Influence of sand burial on the biomass allocation}
+\subsection{Influence of sand burial on the biomass allocation of \textit{S. littoreus}}
 \begin{figure}
@@
   \caption{
-    Ratio between stem weights and leaf weights after the experiments under different treatments.
-The white lines denote mean ratio of the control group (CG) while the grey spans denote the standard error of.
-Weights ratio from different sections were compared one by one (\textbf{A:} base sections, \textbf{B:} middle sections, \textbf{C:} apex sections, \textbf{D:} all sections).
+    Weight ratio between stem and leaf after the end of experiments under different treatments.
+The white lines denote mean ratio of the control group (CG) while the grey spans denote the standard error of the control group.
+Weights ratio from different sections were compared one by one (\textbf{A:} base sections, \textbf{B:} middle sections, \textbf{C:} top sections, \textbf{D:} all sections).
   }
@@
 % 大多数的人工沙埋不同程度上促进了不定根的生成，无论是不定根数量还是总长度（Fig3）。
-Most of sand-burial treatments promote the generation of adventitious roots to varying degrees, both in terms of the number of roots and the total length of the roots (Figure~\ref{fig:roots} A and B).
+The production of adventitious roots was promoted in most of the sand burial treatments, both in total length and number of roots.
+The most increase was observed in the HM treatments, and the average root length is $5.1cm$, the average root number is $2$, while no adventitious roots were observed in the CG treatments (Figure~\ref{fig:roots} A and B).
 % 而且不定根主要分布在基部，顶端无不定根生成。
-What's more, the adventitious roots are mainly distributed at the base and the adventitious roots are not generated at the apex (Figure~\ref{fig:roots} C).
+The adventitious roots were mainly occurred at the base section of stolons (96\%), and few (4\%) were found at the middle section, but no adventitious roots were found at top sections (Figure~\ref{fig:roots}C).
 % 经过20天的沙埋实验，老鼠楽植株茎和叶片的干重比例在不同程度上发生了改变。
-After 20 days of sand-burying experiments, the ratio of dry weight between stems and leaves of \textit{S.
-littoreus} plant changed to varying degrees (most of which decreased in ratio of stem weight and leaf weight) under different treatments (Figure~\ref{fig:ratio}).
-% 相对于空白对照组来说，沙埋使得植株将干重更多分配在茎上而非叶片上，在植株的顶端尤其明显。
-Compared with the control group (CG), sand burial caused the plant to distribute dry weight more on the stem than on the leaves, especially at the top of the plant (Figure~\ref{fig:ratio} C).
+The dry weight ratio between stems and leaves of \textit{S.
+littoreus} was decreased under most of the sand burial treatments compared with the CG treatments, and varied in different sections of stolons.
+More biomass was allocated to leaves, particularly for the top section of stolons (Figure~\ref{fig:ratio}).
 
@@
 
-\subsection{Mechanism of \textit{\textit{S. littoreus}'} responses to severe sand burial}
+\subsection{Responses of \textit{S. littoreus} to severe sand burial}
 
@@
 
-Sand burial has been assumed to reduce the photosynthetic area of species, which finally inhibit the plant performance in coastal sand dunes \citep{hespEcologicalProcessesPlant1991,brownMechanismsSurvivingBurial2018}.
-Species that withstand sand burial can recover very rapidly by elongating internodes in vertical shoots to overcome this physical barrier \citep{frosiniGlobalChangeResponse2012,keijsersModelingBiogeomorphicEvolution2016,quEffectsSandBurial2017,enriquezAssessingBeachDune2019}.
-However, this is inconsistent with our study, as we clearly show that sand burial on stolons of \textit{S.
-littoreus} in all treatments did not significantly affect the vertical growth of its conjoint ramets on the nebkhas.
+Sand burial has been assumed to reduce the photosynthetic area of species, which finally inhibit the plant performance in coastal sand dunes \citep{hespEcologicalProcessesPlant1991, brownMechanismsSurvivingBurial2018}.
+Species that withstand sand burial can recover very rapidly by elongating internodes in vertical shoots to overcome this physical barrier \citep{frosiniGlobalChangeResponse2012,keijsersModelingBiogeomorphicEvolution2016, quEffectsSandBurial2017,enriquezAssessingBeachDune2019}.
+However, this was inconsistent with our study, as we clearly showed that all sand burial treatments on stolons had no significant impact on the vertical growth of its conjoint ramets on the nebkhas.
 This is probably due to the growth characteristics of \textit{S.
-littoreus} which displays both vertical and horizontal development, the height of its ramets ranges from 40 to 60 cm, and it is virtually impossible to bury the entire vertical ramets by the sand sediments relative to its conjoint stolons during a single typhoon event \citep{xian-jiDiurnalVariationCharacteristics2017}.
-For the plants on the windward slopes, some unburied leaves will continue to provide photosynthetic substance to sustain the growth of sand dune plants even when significant burial has taken place (Figure~\ref{sample-pic}).
-As a result, growths of the ramets height were hardly effected by natural sand burial levels (which we simulated artificially).
+littoreus}, which displays both vertical and horizontal extension, the height of its ramets ranges from 40 to 60 cm, and it is virtually impossible to bury the entire vertical ramets by the sand sediments relative to its conjoint stolons during a single typhoon event \citep{yangDiurnalvariationcharacteristics2017}.
+For the plants on the windward slopes, some unburied leaves are expected to provide photosynthetic substance to sustain the continuous growth of \textit{S.
+littoreus} even when severe burial has taken place (Figure~\ref{fig:sample-pic}).
 
-Sand burial is considered as the key factor controlling the spatial distribution of specific species, and species tolerant to sand burial usually react positively to sand burial, while they respond negatively or are uninfluenced if the sand burial rate is under some threshold \citep{hespReviewBiologicalGeomorphological1989, maunAdaptationsEnhancingSurvival1994,brownMechanismsSurvivingBurial2018}.
-Our results indicated that all sand burial treatments had a significant promotion on the growth of stolons on the windward slopes, and complete sand burial had a more obvious influence than sand deposition under half sand burial.
-Also consistent with our field investigation, we found that the tall remets of \textit{S.
-littoreus} could intercept sand sediments, and its conjoint stolons were buried at different levels on nebkhas, with more sand burial on the developmental succession period than it on the stabilized succession period.
+Consequently, the rapid growth of ramets height in \textit{S.
+littoreus} is not considered as the priority for the escape of sand burial, but it inclines to increase the stolon length due to its vulnerability to buried in a typhoon event, which may contribute to the no significant impact on the ramets height by artificial sand burial in our experiment \citep{maunAdaptationsEnhancingSurvival1994}.
+Our field investigation further showed that the maximum length of \textit{S.littoreus} stolons could be up to $2-3 m$, which was about to 4-6 times of its ramets height in a frequent sand burial habitat (Figure~\ref{fig:added}B).
+This is in agreement to the previous study from Woodhouse et al.
+\citeyear{woodhouseEffectSpeciesDune1977}, who reported that Uniola paniculata tended to grow upward rather than seaward, while \textit{Ammophila breviligulata} preferred to colonize seaward beach surfaces by rhizome growth, which may explain the wider distribution of the latter in an intensive sand burial environment subsequently.
+
+\begin{figure}[!h]
+  \centering
+  \subfloat[Developmental period.]{%
+  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9a.jpg}}}\hspace{5pt}
+  \subfloat[Stabilized period.]{%
+  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9b.jpg}}}
+  \caption{The stolon length of \textit{S. littoreus} on nebkhas in the developmental period (a) and the stabilized period (b).} 
+  \label{fig:added}
+\end{figure}
+
+Extensive colonization of horizontal stolons after sand burial will facilitate the plants to increase its capacity for utilization of water and nutrition, which is especially critical for the establishment of plants in a resource-poor environment, such as coastal sand dunes, and further enhance their growth as the dominant species in coastal sand dunes.
+Our results indicated that all sand burial treatments had a significant promotion on the  stolons growth, and complete sand burial had a more obvious influence than half sand burial.
+Species usually stimulate their growing point according to the signal of the gravity signal stresses \citep{zhouAnalysisgrowthstrategy2015}, and increase their node number and internode length to escape this physical barrier \citep{maunEffectsBurialSand1996}.
+The stresses signal of gravity signal in complete sand burial was usually stronger than it in half sand burial \citep{wangAdvancesStudiesMorphological2005}.
+This was consistent with our field investigation, we found that the tall remets of \textit{S.
+littoreus} could intercept sand sediments, and its conjoint stolons were buried at different levels on, with more sand burial on nebkhas the than it on swales.
 The stolon length of \textit{S.
-littoreus} on the former was much longer than it on the latter, which can be attributed to the more dynamic sand movement on the nebkhas in the developmental or building period (Figure~\ref{fig:growth}).
-Qu et al \citet{quEffectsSandBurial2017} also indicated that both seedling height and the survival rate of Artemisia halodendron was enhanced by intensive sand burial, but not stimulated by moderate burial, and shallow burial even had a negative impact on its survival and growth.
-Species usually stimulate their growing point according to the signal of the gravity stresses \citep{ruilinAnalysisGrowthStrategy2015}, and increase their node number and internode length to escape this physical barrier \citep{maunEffectsBurialSand1996}.
-The stresses signal of gravity in complete sand burial was usually stronger than in half sand burial \citep{wangAdvancesStudiesMorphological2005}.
-The current study indicated that complete sand burial on stolons of \textit{S.littoreus} on windward slopes could more rapidly promote plant growth than half sand burial, particularly the growth of the stolon apex, while the base and middle section of stolons were unaffected.
-Since plants often obtain their energy by respiration, once the acceleration of leaf growth still cannot meet the requirement of photosynthesis and break through the sand burial, the quantity of matter will be consumed.
-If the species fails to synthetize the required resources, the growth of leaves in the apex will accelerate rapidly in order to produce more photosynthetic substance to adapt to the sand burial.
-Our results further supported this hypothesis, we found that the growth of the stolon apex of \textit{S.littoreus} was even faster as the sand burial prolonged, and complete sand burial had more obvious effects than half sand burial.
-This has also verified by other studies, and, for example, in \textit{Hydrocotyle vulgaris} and \textit{Lamiastrum galeobdolon}, both clonal plants, the leaf area increased with a decrease of light intensity under sand burial \citep{dongMorphologicalResponsesLocal1995}.
+littoreus} on nebkhas in developmental period was much longer than it in stabilized period, which can be attributed to the more dynamic sand movement on the fomer (Figure~\ref{fig:added}).
 
-Production of adventitious roots and germination of leaves on stolons can induce the variation of its substance redistribution (Shi et al.
-2004), and change the biomass and growth rhythms of plants \citep{martinezResponsesDuneMosses1999,dechAdventitiousRootProduction2006}.
-Our results indicate that more adventitious roots were allocated to the stolon base, while a larger percent of leaves were observed on the stolon apex compared with other segments of stolons after sand burial.
-Generally, more sand burial depth can be found on the base of stolons due to sand sediments accumulated around the conjoint ramets, deeper sand burial can improve the access of roots to water, and favor the reservation of soil water \citep{yuanEffectsSandAccretion1993}.
-Moreover, \textit{S.littoreus} has a fibrous root system, and adventitious roots are initially produced in the node in the form of primordium.
-However, only the primordium in the unstretched base node of the stolons can develop well and finally break through the cuticular layer to produce the adventitious roots \citep{hochholdingerWeedsCropsGenetic2004}.
-As clonal plants, light will influence the phenotypic plasticity, and foraging behavior will change obviously in order to obtain enough resources \citep{fuResponsesGrasslandHerbaceous2013}. 
-The apex is usually the least buried segment of stolons, as the photosynthetic organ, more leaves emerging on the stolon apex will reduce the risk of further sand burial, increase the light capture for photosynthesis and carbon gain \citep{yuanEffectsSandAccretion1993,shiEffectsSandBurial2004,brownMechanismsSurvivingBurial2018}, and ensure enough supply of carbohydrates for \textit{S.littoreus} to escape the sand burial.
-This was confirmed by Maun \citet{maunAdaptationsEnhancingSurvival1994}, who showed that leaf growth, total leaf area, number of tillers and total dry biomass were usually stimulated by partial sand burial for most of the species seedlings he studied.
+Production of adventitious roots on the stolons will enhance the capacity of plants to use limited soil water and nutrition, and change the biomass and growth rhythms of plants \citep{martinezResponsesDuneMosses1999,dechAdventitiousRootProduction2006}.
+Our results indicated that the adventitious roots were produced on the \textit{S.
+littoreus} stolons in most of the sand burial treatments, both total length and number of roots were increased compared with the CG treatments, which will facilitate their revitalization from sand burial cause by typhoon events.
+More adventitious roots were allocated to the stolon base, after sand burial.
+Generally, sand burial depth is deeper on the stolon base than other stolon sections due to more sand sediments accumulated around the conjoint ramets, which will increase the capacity for root growth and can improve their access to soil water \citep{yuanEffectsSandAccretion1993}.
+Moreover, \textit{S.littoreus} has a fibrous root system, and adventitious roots are initially produced from the primordium in the stolon node.
+However, only the primordium in the stolons base can develop well and finally break through the cuticular layer to produce the adventitious roots \citep{hochholdingerWeedsCropsGenetic2004}.
+
+The top of stolon is usually the least buried segment of stolons, as the photosynthetic organ, more leaves emerging on the top of stolon will reduce the risk of plants from further sand burial, increase their light capture for photosynthesis and carbon gain \citep{yuanEffectsSandAccretion1993, shiEffectsSandBurial2004, brownMechanismsSurvivingBurial2018}, and ensure enough supply of carbohydrates for plants to escape the sand burial.
+Our study further supported this conclusion, and we found that a larger percent of leaves were observed on the top of stolon compared with other stolon sections.
 Gilbert et al.
-\citet{gilbertGrowthResponsesCoastal2008} also demonstrated that sand burial could increase the leaf area in mobile-dune species, which fully or partially replaced the lost photosynthetic leaf area, so the shoot must elongate its stem to keep newly produced leaves above the sand surface subsequent to the sand burial.
-The stem tissue density of species is negatively related to the maximal stem elongation rate, which will reduce the cost of stem tissue production.
-Production of taller but thinner shoots was observed in the young clones of Sporobolus virginicus after increased burial severity \citep{frosiniGlobalChangeResponse2012}.
-This was also supported by our study which indicated that whatever the sand burial treatments, the dry biomass ratio of stem to total stolons showed a decreasing trend from the base to the apex of stolons.
+\citeyear{gilbertGrowthResponsesCoastal2008} also demonstrated that sand burial could increase the leaf area in mobile dune species, which fully or partially replaced the lost photosynthetic leaf area, so the shoot must elongate its stem to keep newly produced leaves above the sand surface subsequent to the sand burial.
+Consequently, in order to reduce the cost of stem tissue production, the stem tissue density of species is usually negative to the maximal stem elongation rate \citep{frosiniGlobalChangeResponse2012}.
+We also found that the extension rate was faster in top of stolon than other stolon sections of \textit{S.littoreus}, and it grew even faster as the sand burial prolonged.
+Consequently, the dry biomass ratio of stem to leaves showed a decreasing trend from the stolon base to the stolon top of \textit{S.
+littoreus} in all sand burial treatments.
 
@@
 % 凭借上述机制，我们的结果表明老鼠楽能够有效在近地表被严重的沙埋情况下加速生长并存活下来。在热带和亚热带地区的海岸，频繁的台风常常为迎风坡带来数十厘米厚的沙埋，尽管这样的沙埋足以阻止大多数植物在此生长，但老鼠楽凭借其独特的适应能力在此占据来绝对优势。
-With the above mentioned mechanisms, our results indicate that \textit{S.
-littoreus} can accelerate and survive in the presence of severe sand burial near the surface.
-Along the coasts of the tropical and subtropical regions, frequent typhoons often bring with them tens of centimetres of sand to the windward slope each time.
-Although such sand is sufficient to prevent the development of most plants, \textit{S.
-littoreus} are invincible here due to their unique adaptive capacity.
+Response of plants to sand burial is usually species specific, and the growth of plants will be enhanced under optimal sand burial rate \citep{noletUAVimagingModelGrowth2018}.
+We found that \textit{S.littoreus} can adapt to the severe sand burial caused by frequent typhoons in our study area, and will revitalize later by increasing the horizontal stolon length, producing abundant adventitious roots on the stolon base and allocate more biomass to leaves on the stolon apex \citep{yuanEffectsSandAccretion1993}.
 However, if the sand burial rate is over some threshold, the growth of sand dune species will be inhibited \citep{maunEffectsBurialSand1996, shiEffectsSandBurial2004}.
-Our observation showed that few \textit{S.
-littoreus} on the leeward slopes where the sand burial are so severe that few plants can survive (Figure~\ref{fig:leeward_swale} A).
-This was especially true for the former, which could be attributed to the excessive sand deposition continuously depleting the stored reserves of stolons, and the increased difficulty of plants to escape from sand burial \citep{frosiniGlobalChangeResponse2012}, finally inhibiting the growth of \textit{S.
-littoreus} on these slopes (Figure~\ref{sample-pic}).
-\textit{Ammophila arenaria} was monitored with an Unmanned Aerial Vehicle by Nolet et al.
-\citet{noletUAVimagingModelGrowth2018}, and their data also indicated that the optimal burial rate for this species was $0.31 m$ of sand per growing season, and the maximum tolerance for \textit{Ammophila} ranges from $0.78m$ to $0.96 m$ for cover and NDVI, respectively.
-What's more, in the swales with less sand and better habitats, \textit{S.
-littoreus} were scattered, but this was already an area where a variety of plants were symbiotic and competitive (Figure~\ref{fig:leeward_swale} B).
+Our field investigation showed that few \textit{S.
+littoreus} can be found on the leeward slope of nebkhas (Figure~\ref{fig:leeward_swale}A), which can be attributed to the excessive sand burial on both ramets and conjoint stolons of \textit{S.
+littoreus}.
+Absence of photosynthesis area, combined with the continuous depletion of reserves previously stored in the plants \citep{frosiniGlobalChangeResponse2012}, finally lead to the failure of \textit{S.
+littoreus} escaped from excessive sand burial on leeward slope of nebkhas (Figure~\ref{fig:sample-pic}).
+Similarly, if the sand burial rate is below some threshold, the species that can not withstand the severe sand burial will co-occur with those resistant to it.
+We found that low to moderate sand burial treatments had no significant impact on the stolon extension of \textit{S.littoreus}, which will not favor its access to the more habitats for soil water and nutrition, and further weaken its advantages as the dominant species with the decrease of sand burial rate.
+This is also consistent with our field investigation, \textit{Oenothera drummondii}, an invasive species widely distributed on the stabilized dune in South China, was co-occurred with \textit{S.littoreus} on the less dynamic nebkhas in our study area (Figure~\ref{fig:added}A).
+
+We consider that the capacity of \textit{S.
+littoreus} stabilizing and building the coastal sand dunes along the coastline of South China has been  underestimated or neglected by the local government, and the coastal managers should allow the regular input of wind-blown sand towards this unique species for the protection and building of coastal sand dunes \citep{noletUAVimagingModelGrowth2018}, which can greatly mitigate the loss from coastal hazards in this region.
+So the nebkhas formed by \textit{S.
+littoreus} should be kept dynamic rather than stabilized by some invasive species such as \textit{C.
+equisetifolia} in Southeast China.
+Otherwise, it will further increase the risk of species invasion on coastal sand dunes, such as \textit{O.
+drummondii}.
+Consequently, this native and highly adaptive species will gradually be replaced and eradicated, and  the degradation of coastal dune systems in this region was also expected to be aggravated.
 
@@
 
-According to our study, we found that an optimal sand burial rate will not affect the survival of \textit{S.
-littoreus}, but enhance its growth on coastal sand dunes.
-This is consistent with its role as the dominant species in coastal foredunes, production of copious adventitious roots, extension of its stolons and alteration of biomass allocation pattern will all stimulate its shoot growth over the accumulating sand \citep{dechAdventitiousRootProduction2006}.
-We consider that the protective and defensive value offered by coastal sand dunes along the coastline of South China may be underestimated or neglected by the local government, and the coastal managers should allow the regular input of wind-blown sand towards this unique species for the protection and building of coastal sand dunes \citep{noletUAVimagingModelGrowth2018}, which can greatly mitigate the loss from coastal hazards in this region.
-So the nebkhas formed by \textit{S.
-littoreus} should be kept dynamic rather than stabilized by some invasive species such as \textit{C.
-equisetifolia} in Southeast China as such practices will lead to the loss of this native, highly adaptive species and accelerate the degradation of coastal dune systems in this region.
-
 \section{Conclusion}
@@
 
-(1) All sand burial treatments had no significant impact on the growth of the height of ramets of \textit{S.
-littoreus}.
-However, the extension of its stolon was enhanced under intense sand burial (HI and CI) treatments by 24.56\% and 40.79\%, respectively.
+(1) All sand burial treatments had no significant impact on the 
+ramets height of S.
+littoreus.
+However, compared with the CG treatments, they significantly enhanced the stolon extension of S.
+littoreus under intense sand burial (HI and CI) treatments by 24.56\% and 40.79\%, respectively.
 
-(2) Sand burial increased the production of adventitious roots mainly in the base section of stolons, and germination of leaves on the apex of stolons, as adaptation strategies to long-last sand burials.
+(2) Sand burial stimulated the production of adventitious roots mainly on stolon base, and enhanced the germination of leaves on the top of stolon.
 
-(3) Based on highly adaptation to intense sand burial (even buried brought by typhoons), \textit{S.
-littoreus} can be one of the most protective and defensive species in the coastal ecological systems.
+(3) S. littoreus can adapt to the intense sand burial, it can be considered as one of the optimal species for stabilizing and building the coastal sand dunes in South China.
 

### 2020-12-28 tex/interactcsesample.tex
revised according to Du's comments -second v

@@
   Qirui Wu \textsuperscript{a},
-  Mingyang Ni \textsuperscript{a} and Yingling Zhang \textsuperscript{a}}\affil{\textsuperscript{a}School of Geography and Planning, Sun Yat-Sen University, Guangzhou, 510275, China; \textsuperscript{b} Guangdong Key Laboratory for Urbanization and Geo-simulation, Guangzhou, 510275, China}
+  Mingyang Ni \textsuperscript{a} and Yijia Wang \textsuperscript{a}}\affil{\textsuperscript{a}School of Geography and Planning, Sun Yat-Sen University, Guangzhou, 510275, China; \textsuperscript{b} Guangdong Key Laboratory for Urbanization and Geo-simulation, Guangzhou, 510275, China}
 }
@@
 % 研究了福建平潭岛海岸滨鹬对不同埋沙深度和埋沙深度的响应。
-The responses of \textit{Spinifex littoreus} to different sand burial depths and levels were examined on the coast of Pingtan island, Fujian Province, South China. 
+The responses of \textit{Spinifex littoreus} to different sand burial depths and levels were examined on the coast of Pingtan Island, Fujian Province, South China. 
 % 结果表明，与对照组相比，砂埋对其匍匐茎的垂直生长无显著影响。
-The results indicated that, compared with the control group, sand burial on the \textit{S. littoreus} stolons had no significant impact on the vertical growth of its conjoint ramets. 
+The results indicated that, compared with the control group (CG), sand burial on the \textit{S. littoreus} stolons had no significant impact on the vertical growth of its conjoint ramets. 
 % 然而，随着砂埋的继续，匍匐茎顶端生长更快，完全砂埋比半砂埋影响更明显。
-However, the horizontal growth of stolons on \textit{S.
-littoreus} were stimulated and significantly increased in half intense (HI) and complete intense (CI) sand burial by 24.56\% and 40.79\%, respectively.
+However, the horizontal growth of \textit{S.
+littoreus} stolons were stimulated and significantly increased in half-intense (HI) and complete-intense (CI) sand burial treatments by 24.56\% and 40.79\%, respectively.
 % 在不定根和叶片上，三个匍匐茎上的干生物量分配均发生了变化，而在茎上则没有变化。
-Throughout the experiment, about 96\% of adventitious roots were observed on the base section of stolons, comparing with even no roots with the control groups. 
-After a 20-day artificial sand burial, the dry weight ratio between stem and leaf of \textit{S. littoreus} was decreased in all three sections of stolons, especially for the top sections. 
+Throughout the experiment, about 96\% of adventitious roots were observed on the base section of stolons, while no roots in the control group (CG). 
+After a 20-day artificial sand burial treatments, the dry weight ratio between stem and leaf of \textit{S. littoreus} was decreased in all three sections of stolons, especially for the top sections. 
 % 通过匍匐茎的快速生长，匍匐茎基部产生大量不定根，匍匐茎顶端的叶片萌发率较高，可以适应完全的砂埋。
 Overall, \textit{S.
-littoreus} can adapt to the complete and intense sand burial by rapid growth of stolons, abundant production of adventitious roots on the stolon base, and more germination of leaves on the stolon top.
+littoreus} can adapt to the complete and intense sand burial in growing season by rapid growth of stolons, abundant production of adventitious roots on the stolon base, and more germination of leaves on the stolon top.
 \end{abstract}
@@
 % 主要介绍沙生植物对海岸生态系统对重要意义
-Sand dunes occupy a finite area in coastal regions, but they are characterized by providing multiple ecological services, and play an important role in the sustainable development in those regions with rising sea levels, surface subsidence and coastal hazards
+Coastal sand dunes can provide multiple ecological services and play an important role in the sustainable development of coastal areas with rising sea levels, surface subsidence and coastal hazards 
 \citep{martinezFragilityConservationWorld2004,debattistiBelowgroundBiomassPlants2020}. 
-Recently, due to the influence of both climate change and anthropogenic activities, many coastal sand dunes have been modified or destroyed, and this can, or has potentially led to the retreat of coastlines, disappearance of habitats, loss of biodiversity, and severe degradation of ecosystem functions in coastal sand dunes
+Recently, due to the influence from both climate change and anthropogenic activities, many coastal sand dunes have been modified or destroyed, and this can, or has potentially led to the retreat of coastlines, disappearance of habitats, loss of biodiversity, and severe degradation of ecosystem functions in coastal sand dunes
 \citep{feaginCoastalErosionGlobal2005,schlacherVegetationGhostCrabs2011,quEffectsSandBurial2017}. 
@@
 % 主要介绍沙埋与沙生植物对关系
-Psammophytes can build and stabilize coastal dunes, which will favor the restoration of their ecological functions due to specific adaptive strategies 
+Psammophytes can build and stabilize coastal sand dunes, which will favor the restoration of their ecological functions due to specific adaptive strategies 
 \citep{yuanEffectsSandAccretion1993,brownMechanismsSurvivingBurial2018,debattistiBelowgroundBiomassPlants2020}. 
 However, only a few species can survive in these ecosystems due to the harsh environmental stresses, such as drought, salt spray, strong winds, and especially the frequent and intensive sand burial 
-\citep{maunEffectsBurialSand1986,hespEcologicalProcessesPlant1991,maunAdaptationsEnhancingSurvival1994,zhaoAdvanceDistributionAdaptability2014,duSaltSprayDistribution2020}. 
+\citep{maunEffectsBurialSand1986,hespEcologicalProcessesPlant1991,maunAdaptationsEnhancingSurvival1994,zhaoAdvanceDistributionAdaptability2014,duSaltSprayDistribution2020a}. 
 Sand burial is commonly considered as the selective force for coastal plant regeneration and survival \citep{moreno-casasolaSandMovementFactor1986, maunAdaptationsEnhancingSurvival1994}, which can decrease and even eliminate the psammophytes if the sand burial levels are over their tolerance capacity, ultimately giving rise to the alteration of species composition in coastal dune systems \citep{maunZonationVegetationLacustrine1999,millerEffectsDisturbanceVegetation2015}.
@@
 % 这一段主要讲海岸沙生植物耐沙埋能力的用处
-The tolerance capacity to different sand burial levels is varied among species, which finally affect the initial and subsequent coastal dune development and morphology 
+The tolerance capacity of species to different sand burial levels varies greatly, which finally affect the initial and subsequent coastal dune development and morphology 
 \citep{hespReviewBiologicalGeomorphological1989}. 
 Generally, the growth of most psammophytes can be expected to be stimulated with low to moderate sand burial \citep{zhouAnalysisgrowthstrategy2015,harrisDifferentialResponseBarrier2017,brownMechanismsSurvivingBurial2018,wangEffectsSandBurial2019}, while intensive sand burial will decrease its survival and per plant biomass \citep{maunEffectsBurialSand1996,franksBurialDisturbanceLeads2003}.
-Wang et al.
 \citet{wangAdvancesStudiesMorphological2005} demonstrated that both stem height in the vertical direction and leaf weight of \textit{Messerschmidia sibirica} were increased with light sand burial, while they all decreased with moderate treatments contrasted with the control.
-In addition, Zhou et al.
-\citet{zhouphysiologicaladaptationmechanisms2015} showed that the growth of \textit{Artemisia desterorum} was enhanced with moderate sand burial, but inhibited with intense sand burial.
+In addition, \citet{zhouphysiologicaladaptationmechanisms2015} showed that the growth of \textit{Artemisia desterorum} was enhanced with moderate sand burial, but inhibited with intense sand burial.
 Elongation of stolons, upward growth of ramets, and development of new adventitious roots are the main adaptive strategies for plants to sand burial, potentially leading to an alteration in the biomass allocation of psammophytes in coastal sand dunes \citep{dechAdventitiousRootProduction2006,frosiniGlobalChangeResponse2012,mendoza-gonzalezBiologicalFloraCoastal2014,brownMechanismsSurvivingBurial2018}.
@@
 Frequent typhoons often occur in the growing season of this species in South China, which causes severe sand burial on \textit{S.
-littoreus}, particularly its stolons on nebkhas (a sand dune that forms around vegetation) forming the foredune zone \citep{yangDiurnalvariationcharacteristics2017}(Figure~\ref{fig:sample-pic} A).
-However, the tolerance capacity of this species to sand burial is still unclear at present, and how this species revitalized in the frequent sand burial is less studied.
+littoreus}, particularly its stolons on nebkhas (a sand dune that forms around vegetation) forming the foredune zone \citep{yangDiurnalvariationcharacteristics2017}(Figure~\ref{fig:sample-pic}a).
+However, the tolerance capacity of this species to sand burial is still unclear at present, and how this species revitalized in the sand burial caused by frequent typhoon events in growing season.
 Furthermore, local government has planted an invasive species \textit{Casuarinas equisetifolia} for the stabilization of nebkhas originally formed by \textit{S.
-littoreus}, which causes severe damage to this native species, and will inevitably increase the fragility of coastal dune ecosystems in this region (Figure~\ref{fig:sample-pic} B).
+littoreus}, which causes severe damage to this native species, and will inevitably increase the fragility of coastal dune ecosystems in this region (Figure~\ref{fig:sample-pic}b).
 Therefore, understanding the adaptive strategies of \textit{S.
-littoreus} to sand burial levels, and its role in the stabilization of coastal dunes are very crucial for the effective coastal management and conservation in South China.
+littoreus} to sand burial levels, and its role in the stabilization of coastal sand dunes are very crucial for the effective coastal management and conservation in South China.
 
@@
   \centering
-  \subfloat[\textit{S. littoreus} under natural sand burial.]{%
+  \subfloat[\textit{S. littoreus} was burial after a typhoon.]{%
   \resizebox*{6cm}{!}{\includegraphics{../figs/sand_buried_plants.png}}}\hspace{5pt}
-  \subfloat[\textit{C. equisetifolia} damaged by sand burial.]{%
+  \subfloat[\textit{S. littoreus} nebkhas was eradicated and planted with \textit{C. equisetifolia}.]{%
   \resizebox*{6cm}{!}{\includegraphics{../figs/damaged_trees.jpg}}}
-  \caption{(a) Intensive sand burial on the \textit{Spinifex littoreus} nebkhas on Pingtan island after typhoon Soudelor (1513) landed in Putian City, Fujian Province, China in August, 2015.
-(b)The nebkhas formed by \textit{Spinifex littoreus} was stabilized by the planting of an invasive species Casuarinas equisetifolia seedlings on Pingtan Island, Fujian Province, China.}
+  \caption{(a) Intensive sand burial on the \textit{Spinifex littoreus} nebkhas on Pingtan Island after typhoon Soudelor (1513) landed in Putian City, Fujian Province, China in August, 2015.
+(b) The nebkhas formed by \textit{Spinifex littoreus} was stabilized by the planting of an invasive species Casuarinas equisetifolia seedlings on Pingtan Island, Fujian Province, China.}
   \label{fig:sample-pic}
@@
 In this study, we assume that the growths of \textit{S.
-littoreus} can be facilitated with the increase of sand burial, which is probably the key factor for this native plant to adapt to the intense sand burial.
+littoreus} can be facilitated with the increase of sand burial, which is probably the key factor for this native plant to adapt to the intense sand burial caused by frequent typhoon events in growing season.
 Then, the vertical height of ramets, horizontal length of stolons, and biomass allocation of adventitious roots, stems and leaves on stolons of \textit{S.
@@
 
-Pingtan island is located on the eastern coast of Fujian province, South China, with a sub-humid and oceanic monsoon climate.
-The study area is situated in the southeast of Pingtan island $(25^{\circ}26'36''-25^{\circ}26'48''N, 119^{\circ}46'09''-119^{\circ}46'21''E)$, and is usually regarded as the most well-preserved coastal sand dunes in China (Figure~\ref{fig:map})
+Pingtan Island is located on the eastern coast of Fujian province, South China, with a sub-humid and oceanic monsoon climate.
+The study area is situated in the southeast of Pingtan Island $(25^{\circ}26'36''-25^{\circ}26'48''N, 119^{\circ}46'09''-119^{\circ}46'21''E)$, and is usually regarded as the most well-preserved coastal sand dunes in China (Figure~\ref{fig:map})
 \citep{yangDiurnalvariationcharacteristics2017}. 
@@
 The monsoon is the dominant wind in this area, SE in the summer and NE in the winter, with an annual average wind speed of $6.9 m/s$.
-A total of 106 typhoons made landfall on Pingtan island from 1981 to 2019, average 2.65 times per year, and mainly they occurred in July to September.
+A total of 106 typhoons made landfall on Pingtan Island from 1981 to 2019, average 2.65 times per year, and mainly they occurred in July to September.
 The maximum wind speed can be up to $32.7 m/s$, ultimately leading to the severe sand burial on the psammophytes in this period.
@@
 \textit{S.
-littoreus} is the dominant species in the study area and the auxiliary plants including \textit{Oenothera drummondii}, \textit{Cynodon dactylon}, \textit{Pluchea pteropoda}, and \textit{Sesuvium portulacastrum}.
+littoreus} is the dominant species in the study area and the auxiliary plants including \textit{Oenothera drummondii}, \textit{Cynodon dactylon}, \textit{Pluchea pteropoda}, and \textit{Sesuvium portulacastrum} \citep{yangDiurnalvariationcharacteristics2017}.
 
@@
 Considering most of the \textit{S.
-littoreus} were distributed on the windward slope of nebkhas in mobile dunes belt, 35 healthy plants with uniform size and comparable age were selected for study on this slope (Figure\ref{fig:leeward_swale}).
+littoreus} were distributed on the windward slope of nebkhas in mobile dunes belt, 35 healthy plants with uniform size were selected for study on this slope (Figure\ref{fig:leeward_swale}).
 All the observed plants can be well distinguished from surrounding plants, the height of vertical ramets and the length of stolons were all similar with each other before the burial treatments.
@@
 littoreus} on the windward slopes were selected, and labeled with a red cord at points 1/3 and 2/3 of the length from the stem base to the top of the stolons.
-Weeds around the selected plants were manually cleared, and wooden frames 20 cm in height (similar to the height of stolons) were set around the selected plants.
+All plant species around the selected plants around the selected plants were manually cleared, and wooden frames $20 cm$ in height (similar to the height of stolons) were set around the selected plants.
 Later, all the observed plants were fixed with a label, and its serial number was recorded on the label and wooden baffles respectively in order to facilitate the periodic measurements later.
 The few adventitious roots present on the stolons of the observed plants were completely eliminated, the height of vertical ramets and length of stolons were measured separately before the experiments began.
-Later, all the plants were buried with sand from the nearby dunes (Figure~\ref{fig:diagram}, Table~\ref{tab:treatment}).
-While control groups (CG) had not been buried by sand artificially, and other groups were buried in different ways.
+Later, all the plants were buried with sand nearby artificially (Figure~\ref{fig:diagram}, Table~\ref{tab:treatment}), While control groups (CG) were unburied throughout the experiments.
 
@@
 
-Since the height of vertical ramets of \textit{S.
-littoreus} is relatively high, it is naturally impossible for them to be completely buried in the sand.
+Since the vertical ramets of \textit{S.
+littoreus} is relatively high, it is unlikely for them to be completely buried in single typhoon event (Figure~\ref{fig:sample-pic}a).
 The treated \textit{S.
@@
 When the experiments were finished, both above and below ground biomass of plants were collected and separated according to the label on the stolons.
-Then all the samples were taken back to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of 65℃ for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: $0.0001g$).
+Then all the samples were taken back to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of $65^{\circ}C$ for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: $0.0001g$).
 
@@
 Specifically, the significant effect of sand burial on the stolon growth was firstly observed at 9 days for the CI treatments, while it delayed at 13 days for the HI treatments ($P<0.05$).
-Moreover, the growth of horizontal stolons was more enhanced by sand burial in CI groups than HI groups, with the stolon length increased by $40.79\%$ in CI treatments, while $24.56\%$ in HI treatments after the end of 20-day sand burial experiment (Figure~\ref{fig:growth} A and B).
+Moreover, the growth of horizontal stolons was more enhanced by sand burial in CI treatments than HI treatments, with the stolon length increased by $40.79\%$ in CI treatments, while $24.56\%$ in HI treatments after the end of 20-day sand burial experiment (Figure~\ref{fig:growth}a and B).
 Based on that, the proportion of stolon length in top section was increased continuously from $22.09\%$, $25.53\%$ to $46.48\%$, $50.20\%$, for HI and CI treatments, respectively.
@@
   \caption{
-    Growth process of horizontal stolons with half intense (HI) group and complete intense (CI) group plants.
+    Growth process of horizontal stolons with half-intense (HI) group and complete-intense (CI) group plants.
     \textbf{A} growth of horizontal stolons' length of HI group, compared with the control group (CG).
@@
 The production of adventitious roots was promoted in most of the sand burial treatments, both in total length and number of roots.
-The most increase was observed in the HM treatments, and the average root length is $5.1cm$, the average root number is $2$, while no adventitious roots were observed in the CG treatments (Figure~\ref{fig:roots} A and B).
+The most increase was observed in the HM treatments, and the average root length is $5.1cm$, the average root number is $2$, while no adventitious roots were observed in the CG treatments (Figure~\ref{fig:roots}a and B).
 % 而且不定根主要分布在基部，顶端无不定根生成。
-The adventitious roots were mainly occurred at the base section of stolons (96\%), and few (4\%) were found at the middle section, but no adventitious roots were found at top sections (Figure~\ref{fig:roots}C).
+The adventitious roots were mainly occurred at the base section of stolons (96\%), and few (4\%) were found at the middle section, while no adventitious roots were found at top sections (Figure~\ref{fig:roots}C).
 % 经过20天的沙埋实验，老鼠楽植株茎和叶片的干重比例在不同程度上发生了改变。
@@
 
-% 我们的研究表明，老鼠楽对沙埋有多种不同的响应方式
-Our results suggest that \textit{S. littoreus} responds to sand burial in a variety of ways: uninfluenced ramets height, increased horizontal stolons length, and changed biomass allocation.
-% 这些响应方式的产生可能基于生理生态机制，我们通过和其它海岸沙生植物之间进行对比来进行探讨。
-These responses based on physiological and ecological mechanisms, which we can give a glance to by comparing with other coastal sandy plants.
-
 Sand burial has been assumed to reduce the photosynthetic area of species, which finally inhibit the plant performance in coastal sand dunes \citep{hespEcologicalProcessesPlant1991, brownMechanismsSurvivingBurial2018}.
@@
 For the plants on the windward slopes, some unburied leaves are expected to provide photosynthetic substance to sustain the continuous growth of \textit{S.
-littoreus} even when severe burial has taken place (Figure~\ref{fig:sample-pic}).
+littoreus} even when severe burial occurred (Figure~\ref{fig:sample-pic}).
 
 Consequently, the rapid growth of ramets height in \textit{S.
-littoreus} is not considered as the priority for the escape of sand burial, but it inclines to increase the stolon length due to its vulnerability to buried in a typhoon event, which may contribute to the no significant impact on the ramets height by artificial sand burial in our experiment \citep{maunAdaptationsEnhancingSurvival1994}.
-Our field investigation further showed that the maximum length of \textit{S.littoreus} stolons could be up to $2-3 m$, which was about to 4-6 times of its ramets height in a frequent sand burial habitat (Figure~\ref{fig:added}B).
-This is in agreement to the previous study from Woodhouse et al.
-\citeyear{woodhouseEffectSpeciesDune1977}, who reported that Uniola paniculata tended to grow upward rather than seaward, while \textit{Ammophila breviligulata} preferred to colonize seaward beach surfaces by rhizome growth, which may explain the wider distribution of the latter in an intensive sand burial environment subsequently.
+littoreus} is not considered as the priority for the escape of sand burial, but it inclines to increase the stolon length due to its vulnerability to be buried in a typhoon event, which may contribute to the no significant impact on the ramets height by artificial sand burial tin our experiment \citep{maunAdaptationsEnhancingSurvival1994}.
+Our field investigation further showed that the maximum length of \textit{S.littoreus} stolons could be up to $2-3 m$, which was about to 4-6 times of its ramets height in a frequent sand burial habitat (Figure~\ref{fig:added}b).
+This is in agreement to the previous study from \citet{woodhouseEffectSpeciesDune1977}, who reported that \textit{Uniola paniculata} tended to grow upward rather than seaward, while \textit{Ammophila breviligulata} preferred to colonize seaward beach surfaces by rhizome growth, which may explain the wider distribution of the latter in an intensive sand burial environment subsequently.
 
@@
   \resizebox*{6cm}{!}{\includegraphics{../figs/fig9b.jpg}}}
-  \caption{The stolon length of \textit{S. littoreus} on nebkhas in the developmental period (a) and the stabilized period (b).} 
+  \caption{The stolon length of \textit{S. littoreus} on nebkhas in the developmental period (a) and the stabilized period (b). (Photo by Pingtan Island)} 
   \label{fig:added}
@@
 
-Extensive colonization of horizontal stolons after sand burial will facilitate the plants to increase its capacity for utilization of water and nutrition, which is especially critical for the establishment of plants in a resource-poor environment, such as coastal sand dunes, and further enhance their growth as the dominant species in coastal sand dunes.
-Our results indicated that all sand burial treatments had a significant promotion on the  stolons growth, and complete sand burial had a more obvious influence than half sand burial.
+Extensive colonization of horizontal stolons after sand burial will facilitate the plants to increase its capacity for utilization of water and nutrition, which is especially critical for the establishment of plants in a resource-poor environment, such as coastal sand dunes, and further enhance their growth as the dominant species in coastal sand dunes \citep{divyasreeEcologicalStudyReproduction,mendoza-gonzalezBiologicalFloraCoastal2014}.
+Our results indicated that all sand burial treatments had a significant promotion on the  stolon growth, and complete sand burial had more obvious influence than half sand burial.
 Species usually stimulate their growing point according to the signal of the gravity signal stresses \citep{zhouAnalysisgrowthstrategy2015}, and increase their node number and internode length to escape this physical barrier \citep{maunEffectsBurialSand1996}.
@@
 This was consistent with our field investigation, we found that the tall remets of \textit{S.
-littoreus} could intercept sand sediments, and its conjoint stolons were buried at different levels on, with more sand burial on nebkhas the than it on swales.
+littoreus} could intercept sand sediments, and its conjoint stolons were buried at different levels on nebkhas.
 The stolon length of \textit{S.
@@
 littoreus} stolons in most of the sand burial treatments, both total length and number of roots were increased compared with the CG treatments, which will facilitate their revitalization from sand burial cause by typhoon events.
-More adventitious roots were allocated to the stolon base, after sand burial.
+More adventitious roots were allocated to the stolon base after sand burial.
 Generally, sand burial depth is deeper on the stolon base than other stolon sections due to more sand sediments accumulated around the conjoint ramets, which will increase the capacity for root growth and can improve their access to soil water \citep{yuanEffectsSandAccretion1993}.
 Moreover, \textit{S.littoreus} has a fibrous root system, and adventitious roots are initially produced from the primordium in the stolon node.
-However, only the primordium in the stolons base can develop well and finally break through the cuticular layer to produce the adventitious roots \citep{hochholdingerWeedsCropsGenetic2004}.
+However, only the primordium in the stolon base can develop well and finally break through the cuticular layer to produce the adventitious roots \citep{hochholdingerWeedsCropsGenetic2004}.
 
-The top of stolon is usually the least buried segment of stolons, as the photosynthetic organ, more leaves emerging on the top of stolon will reduce the risk of plants from further sand burial, increase their light capture for photosynthesis and carbon gain \citep{yuanEffectsSandAccretion1993, shiEffectsSandBurial2004, brownMechanismsSurvivingBurial2018}, and ensure enough supply of carbohydrates for plants to escape the sand burial.
+The top section of stolon is usually the least buried sections of stolons, as the photosynthetic organ, more leaves emerging on the top of stolon will reduce the risk of plants from further sand burial, increase their light capture for photosynthesis and carbon gain \citep{yuanEffectsSandAccretion1993, shiEffectsSandBurial2004, brownMechanismsSurvivingBurial2018}, and ensure enough supply of carbohydrates for plants to escape the sand burial.
 Our study further supported this conclusion, and we found that a larger percent of leaves were observed on the top of stolon compared with other stolon sections.
-Gilbert et al.
-\citeyear{gilbertGrowthResponsesCoastal2008} also demonstrated that sand burial could increase the leaf area in mobile dune species, which fully or partially replaced the lost photosynthetic leaf area, so the shoot must elongate its stem to keep newly produced leaves above the sand surface subsequent to the sand burial.
+\citet{gilbertGrowthResponsesCoastal2008} also demonstrated that sand burial could increase the leaf area in mobile dune species, which fully or partially replaced the lost photosynthetic leaf area, so the shoot must elongate its stem to keep newly produced leaves above the sand surface subsequent to the sand burial.
 Consequently, in order to reduce the cost of stem tissue production, the stem tissue density of species is usually negative to the maximal stem elongation rate \citep{frosiniGlobalChangeResponse2012}.
@@
 Response of plants to sand burial is usually species specific, and the growth of plants will be enhanced under optimal sand burial rate \citep{noletUAVimagingModelGrowth2018}.
-We found that \textit{S.littoreus} can adapt to the severe sand burial caused by frequent typhoons in our study area, and will revitalize later by increasing the horizontal stolon length, producing abundant adventitious roots on the stolon base and allocate more biomass to leaves on the stolon apex \citep{yuanEffectsSandAccretion1993}.
+We found that \textit{S.littoreus} can adapt to the severe sand burial caused by frequent typhoons in our study area, and will revitalize later by increasing the horizontal stolon length, producing abundant adventitious roots on the stolon base and allocating more biomass to leaves on the stolon apex \citep{yuanEffectsSandAccretion1993}.
 However, if the sand burial rate is over some threshold, the growth of sand dune species will be inhibited \citep{maunEffectsBurialSand1996, shiEffectsSandBurial2004}.
 Our field investigation showed that few \textit{S.
-littoreus} can be found on the leeward slope of nebkhas (Figure~\ref{fig:leeward_swale}A), which can be attributed to the excessive sand burial on both ramets and conjoint stolons of \textit{S.
+littoreus} can be found on the leeward slope of nebkhas (Figure~\ref{fig:leeward_swale}a), which can be attributed to the excessive sand burial on both ramets and conjoint stolons of \textit{S.
 littoreus}.
 Absence of photosynthesis area, combined with the continuous depletion of reserves previously stored in the plants \citep{frosiniGlobalChangeResponse2012}, finally lead to the failure of \textit{S.
-littoreus} escaped from excessive sand burial on leeward slope of nebkhas (Figure~\ref{fig:sample-pic}).
+littoreus} escaped from excessive sand burial on leeward slope of nebkhas (Figure~\ref{fig:leeward_swale}a).
 Similarly, if the sand burial rate is below some threshold, the species that can not withstand the severe sand burial will co-occur with those resistant to it.
 We found that low to moderate sand burial treatments had no significant impact on the stolon extension of \textit{S.littoreus}, which will not favor its access to the more habitats for soil water and nutrition, and further weaken its advantages as the dominant species with the decrease of sand burial rate.
-This is also consistent with our field investigation, \textit{Oenothera drummondii}, an invasive species widely distributed on the stabilized dune in South China, was co-occurred with \textit{S.littoreus} on the less dynamic nebkhas in our study area (Figure~\ref{fig:added}A).
+This is also consistent with our field investigation, \textit{Oenothera drummondii}, which is more frequently occurred on the nebkhas stabilized by \textit{C.
+equisetifolia}, an invasive species widely distributed on the stabilized dune in South China, was co-occurred with \textit{S.littoreus} on the less dynamic nebkhas in our study area (Figure~\ref{fig:added}a).
 
@@
 (1) All sand burial treatments had no significant impact on the 
-ramets height of S.
-littoreus.
-However, compared with the CG treatments, they significantly enhanced the stolon extension of S.
-littoreus under intense sand burial (HI and CI) treatments by 24.56\% and 40.79\%, respectively.
+ramets height of \textit{S.
+littoreus}.
+However, compared with the CG treatments, they significantly enhanced the stolon extension of \textit{S.
+littoreus} under intense sand burial (HI and CI) treatments by 24.56\% and 40.79\%, respectively.
 
-(2) Sand burial stimulated the production of adventitious roots mainly on stolon base, and enhanced the germination of leaves on the top of stolon.
+(2) Sand burial stimulated the production of adventitious roots mainly on stolon base, and enhanced the germination of leaves on the stolon top of \textit{S. littoreus}.
 
-(3) S. littoreus can adapt to the intense sand burial, it can be considered as one of the optimal species for stabilizing and building the coastal sand dunes in South China.
+(3) \textit{S.
+littoreus} can adapt to the intense sand burial in growing season by rapid growth of stolons, it can be considered as one of the optimal species for stabilizing and building the coastal sand dunes in South China.
 
@@
 % An unnumbered section, e.g.\ \verb"\section*{Acknowledgements}", may be used for thanks, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.
-Thanks to Patrick Hesp for his assistance with editing our paper.
+Thanks to Patrick Hesp for his assistance with editing our paper. Thanks to Yingling Zhang and Zhiqiang Ye for their assistance with the field experiment.
 
@@
 
-\section{References}
-
 \bibliographystyle{tfcse}

### 2020-12-28 tex/interactcsesample.tex
change figs' number

@@
 Specifically, the significant effect of sand burial on the stolon growth was firstly observed at 9 days for the CI treatments, while it delayed at 13 days for the HI treatments ($P<0.05$).
-Moreover, the growth of horizontal stolons was more enhanced by sand burial in CI treatments than HI treatments, with the stolon length increased by $40.79\%$ in CI treatments, while $24.56\%$ in HI treatments after the end of 20-day sand burial experiment (Figure~\ref{fig:growth}a and B).
+Moreover, the growth of horizontal stolons was more enhanced by sand burial in CI treatments than HI treatments, with the stolon length increased by $40.79\%$ in CI treatments, while $24.56\%$ in HI treatments after the end of 20-day sand burial experiment (Figure~\ref{fig:growth} A and B).
 Based on that, the proportion of stolon length in top section was increased continuously from $22.09\%$, $25.53\%$ to $46.48\%$, $50.20\%$, for HI and CI treatments, respectively.
@@
 The production of adventitious roots was promoted in most of the sand burial treatments, both in total length and number of roots.
-The most increase was observed in the HM treatments, and the average root length is $5.1cm$, the average root number is $2$, while no adventitious roots were observed in the CG treatments (Figure~\ref{fig:roots}a and B).
+The most increase was observed in the HM treatments, and the average root length is $5.1cm$, the average root number is $2$, while no adventitious roots were observed in the CG treatments (Figure~\ref{fig:roots} A and B).
 % 而且不定根主要分布在基部，顶端无不定根生成。

### 2021-01-01 tex/interactcsesample.tex
rectified according Du's comments -v3

@@
 \documentclass[]{interact}
-
+\usepackage{lineno}
 \usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
@@
 
+\linenumbers
 \articletype{ARTICLE}% Specify the article type or omit as appropriate
@@
 Throughout the experiment, about 96\% of adventitious roots were observed on the base section of stolons, while no roots in the control group (CG). 
-After a 20-day artificial sand burial treatments, the dry weight ratio between stem and leaf of \textit{S. littoreus} was decreased in all three sections of stolons, especially for the top sections. 
+After 20-day artificial sand burial treatments, the dry weight ratio between stem and leaf of \textit{S. littoreus} was decreased in all three sections of stolons, especially for the top sections. 
 % 通过匍匐茎的快速生长，匍匐茎基部产生大量不定根，匍匐茎顶端的叶片萌发率较高，可以适应完全的砂埋。
@@
 littoreus} on the windward slopes were selected, and labeled with a red cord at points 1/3 and 2/3 of the length from the stem base to the top of the stolons.
-All plant species around the selected plants around the selected plants were manually cleared, and wooden frames $20 cm$ in height (similar to the height of stolons) were set around the selected plants.
+All plant species around the selected plants were manually cleared, and wooden frames $20 cm$ in height (similar to the height of stolons) were set around the selected plants.
 Later, all the observed plants were fixed with a label, and its serial number was recorded on the label and wooden baffles respectively in order to facilitate the periodic measurements later.
@@
 Since the vertical ramets of \textit{S.
-littoreus} is relatively high, it is unlikely for them to be completely buried in single typhoon event (Figure~\ref{fig:sample-pic}a).
+littoreus} is relatively high, it is unlikely for them to be completely buried in a single typhoon event (Figure~\ref{fig:sample-pic}a).
 The treated \textit{S.
@@
 Consequently, the rapid growth of ramets height in \textit{S.
-littoreus} is not considered as the priority for the escape of sand burial, but it inclines to increase the stolon length due to its vulnerability to be buried in a typhoon event, which may contribute to the no significant impact on the ramets height by artificial sand burial tin our experiment \citep{maunAdaptationsEnhancingSurvival1994}.
+littoreus} is not considered as the priority for the escape of sand burial, but it inclines to increase the stolon length due to its vulnerability to be buried in a typhoon event, which may contribute to the no significant impact on the ramets height by artificial sand burial in our experiment \citep{maunAdaptationsEnhancingSurvival1994}.
 Our field investigation further showed that the maximum length of \textit{S.littoreus} stolons could be up to $2-3 m$, which was about to 4-6 times of its ramets height in a frequent sand burial habitat (Figure~\ref{fig:added}b).
@@
   \resizebox*{6cm}{!}{\includegraphics{../figs/fig9b.jpg}}}
-  \caption{The stolon length of \textit{S. littoreus} on nebkhas in the developmental period (a) and the stabilized period (b). (Photo by Pingtan Island)} 
+  \caption{The stolon length of \textit{S. littoreus} on nebkhas in the developmental period (a) and the stabilized period (b). (Photo was taken in Pingtan Island)} 
   \label{fig:added}
@@
 
-Extensive colonization of horizontal stolons after sand burial will facilitate the plants to increase its capacity for utilization of water and nutrition, which is especially critical for the establishment of plants in a resource-poor environment, such as coastal sand dunes, and further enhance their growth as the dominant species in coastal sand dunes \citep{divyasreeEcologicalStudyReproduction,mendoza-gonzalezBiologicalFloraCoastal2014}.
+Extensive colonization of horizontal stolons after sand burial will facilitate the plants to increase its capacity for utilization of water and nutrition, which is especially critical for the establishment of plants in a resource-poor environment, such as coastal sand dunes, and further enhance their growth as the dominant species in coastal sand dunes \citep{divyasreeEcologicalStudyReproduction2019,mendoza-gonzalezBiologicalFloraCoastal2014}.
 Our results indicated that all sand burial treatments had a significant promotion on the  stolon growth, and complete sand burial had more obvious influence than half sand burial.
@@
 We found that low to moderate sand burial treatments had no significant impact on the stolon extension of \textit{S.littoreus}, which will not favor its access to the more habitats for soil water and nutrition, and further weaken its advantages as the dominant species with the decrease of sand burial rate.
-This is also consistent with our field investigation, \textit{Oenothera drummondii}, which is more frequently occurred on the nebkhas stabilized by \textit{C.
-equisetifolia}, an invasive species widely distributed on the stabilized dune in South China, was co-occurred with \textit{S.littoreus} on the less dynamic nebkhas in our study area (Figure~\ref{fig:added}a).
+This is also consistent with our field investigation, \textit{Oenothera drummondii}, an invasive species widely distributed on the stabilized dune in South China, is more frequently co-occurred with \textit{S.littoreus} on the nebkhas stabilized by \textit{C.
+equisetifolia} in our study area (Figure~\ref{fig:added}a).
 
@@
 However, \textit{S.
-littoreus} can not be dominant in this area because of heavy competition.}
+littoreus} can not be dominant in this area because of heavy competition.
+Photo was taken in Pingtan Island.}
   \label{fig:leeward_swale}
@@
 
-(3) \textit{S.
-littoreus} can adapt to the intense sand burial in growing season by rapid growth of stolons, it can be considered as one of the optimal species for stabilizing and building the coastal sand dunes in South China.
+(3) \textit{S. littoreus} can adapt to the severe sand burial in growing season, it can be considered as one of the optimal species for stabilizing and building the coastal sand dunes in South China.
 

### 2021-01-02 drafts/Response letter.md
Finished the response letter

## Response letter:

January 1st, 2020

Editor-in-Chief
*Ecoscience*

Dear Dr. Hugo Asselin,

We thank the two anonymous reviewers for their thoughtful and useful comments on the previous of our manuscript (TECO-2020-0114) and we are pleased to submit this revised version for potential publication in *Ecoscience*. We have carefully followed the reviewers' suggestions as well as your editorial concerns, in conducting our revision. We now re-analysised the data and nearly rewrite the manuscript to response to reviewers' major concerns, the main points that have been changed in the new version are:

- We have significantly streamlined the manuscript to make it more focused on our main findings now.
- We have re-analysed the data to ensure that the methods and results are more reliable and that the significance levels and error criteria have been chosen in line with international practice.
- We have revised the presentation of the manuscript to make our experimental approach more understandable.

We have also addressed all the other questions and comments raised by the two reviewers. A detailed response to each question and each comment from the reviewers is attached to this cover letter.

We trust that this new version will satisfy both you and the reviewers. Thank you once again for the time that you and reviewers have spent reviewing this MS.

The manuscript includes 1 text (3903 words), 9 figures, 40 references. 9 figure and 1 tables.

We look forward to hearing from you.

Yours sincerely,
Shuang Song (on behalf of the author team)

## Response to Reviewer #1

We have followed all your suggestions in our revision. Below are the reviewer’s previous comments, followed by our responses.

Sincerely,
Shuang Song

---

***[Reviewer #1 Comment #1]*** The ms of Song et al concerns the adaptive capacity of psammophytes to sand burial as a crucial factor for the ecological restoration of coastal dune systems. The aim of the study was to analyze the responses of a typical for the coastal area of South China psammophytic species (Spinifex littoreus) to different sand burial depths and levels. The study is particularly relevant as coastal dunes in China are highly endangered (as many coastal dune systems in the world). The study is also very interesting and well conducted and reports valuable information, which could be a useful tool in the future for a natural and environmentally friendly way for protection and restoration of coastal dune systems in the area. In my opinion, the ms is worth to be published, just minor changes are requested.
***[Response]*** We are grateful to reviewer #1 for the effort reviewing our paper and his/her positive feedback. The information of our work as written by this reviewer is useful and critical. Here below we address the questions and suggestions raised by the reviewer #1.

***[Reviewer #1 Comment #2]*** Line 116: Figure 1. is the third Figure, mentioned in the text, so I think it would be better to renumber it to Figure 3. and renumber the other Figures accordingly.
***[Response]*** Since we re-analyzed our data, we have re-organized manuscript with figures where numbers are well renumbered.

***[Reviewer #1 Comment #3]*** Lines 117-119: Can you provide a reference, that concerns flora and/or vegetation of nebkhas/foredunes in the area?
***[Response]*** We added some new cites in the proper position of ms now (e. g. (Yang et al. 2017, Divyasree & Raju 2019)) to describe the vegetation in this area.

***[Reviewer #1 Comment #4]*** Line 125: How did you compare the age of different plants?
***[Response]*** Thanks for pointing this out. In fact, we only compare them by size (we mis-wrote in the last version.).

***[Reviewer #1 Comment #5]*** Lines 127-129: Did you measure the height of vertical ramets and the length of stolons to know they were all similar with each other before choosing the plants for the study?
***[Response]*** Yes, we started our measurements in the first day of experiment and the we show them in the figures now [**see Figure 5**].

***[Reviewer #1 Comment #6]*** Line 131: What do you mean by "weeds" - all plant species around the selected plants, or particular species, that you consider undesirable, which tend to overgrow or choke out more desirable plants?
***[Response]*** Thanks for the valuable comment, this has been clarified in the revised version of the manuscript:
**[Line 130-131]** All plant species around the selected plants were manually cleared, and...

***[Reviewer #1 Comment #7]*** Lines 269-272: This sentence is not clear to me.
***[Response]*** Thanks for pointing this out, we have deleted this unclear sentence.

***[Reviewer #1 Comment #8]*** Although I'm not a native English speaker, I believe that English should be improved. I wouldn't say it is poor but it needs to be revised. Some examples:
Lines 28-29: Sand dunes occupy a finite area in coastal regions, but they are characterized by providing multiple ecological services, …
Line 57: The tolerance capacity to different sand burial levels is varied among species, …
Lines 142-143: Since the height of vertical ramets of S. littoreus is relatively high, it is usually impossible for them to be completely buried in the sand.
***[Response]*** Thanks for the valuable comment, this has been clarified in the revised version of the manuscript.

### References

Divyasree, M. & A. J. S. Raju, 2019. An Ecological Study Of Reproduction In Spinifex Littoreus (Burm.F.) Merr. (Poaceae), A Dominant Species Of Sand Dune Ecosystem Along The Visakhapatnam Coast, Andhra Pradesh. Journal of Palynology, 55: 35–54.

Yang, X., J. Du, J. Qin, Z. Chen, L. Yang & S. Song, 2017. Diurnal variation characteristics of leaf water potential of Spinifex littoreus on the nebkhas in different succession periods on the coast of Pingtan Island, Fujian Province, China. Chinese Journal of Applied Ecology, 28: 3260.

## Response to Reviewer #2

We have followed all your suggestions in our revision. Below are the reviewer’s previous comments, followed by our responses.

Sincerely,
Shuang Song

---

***[Reviewer #2 Comment #1]***

The authors conducted an experiment to determine how sand burial added at different rates and in different location at a coastal site impact different growth metrics of Spinifex littoreus. The authors found that sand burial had a limited impact on vertical ramet height regardless of amount of sand burial. However, burial did influence stolon growth, such that complete burial increased stolon growth. The authors also found that adventitious root growth was impacted by sand burial. Adventitious roots were present in all burial treatments and their presence increased as burial amount increased.

Overall, I think that most of the manuscript is well written but could benefit from more editing to make the language clearer for the reader. The main concern I have I have with this study is the length of the manuscript, the justification of the methods, and how the statistical analysis was conducted. I will include concerns and comment for each section below.

***[Response]*** Thank you for acknowledging the importance of our research and we have now restructured the manuscript so that these important questions can be clearly answered and discussed in a focused manner.

**Introduction:**

***[Reviewer #2 Comment #2]*** I think the introduction is well done. The authors include adequate information and have clearly shows their understanding of the dune burial literature. Primarily I think the introduction would benefit from a clear hypothesis statement. The objectives of the project are clear, but I think the reader will benefit from a hypothesis which will orient the reader so that they know what the experts (the authors) are expecting from their study.

***[Response]*** Thanks to your positive comments and useful suggestions, we now clearly give our scientific hypothesis: 
**[P3: L94-96]** In this study, we assume that the growths of *S. littoreus* can be facilitated with the increase of sand burial, which is probably the key factor for this native plant to adapt to the intense sand burial caused by frequent typhoon events in growing seasons.

Some other line by line comments:

***[Reviewer #2 Comment #3]*** Line 63-67 - These two sentences present similar results, but the author makes it seem as though they are contradictory – consider revising.
***[Response]*** Thank you for pointing this out, we have now changed them to a paratactic relationship **[P2, L63-67]**:

> Wang (2005) demonstrated that both stem height in the vertical direction and leaf weight of Messerschmidia sibirica were increased with light sand burial, while they all decreased with moderate treatments contrasted with the control. In addition, Zhou et al. (2015a) showed that the growth of Artemisia desterorum was enhanced with moderate sand burial, but inhibited with intense sand burial.

***[Reviewer #2 Comment #4]*** Line 83 – the term nebkhas is a little jargony - readers that are not familiar with types of dunes will not know what this is. I suggest defining more clearly.
**[Response]** Thank you for pointing this out, we now give a simple note **[P2, L82-83]**:

> ...particularly its stolons on nebkhas (a sand dune that forms around vegetation)...

**Methods:**

***[Reviewer #2 Comment #5]*** There are some revisions that could benefit the flow of the methods, mostly with regard to editing sentence structure.

My primary concern with the methods comes from the lack of detail regarding the timeline of when the measurements were made, etc. Specifically, this is an issue in lines 133-139.

I have a concern with the methods of uncovering and re-covering plants to make measurements. I understand the need to uncover the plants to make the measurements the authors needed to make. But by continuously uncovering and re-covering the plants they are complicating the burial treatment (specifically for with regard to gravity signal strength). But if the authors have found another study that uses a similar method, they should cite that paper for justification. If not, they should provide their own justification to explain how this method will not influence plant response to treatments.

***[Response]*** Thanks to your valuable comments, we have now given a more detailed explanation of the measurement process **[P6, L145-155]**:

>During the measurements, the sand burying the plants was carefully removed to one side in a wooden baﬄe, and the height of the vertical ramets, the length of the stolons and adventitious roots were all measured with a tape. Considering the uncovering and re-covering of sand will probably aﬀect the gravity signal of plants to sand burial, we ﬁnished our measurements in minutes to minimize the potential disturbance, and re-covered the plants to the previous sand burial level with same sand. When the experiments were ﬁnished, both above and below ground biomass of plants were collected and separated according to the label on the stolons. Then all the samples were taken back to the laboratory, and the roots, stems and leaves were separated from the stolons, dried in the oven with a temperature of 65◦C for about 24 h until the weight was constant, and then weighed with an analytical balance (accuracy: 0.0001g).

In summary, as our measurements are usually of short duration (a few minutes) and the overall experiment of long duration (20 days), we believe that we can ignore the effect of the short measurement time on the long-term growth of the plants. By the way, such an experimental approach is similar to that of Zhou et al.

**Data analysis:**

***[Reviewer #2 Comment #6]*** I am confused about why the authors used SD as their measure of variance rather than standard error. When comparing and testing differences of treatments/controls you should be using standard error as the proper metric to represent variation.
***[Response]*** Yes you are right, thank you very much for pointing this out, we confused the two concepts before and have now corrected it.

***[Reviewer #2 Comment #7]*** The use of an alpha-value of 0.1 is not typical in Ecological sciences (at least in the U.S.). Is there a justification for why analysis was conducted with an alpha = 0.1? Usually the common practice is setting the critical value at alpha = 0.05.
***[Response]*** Thank you for your helpful suggestions, we have used 0.05 as the p threshold throughout the new version of manuscript to allow comparison with previous studies.

***[Reviewer #2 Comment #8]*** Based on the scientific design the authors are describing, they should probably be analyzing the data with either a two- or three-way ANOVA. It seems as though plot position (windward, leeward, and swale), days since buried, and amount of burial are all factors with different levels that could be interacting and thus impacting plant response. For this reason, a factorial ANOVA should be considered for analysis. Factorial ANOVAs can be conducted in coordination with repeated measures and I think this should be considered. If the authors have considered these data analysis techniques and chose to not analyze the data in this way, they should provide justification for why they chose not to conduct these analyses.
***[Response]*** We think mix-designed repeated measurements ANOVA is the proper method because it can analyze mixed-effects between treatments and time. It was a pity that we had not concentrated on the mixed-effect in the past version of manuscript. However, we have rectified that and give a sketch to differences between the sand-buried groups and the control groups, in the latest version of manuscript **[see the new figure 4]**.

***[Reviewer #2 Comment #9]*** Some specific comments for the methods section:

Line 107 – change to “Monsoons are…”

Line 141-142 – I don’t think this is a complete sentence.

***[Response]*** Thank you for pointing out these issues, we have revised each of them in the new version:

> [P3, L107] Monsoons are the dominant wind...
>
> [L138-140] Since the vertical ramets of S. littoreus is relatively high, it is unlikely for them to be completely buried in a single typhoon event (Figure 1a). The treated S. littoreus, thus, only the stolons of which were buried at diﬀerent depths and levels (see Figure 3 and Table 1).

***[Reviewer #2 Comment #10]*** Line 145-147 - This is confusing. I am unclear whether there are many different burial levels or if there is only a control group and a burial group? Previous sentences make it seem like there are multiple treatments (line 141-142) but this sentence makes it seem there is just high intensity and a control.
***[Response]*** In the previous version, we presented and discussed the results of the experiments in different locations, which were illustrated due to the small sample of plants on non-windward slopes. We now focus only on the windward slopes, where the species grows most vigorously, to focus on responding to our core hypotheses. The other areas (leeward slopes and swales) we have added to the discussion. In the current version we have therefore deleted the sentence.

***[Reviewer #2 Comment #11]*** Line 165-167 - The Car and Multcomp packages likely have citations included in their R documentation. I think R packages should be cited properly. 
***[Response]*** We have re-analysed the data using Python after correcting the method and have included the corresponding references **[L157-161]**:

> All the data were calculated with average according to all the replications with standard error as measurement of variability. The results were analysed with Python3 and package Pingouin (Vallat 2018). For each observed variable, we used repeated measure ANOVA analysis to test if the experimental treatments were veriﬁed due to time, and checked the signiﬁcance (P < 0.05).

**Results:**

***[Reviewer #2 Comment #12]*** There are a lot of results for this paper and I think some for the most important results get lost in the complexity of the results section as a whole. I think this paper will benefit from pairing down the results to the most important results that contribute most to the gaps in dune grass burial literature.
***[Response]*** Thank you for your valuable suggestions, we have now significantly streamlined the results and focused on two main points:

- Inﬂuence of sand burial on the growths of S. littoreus
- Inﬂuence of sand burial on the biomass allocation of S. littoreus

***[Reviewer #2 Comment #13]*** Specific comments in the results section:
Line 213-216 – This section again appears to be results of a two-way ANOVA in which the author is analyzing how burial is impacted by burial based on time period - however, the statistical analysis section does not talk about the author running a factorial ANOVA.
***[Response]*** We have rewritten the results section and now ensure that both the charts and the text show the interaction issues of time correctly in **[Figure 4]**.

***[Reviewer #2 Comment #14]*** Line 223 – Delete “In half sand burial”
***[Response]*** Thanks for this specific useful comment, rectified.

***[Reviewer #2 Comment #15]*** Line 237-240 – This seems a little unclear. It is unclear how important some of these results are to the study. I think this clarity could be improved by incorporating a hypothesis in the introduction.
***[Response]*** We have re-analysed the data and show the results of the biomass allocation in a dedicated section **[see section result Inﬂuence of sand burial on the biomass allocation of S. littoreus]**.

**Discussion:**

***[Reviewer #2 Comment #16]*** The discussion section is also very long, and I think this paper will be better if it were short than the current version and focus on the informative results. The authors dedicate much of their discussion to comparison with other burial studies, which is a good practice in scientific writing. But, most/all the comparisons are between different species. But we know that burial response is species specific. So, I think the discussion dedicates too much space to species-species comparisons of S littoreus and other species studied by other researchers.
***[Response]*** Again, we have followed your useful advice and will now focus our discussion on two points, now:

- Responses of S. littoreus to severe sand burial
- Signiﬁcance of S. littoreus’ adaptation to sand burial

***[Reviewer #2 Comment #17]*** Specific comments for the results section:
Line 247: This is not an assumption. There are many sand burial studies that have shown this definitively.
***[Response]*** Thanks, you are right, that was not an assumption, rectified:

> [L189] Sand burial can reduce the photosynthetic area...

***[Reviewer #2 Comment #18]*** Line 251-254 – This is where the concern of the methods comes in. i.e. How is the intermittent uncovering and recovering of individuals impacting the results of this study?
***[Response]*** We explained after that:

> [L196-200] This is probably due to the growth characteristics of S. littoreus, which displays both vertical and horizontal extension, the height of its ramets ranges from 40 to 60 cm, and it is virtually impossible to bury the entire vertical ramets by the sand sediments relative to its conjoint stolons during a single typhoon event

We believe that this difference is likely to be an important factor in the ability of the species we studied to adapt to the harsh post-typhoon sand-buried environment.

***[Reviewer #2 Comment #19]*** Line 261-262 – This needs to be more scientifically written. The lateral expansion of dune plants may be about "escaping sand burial" but it is a critical mechanism contributing to building dune ridges that protect the length of the coast.
***[Response]*** Thanks to your helpful suggestions, we have changed the presentation to show this "escape effect" in a more scientific way:

> [L203-206] Consequently, the rapid growth of ramets height in S. littoreus is not considered as the priority for the escape of sand burial, but it inclines to increase the stolon length due to its vulnerability to be buried in a typhoon event, which may contribute to the no signiﬁcant impact on the ramets height by artiﬁcial sand burial in our experiment (Maun 1994).

***[Reviewer #2 Comment #20]*** Line 263-267 – Some of this is either inaccurate or unclear. This sentence suggests that Ammophila and Uniola grow in different areas of the beach. But, Ammophila and Uniola grow in similar beach areas. The difference is with growth strategy Uniola does grow more vertically while Ammophila has more rapid vertical expansion. 
***[Response]*** This sentence has been removed in the new edition, as it does not help much with the main scientific hypothesis we are now concerned with.

***[Reviewer #2 Comment #21]*** Line 294-297 – This is an important sentence, but it needs revised. It is very long for a statement that should be very simple.
***[Response]*** We now discuss this in a much more simple way:

> [L266-268] However, if the sand burial rate is over some threshold, the growth of sand dune species will be inhibited (Maun 1996; Shi et al. 2004).

***[Reviewer #2 Comment #22]*** Line 301-304 – This needs revised slightly. Seems like the authors are saying the height of the ramets causes more burial at different successional stages of dune building/stabilization process?
***[Response]*** We have now added new images **[Figure 9]** to show this discrepancy that we found during the course of our survey. This supports the apparent effect of different levels of sand burial on the growth of this species.

***[Reviewer #2 Comment #23]*** Line 318-321 – I am not sure this sentence contributes much to the current study.
***[Response]*** Thanks for point this out, deleted.

***[Reviewer #2 Comment #24]*** Line 323-326 – I feel like this sentence starts talking about one thing but switches to talk about another? I think the issue lies in the organization of the paragraph. Further, if stress signal of gravity plays a factor is burial response. Then wouldn't uncovering and recovering plants impact the stress signal of gravity through the course of the study?
***[Response]*** As explained in the additional section on methods, our measurements are extremely short relative to the growth experiment, and the results of the long-term experiment are interpreted here.

***[Reviewer #2 Comment #25]*** Line 346-349 – Many of the author's sentences are formatted in this way and I think they should be reconstructed to help the reader follow the sequential processes the author is describing.
***[Response]*** Thank you for your helpful advice, we have checked for similar issues in full manuscript.

***[Reviewer #2 Comment #26]*** Line 389 – I have issue with the use of the word “confirmed” here. I think this is not the correct word selection. findings can't be confirmed by an older study. This study would confirm the findings of Maun 1994, not the other way around.
***[Response]*** You are correct, we have removed a similar misrepresentation, thanks a lot.

***[Reviewer #2 Comment #27]*** Line 356 - This was easily the best portion of this paper. I think the authors should focus and highlight this result/discussion in future drafts of this paper.
***[Response]*** Thank you for such constructive comments, we have devoted half of the new manuscript to presenting and discussing the results in relation to this, which we believe makes the new manuscript more relevant

### References

Maun, M. A., 1994. Adaptations enhancing survival and establishment of seedlings on coastal dune systems. Vegetatio, 111: 59–70.

Vallat, R., 2018. Pingouin: statistics in Python. Journal of Open Source Software, 3: 1026.

Zhou, R., Y. Hou, Y. Wang & J. Zuo, 2015a. The physiological adaptation mechanisms of four common desert species in response to desert environments. Acta Ecologica Sinica, 35: 340–349.

Zhou, R., D. Yang, J. Zuo, Y. Wang, Q. Li & D. Hu, 2015b. Analysis on the growth strategy of creeping stem inVitex trifolia var.simplicifoliadapting to sand burial. Acta Ecologica Sinica, 35: 1165–1174.

### 2021-01-02 tex/interactcsesample.tex
Finished the response letter

@@
   Qirui Wu \textsuperscript{a},
-  Mingyang Ni \textsuperscript{a} and Yijia Wang \textsuperscript{a}}\affil{\textsuperscript{a}School of Geography and Planning, Sun Yat-Sen University, Guangzhou, 510275, China; \textsuperscript{b} Guangdong Key Laboratory for Urbanization and Geo-simulation, Guangzhou, 510275, China}
+  Mingyang Ni \textsuperscript{a}, Yijia Wang \textsuperscript{a} and Yingling Zhang \textsuperscript{a}}\affil{\textsuperscript{a}School of Geography and Planning, Sun Yat-Sen University, Guangzhou, 510275, China; \textsuperscript{b} Guangdong Key Laboratory for Urbanization and Geo-simulation, Guangzhou, 510275, China}
 }
@@
 Annual average temperature is $19.5^{\circ}C$, and precipitation is $1151 mm$.
-The monsoon is the dominant wind in this area, SE in the summer and NE in the winter, with an annual average wind speed of $6.9 m/s$.
+The monsoons are the dominant wind in this area, SE in the summer and NE in the winter, with an annual average wind speed of $6.9 m/s$.
 A total of 106 typhoons made landfall on Pingtan Island from 1981 to 2019, average 2.65 times per year, and mainly they occurred in July to September.
@@
 All the data were calculated with average according to all the replications with standard error as measurement of variability.
-The results were analysed with Python3 and package Pingouin.
+The results were analysed with Python3 and package Pingouin \citep{vallatPingouinstatisticsPython2018}.
 For each observed variable, we used repeated measure ANOVA analysis to test if the experimental treatments were verified due to time, and checked the significance $(P<0.05)$.
@@
 
-Sand burial has been assumed to reduce the photosynthetic area of species, which finally inhibit the plant performance in coastal sand dunes \citep{hespEcologicalProcessesPlant1991, brownMechanismsSurvivingBurial2018}.
+Sand burial can reduce the photosynthetic area of species, which finally inhibit the plant performance in coastal sand dunes \citep{hespEcologicalProcessesPlant1991, brownMechanismsSurvivingBurial2018}.
 Species that withstand sand burial can recover very rapidly by elongating internodes in vertical shoots to overcome this physical barrier \citep{frosiniGlobalChangeResponse2012,keijsersModelingBiogeomorphicEvolution2016, quEffectsSandBurial2017,enriquezAssessingBeachDune2019}.
@@
 % An unnumbered section, e.g.\ \verb"\section*{Acknowledgements}", may be used for thanks, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.
-Thanks to Patrick Hesp for his assistance with editing our paper. Thanks to Yingling Zhang and Zhiqiang Ye for their assistance with the field experiment.
+Thanks to Patrick Hesp for his assistance with editing our paper. Thanks to Yingling Zhang for his assistance with the field experiment.
 

### 2021-01-03 tex/interactcsesample.tex
slightly rectified by Du's comments

@@
 Therefore, understanding the adaptive strategies of \textit{S.
-littoreus} to sand burial levels, and its role in the stabilization of coastal sand dunes are very crucial for the effective coastal management and conservation in South China.
+littoreus} to sand burial levels, and its role in the stabilization of coastal sand dunes are very crucial for the effective coastal dune management and conservation in South China.
 
@@
   \centering
-  \subfloat[\textit{S. littoreus} was burial after a typhoon.]{%
+  \subfloat[\textit{S. littoreus} was buried after a typhoon.]{%
   \resizebox*{6cm}{!}{\includegraphics{../figs/sand_buried_plants.png}}}\hspace{5pt}
@@
   \caption{(a) Intensive sand burial on the \textit{Spinifex littoreus} nebkhas on Pingtan Island after typhoon Soudelor (1513) landed in Putian City, Fujian Province, China in August, 2015.
-(b) The nebkhas formed by \textit{Spinifex littoreus} was stabilized by the planting of an invasive species Casuarinas equisetifolia seedlings on Pingtan Island, Fujian Province, China.}
+(b) The nebkhas formed by \textit{Spinifex littoreus} was stabilized by the planting of an invasive species \textit{Casuarinas equisetifolia} seedlings on Pingtan Island, Fujian Province, China.}
   \label{fig:sample-pic}
@@
 % 我们认为不同的沙埋情形将改变植株的生长方式，是该植物能够适应台风带来的强烈沙埋的关键性因素。
-In this study, we assume that the growths of \textit{S.
+In this study, we assume that the growth of \textit{S.
 littoreus} can be facilitated with the increase of sand burial, which is probably the key factor for this native plant to adapt to the intense sand burial caused by frequent typhoon events in growing season.
@@
 Stolons of \textit{S.
-littoreus} on the windward slopes were selected, and labeled with a red cord at points 1/3 and 2/3 of the length from the stem base to the top of the stolons.
+littoreus} on the windward slopes were selected, and labeled with a red cord at points 1/3 and 2/3 of the length from the stolon base to the stolon top.
 All plant species around the selected plants were manually cleared, and wooden frames $20 cm$ in height (similar to the height of stolons) were set around the selected plants.
@@
   \subfloat[Developmental period.]{%
-  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9a.jpg}}}\hspace{5pt}
+  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9b.jpg}}}\hspace{5pt}
   \subfloat[Stabilized period.]{%
-  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9b.jpg}}}
+  \resizebox*{6cm}{!}{\includegraphics{../figs/fig9a.jpg}}}
   \caption{The stolon length of \textit{S. littoreus} on nebkhas in the developmental period (a) and the stabilized period (b). (Photo was taken in Pingtan Island)} 
@@
 Species usually stimulate their growing point according to the signal of the gravity signal stresses \citep{zhouAnalysisgrowthstrategy2015}, and increase their node number and internode length to escape this physical barrier \citep{maunEffectsBurialSand1996}.
-The stresses signal of gravity signal in complete sand burial was usually stronger than it in half sand burial \citep{wangAdvancesStudiesMorphological2005}.
+The stresses signal of gravity in complete sand burial was usually stronger than it in half sand burial \citep{wangAdvancesStudiesMorphological2005}.
 This was consistent with our field investigation, we found that the tall remets of \textit{S.
@@
 Our results indicated that the adventitious roots were produced on the \textit{S.
-littoreus} stolons in most of the sand burial treatments, both total length and number of roots were increased compared with the CG treatments, which will facilitate their revitalization from sand burial cause by typhoon events.
+littoreus} stolons in most of the sand burial treatments, both total length and number of roots were increased compared with the CG treatments, which will facilitate their revitalization from sand burial caused by typhoon events.
 More adventitious roots were allocated to the stolon base after sand burial.
-Generally, sand burial depth is deeper on the stolon base than other stolon sections due to more sand sediments accumulated around the conjoint ramets, which will increase the capacity for root growth and can improve their access to soil water \citep{yuanEffectsSandAccretion1993}.
+Generally, sand burial depth is deeper on the stolon base than other stolon sections due to more sand sediments accumulated around the conjoint ramets, which will increase the capacity for root growth and can improve their access to soil water and nutrition \citep{yuanEffectsSandAccretion1993}.
 Moreover, \textit{S.littoreus} has a fibrous root system, and adventitious roots are initially produced from the primordium in the stolon node.
@@
 This is also consistent with our field investigation, \textit{Oenothera drummondii}, an invasive species widely distributed on the stabilized dune in South China, is more frequently co-occurred with \textit{S.littoreus} on the nebkhas stabilized by \textit{C.
-equisetifolia} in our study area (Figure~\ref{fig:added}a).
+equisetifolia} in our study area (Figure~\ref{fig:added}a and Figure~\ref{fig:leeward_swale}b).
 
@@
 % An unnumbered section, e.g.\ \verb"\section*{Acknowledgements}", may be used for thanks, etc.\ if required and included \emph{in the non-anonymous version} before any Notes or References.
-Thanks to Patrick Hesp for his assistance with editing our paper. Thanks to Yingling Zhang for his assistance with the field experiment.
+Thanks to Patrick Hesp for his assistance with editing our paper. Thanks to Zhiqiang Ye for his assistance with the field experiment.
 

### 2021-01-03 drafts/Response letter.md
update response letter

@@
 
-January 1st, 2020
+January 3st, 2020
 
@@
 
-We thank the two anonymous reviewers for their thoughtful and useful comments on the previous of our manuscript (TECO-2020-0114) and we are pleased to submit this revised version for potential publication in *Ecoscience*.
+We thank the two anonymous reviewers for their thoughtful and useful comments on our previous manuscript (TECO-2020-0114) and we are pleased to resubmit this revised version for potential publication in *Ecoscience*.
 We have carefully followed the reviewers' suggestions as well as your editorial concerns, in conducting our revision.
-We now re-analysised the data and nearly rewrite the manuscript to response to reviewers' major concerns, the main points that have been changed in the new version are:
+We now re-analysised the data and nearly rewrote the manuscript in response to reviewers' major concerns, the main points that have been changed in the new version are:
 
@@
 
-The manuscript includes 1 text (3903 words), 9 figures, 40 references. 9 figure and 1 tables.
+The manuscript includes 1 text (3915 words), 9 figures, 40 references and one table.
 
@@
 ***[Reviewer #1 Comment #5]*** Lines 127-129: Did you measure the height of vertical ramets and the length of stolons to know they were all similar with each other before choosing the plants for the study?
-***[Response]*** Yes, we started our measurements in the first day of experiment and the we show them in the figures now [**see Figure 5**].
+***[Response]*** Yes, we started our measurements in the first day of experiment and we show them in the figures now [**see Figure 5**].
 
@@
 An Ecological Study Of Reproduction In Spinifex Littoreus (Burm.F.) Merr.
-(Poaceae), A Dominant Species Of Sand Dune Ecosystem Along The Visakhapatnam Coast, Andhra Pradesh.
+(Poaceae), A dominant species of sand dune ecosystem along the visakhapatnam coast, andhra pradesh.
 Journal of Palynology, 55: 35–54.
@@
 By the way, such an experimental approach is similar to that of Zhou et al.
+2015.
 
@@
 
-Zhou, R., Y. Hou, Y. Wang & J. Zuo, 2015a. The physiological adaptation mechanisms of four common desert species in response to desert environments. Acta Ecologica Sinica, 35: 340–349.
-
 Zhou, R., D.
@@
 Li & D.
-Hu, 2015b.
+Hu, 2015.
 Analysis on the growth strategy of creeping stem inVitex trifolia var.simplicifoliadapting to sand burial.

### 2021-01-03 tex/interactcsesample.tex
update response letter

@@
 During the measurements, the sand burying the plants was carefully removed to one side in a wooden baffle, and the height of the vertical ramets, the length of the stolons and adventitious roots were all measured with a tape.
-Considering the uncovering and re-covering of sand will probably affect the gravity signal of plants to sand burial, we finished our measurements in minutes to minimize the potential disturbance, and re-covered the plants to the previous sand burial level with same sand.
+Considering the uncovering and re-covering of sand will probably affect the gravity signal of plants to sand burial, we finished our measurements in a very short time period (usually 3-5 minutes compared with days of interval) to minimize the potential disturbance, and re-covered the plants to the previous sand burial level with same sand.
 When the experiments were finished, both above and below ground biomass of plants were collected and separated according to the label on the stolons.

### 2021-01-03 drafts/Response letter.md
add screen shot
update submit version

@@
 Dear Dr. Hugo Asselin,
+
+![Screenshot](https://gitee.com/SongshGeo/PicGo_picbed/raw/master/img/%E5%BE%AE%E4%BF%A1%E5%9B%BE%E7%89%87_20210103104911.png)
 
@@
 In my opinion, the ms is worth to be published, just minor changes are requested.
+
 ***[Response]*** We are grateful to reviewer #1 for the effort reviewing our paper and his/her positive feedback.
@@
 ***[Reviewer #1 Comment #2]*** Line 116: Figure 1. is the third Figure, mentioned in the text, so I think it would be better to renumber it to Figure 3. and renumber the other Figures accordingly.
+
 ***[Response]*** Since we re-analyzed our data, we have re-organized manuscript with figures where numbers are well renumbered.
@@
 ***[Reviewer #1 Comment #3]*** Lines 117-119: Can you provide a reference, that concerns flora and/or vegetation of nebkhas/foredunes in the area?
+
 ***[Response]*** We added some new cites in the proper position of ms now (e. g. (Yang et al. 2017, Divyasree & Raju 2019)) to describe the vegetation in this area.
@@
 ***[Reviewer #1 Comment #4]*** Line 125: How did you compare the age of different plants?
+
 ***[Response]*** Thanks for pointing this out. In fact, we only compare them by size (we mis-wrote in the last version.).
@@
 ***[Reviewer #1 Comment #5]*** Lines 127-129: Did you measure the height of vertical ramets and the length of stolons to know they were all similar with each other before choosing the plants for the study?
+
 ***[Response]*** Yes, we started our measurements in the first day of experiment and we show them in the figures now [**see Figure 5**].
@@
 ***[Reviewer #1 Comment #6]*** Line 131: What do you mean by "weeds" - all plant species around the selected plants, or particular species, that you consider undesirable, which tend to overgrow or choke out more desirable plants?
+
 ***[Response]*** Thanks for the valuable comment, this has been clarified in the revised version of the manuscript:
-**[Line 130-131]** All plant species around the selected plants were manually cleared, and...
+
+> **[Line 130-131]** All plant species around the selected plants were manually cleared, and...
 
 ***[Reviewer #1 Comment #7]*** Lines 269-272: This sentence is not clear to me.
+
 ***[Response]*** Thanks for pointing this out, we have deleted this unclear sentence.
@@
 Lines 142-143: Since the height of vertical ramets of S. littoreus is relatively high, it is usually impossible for them to be completely buried in the sand.
+
 ***[Response]*** Thanks for the valuable comment, this has been clarified in the revised version of the manuscript.
@@
 ***[Response]*** Thanks to your positive comments and useful suggestions, we now clearly give our scientific hypothesis:
-**[P3: L94-96]** In this study, we assume that the growths of *S.
+
+> **[P3: L94-96]** In this study, we assume that the growths of *S.
 littoreus* can be facilitated with the increase of sand burial, which is probably the key factor for this native plant to adapt to the intense sand burial caused by frequent typhoon events in growing seasons.
@@
 ***[Reviewer #2 Comment #3]*** Line 63-67 - These two sentences present similar results, but the author makes it seem as though they are contradictory – consider revising.
+
 ***[Response]*** Thank you for pointing this out, we have now changed them to a paratactic relationship **[P2, L63-67]**:
 
-> Wang (2005) demonstrated that both stem height in the vertical direction and leaf weight of Messerschmidia sibirica were increased with light sand burial, while they all decreased with moderate treatments contrasted with the control.
+> [P2, L63-67] Wang (2005) demonstrated that both stem height in the vertical direction and leaf weight of Messerschmidia sibirica were increased with light sand burial, while they all decreased with moderate treatments contrasted with the control.
 In addition, Zhou et al.
@@
 ***[Reviewer #2 Comment #4]*** Line 83 – the term nebkhas is a little jargony - readers that are not familiar with types of dunes will not know what this is. I suggest defining more clearly.
+
 **[Response]** Thank you for pointing this out, we now give a simple note **[P2, L82-83]**:
@@
 When comparing and testing differences of treatments/controls you should be using standard error as the proper metric to represent variation.
+
 ***[Response]*** Yes you are right, thank you very much for pointing this out, we confused the two concepts before and have now corrected it.
@@
 Usually the common practice is setting the critical value at alpha = 0.05.
+
 ***[Response]*** Thank you for your helpful suggestions, we have used 0.05 as the p threshold throughout the new version of manuscript to allow comparison with previous studies.
@@
 If the authors have considered these data analysis techniques and chose to not analyze the data in this way, they should provide justification for why they chose not to conduct these analyses.
+
 ***[Response]*** We think mix-designed repeated measurements ANOVA is the proper method because it can analyze mixed-effects between treatments and time.
@@
 Previous sentences make it seem like there are multiple treatments (line 141-142) but this sentence makes it seem there is just high intensity and a control.
+
 ***[Response]*** In the previous version, we presented and discussed the results of the experiments in different locations, which were illustrated due to the small sample of plants on non-windward slopes.
@@
 ***[Reviewer #2 Comment #11]*** Line 165-167 - The Car and Multcomp packages likely have citations included in their R documentation. I think R packages should be cited properly.
+
 ***[Response]*** We have re-analysed the data using Python after correcting the method and have included the corresponding references **[L157-161]**:
@@
 I think this paper will benefit from pairing down the results to the most important results that contribute most to the gaps in dune grass burial literature.
+
 ***[Response]*** Thank you for your valuable suggestions, we have now significantly streamlined the results and focused on two main points:
@@
 Line 213-216 – This section again appears to be results of a two-way ANOVA in which the author is analyzing how burial is impacted by burial based on time period - however, the statistical analysis section does not talk about the author running a factorial ANOVA.
+
 ***[Response]*** We have rewritten the results section and now ensure that both the charts and the text show the interaction issues of time correctly in **[Figure 4]**.
@@
 ***[Reviewer #2 Comment #14]*** Line 223 – Delete “In half sand burial”
+
 ***[Response]*** Thanks for this specific useful comment, rectified.
@@
 I think this clarity could be improved by incorporating a hypothesis in the introduction.
+
 ***[Response]*** We have re-analysed the data and show the results of the biomass allocation in a dedicated section **[see section result Inﬂuence of sand burial on the biomass allocation of S.
@@
 So, I think the discussion dedicates too much space to species-species comparisons of S littoreus and other species studied by other researchers.
+
 ***[Response]*** Again, we have followed your useful advice and will now focus our discussion on two points, now:
@@
 Line 247: This is not an assumption. There are many sand burial studies that have shown this definitively.
+
 ***[Response]*** Thanks, you are right, that was not an assumption, rectified:
@@
 How is the intermittent uncovering and recovering of individuals impacting the results of this study?
+
 ***[Response]*** We explained after that:
@@
 The lateral expansion of dune plants may be about "escaping sand burial" but it is a critical mechanism contributing to building dune ridges that protect the length of the coast.
+
 ***[Response]*** Thanks to your helpful suggestions, we have changed the presentation to show this "escape effect" in a more scientific way:
@@
 The difference is with growth strategy Uniola does grow more vertically while Ammophila has more rapid vertical expansion.
+
 ***[Response]*** This sentence has been removed in the new edition, as it does not help much with the main scientific hypothesis we are now concerned with.
@@
 ***[Reviewer #2 Comment #21]*** Line 294-297 – This is an important sentence, but it needs revised. It is very long for a statement that should be very simple.
+
 ***[Response]*** We now discuss this in a much more simple way:
@@
 Seems like the authors are saying the height of the ramets causes more burial at different successional stages of dune building/stabilization process?
+
 ***[Response]*** We have now added new images **[Figure 9]** to show this discrepancy that we found during the course of our survey.
@@
 ***[Reviewer #2 Comment #23]*** Line 318-321 – I am not sure this sentence contributes much to the current study.
+
 ***[Response]*** Thanks for point this out, deleted.
@@
 Then wouldn't uncovering and recovering plants impact the stress signal of gravity through the course of the study?
+
 ***[Response]*** As explained in the additional section on methods, our measurements are extremely short relative to the growth experiment, and the results of the long-term experiment are interpreted here.
@@
 ***[Reviewer #2 Comment #25]*** Line 346-349 – Many of the author's sentences are formatted in this way and I think they should be reconstructed to help the reader follow the sequential processes the author is describing.
+
 ***[Response]*** Thank you for your helpful advice, we have checked for similar issues in full manuscript.
@@
 This study would confirm the findings of Maun 1994, not the other way around.
+
 ***[Response]*** You are correct, we have removed a similar misrepresentation, thanks a lot.
@@
 ***[Reviewer #2 Comment #27]*** Line 356 - This was easily the best portion of this paper. I think the authors should focus and highlight this result/discussion in future drafts of this paper.
+
 ***[Response]*** Thank you for such constructive comments, we have devoted half of the new manuscript to presenting and discussing the results in relation to this, which we believe makes the new manuscript more relevant

### 2021-04-28 tex/interactcsesample.tex
Article published

@@
 \documentclass[]{interact}
+\usepackage[lists]{endfloat}
 \usepackage{lineno}
@@
 \name{
-  Shuang Song\textsuperscript{a}, 
-  Jianhui Du \textsuperscript{a,b} \thanks{CONTACT Jianhui Du. Email: dujh1982@hotmail.com}, 
+  Shuang Song\textsuperscript{a,b,c}, 
+  Jianhui Du \textsuperscript{a,d} \thanks{CONTACT Jianhui Du. Email: dujh1982@hotmail.com}, 
   Qirui Wu \textsuperscript{a},
-  Mingyang Ni \textsuperscript{a}, Yijia Wang \textsuperscript{a} and Yingling Zhang \textsuperscript{a}}\affil{\textsuperscript{a}School of Geography and Planning, Sun Yat-Sen University, Guangzhou, 510275, China; \textsuperscript{b} Guangdong Key Laboratory for Urbanization and Geo-simulation, Guangzhou, 510275, China}
+  Mingyang Ni \textsuperscript{a}, Yijia Wang \textsuperscript{a,b,c} and Yingling Zhang \textsuperscript{a}}\affil{\textsuperscript{a}School of Geography and Planning, Sun Yat-Sen University, Guangzhou, 510275, China; \textsuperscript{b} State Key Laboratory of Earth Surface Processes and Resource Ecology, Faculty of Geographical Science, Beijing Normal University, Beijing 100875, China; \textsuperscript{c} Institute of Land Surface System and Sustainability, Faculty of Geographical Science, Beijing Normal University, Beijing 100875, China;\textsuperscript{d} Guangdong Key Laboratory for Urbanization and Geo-simulation, Guangzhou, 510275, China}
 }
